### 2013-07-25 darmstadt_gscl_2013/abstract_sidarenka_scheffler_stede.tex
material and paper draft for darmstadt workshop added

\documentclass[citeauthoryear]{llncs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[german]{babel}
\usepackage{authblk}
\usepackage{paralist}
\usepackage{url}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\nnline}{\\[0.2cm]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{headings}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{MT @HanBaldwin: Fightin OOVs in German \#twitter}
\author{Uladzimir Sidarenka \and Tatjana Schef{}f{}ler \and Manfred Stede}
\institute{Universit\"at Potsdam\nnline
  Postanschrift: Universit\"at Potsdam\\
  Karl-Liebknecht Str. 24-25, 2.32\\
  14476 Potsdam\nnline
  {\small E-Mail: \{uladzimir.sidarenka$|$tatjana.schef{}f{}ler$|$manfred.stede\}@uni-potsdam.de}
  %% Homepage: \texttt{http://www.ling.uni-potsdam.de/acl-lab/SocMedia/main.htm}\\
}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Mit 58 Millionen versendeten Kurznachrichten pro Tag stellt Twitter
eine unsch\"atzbare Ressource an Textinformationen dar, deren
qualit\"atvolle automatische Verarbeitung aber erst durch eine
vorausgehende Normalisierung m\"oglich wird. Und obwohl es schon
etliche Verfahren f\"ur Vorverarbeitung von englischen ``noisy''
Texten gibt (vgl. Aw \cite{aw}, Kaufman \cite{kaufman}, Clark
\cite{clark}, Han \cite{han}), m\"ochten wir in diesem Artikel ein
neues Normalisierungsverfahren vorstellen, das explizit auf deutsche
Tweets ausgerichtet ist und den st\"orenden Effekt von Faktoren der
internetbasierten Kommunikation (IBK) in diesem Textgenre verringert.

Um herauszufinden, welche Faktoren es eigentlich sind, analysierten
wir 10,000 Tweets mit \texttt{TreeTagger} (Schmid, \cite{schmid}) und
\texttt{GNU Hunspell} und berechneten dabei, wie viele Tokens des
Eingabetexts von diesen Programmen als ``out-of-vocabulary'' (OOV)
erkannt wurden. Durch eine Ausz\"ahlung und detaillierte manuelle
Klassifizierung der OOV-W\"orter wurde festgestellt, dass OOV-Tokens
im Durchschnitt mehr als 20~\% aller W\"orter im Twitter-Diskurs
ausmachen und von diesen mehr als die H\"alfte auf
Twitter-spezifisches Markup, IBK-Ph\"anomene oder auch
Rechtschreibfehler zur\"uckzuf\"uhren ist.

Um die Prozentrate der OOV-Tokens zu senken, wendeten wir unser Set
von Heuristiken an. Im ersten Verarbeitungsschritt dieses Sets wurden
Hashtag-Zeichen und Retweet-Angaben entfernt sowie
Twitter-Erw\"ahnungen durch ein spezielles Wort ersetzt, das zum
Lexikon der jeweiligen Tools auch hinzugef\"ugt wurde. In
nachfolgenden Etappen wurden dann weitere h\"aufig beobachtete
OOV-Ph\"anomene in Twitter adressiert vor allem durch:
\begin{inparaenum}[a)]
 \item Wiederherstellung von Umlauten (aus ``ae'', ``ue'' usw.),
 \item R\"uckf\"uhrung von vervielfachten Buchstaben
   (z.B. ``Haaalllloooo'') auf die Grundform,
 \item Normalisierung von Slangausdr\"ucken und Kontraktionen
   (``isser'') und
 \item spezielle Satzgrenzenerkennung und Tokenisierung.
\end{inparaenum}

Durch die Anwendung dieser Verfahren wurde eine Reduzierung der
durchschnittlichen OOV-Rate um 6 bis 9~\% erreicht. Eine nachfolgende
Analyse der verbleibenden OOV-Tokens zeigte auch, dass der Rest der
OOVs eher von der Unvollst\"andigkeit der maschinenlesbaren Lexika
zeugt oder durch Produktivit\"at der Sprache selbst zu erkl\"aren ist,
was aber auch in anderen Textgenres h\"aufig vorkommt.

%% Seit seinem Start in 2006 und bis zu heutiger Zeit hat Twitter
%% ununterbrochen immer mehr an Popularit\"at als Kommunikationsmittel
%% unter Internet-Nutzern gewonnen. So wurden Ende 2012 jeden Tag fast
%% eine halbe Milliarde Kurznachrichten weltweit \"uber diesen Service
%% verschickt (vgl. Terdiman, \cite{terdiman}), was Twitter per se zu
%% einem sehr interessanten Objekt computerlinguistischer Forschung
%% machte.

%% Es erwies sich allerdings bald, dass diese unsch\"atzbare Ressource
%% von Textinformation leider nicht ohne Weiteres analysiert
%% bzw. automatisch verarbeitet werden kann. Grund daf\"ur ist die
%% Tatsache, dass die Besonderheiten des verwendeten Lexikons, das
%% spezielle Markup und allgegenw\"artige Pr\"asenz von Schreibfehlern
%% und Slangausdr\"ucken sich negativ auf die Qualit\"at der Arbeit
%% vorhandener NLP-Werkzeuge auswirken, so dass eine Normalisierung des
%% Eingabetexts vor der Verarbeitung n\"otig ist.

%% Das Thema der Normalisierung von Lingo-Texten ist in der
%% englischsprachigen Literatur schon vor zwei Jahrzehnten angeschnitten
%% und seitdem massiv behandelt worden, was zum Teil aber auch dazu
%% gef\"uhrt hat, dass vorgeschlagene Verfahren sich stark
%% \"uberschnitten haben und schwer voneinander abzugrenzen waren. In
%% unserem Artikel wird versucht, eine Klassifikation existierender
%% Textnormalisierungsverfahren vorzunehmen, wobei auf zwei voneinander
%% unabh\"angige Kriterien -- Segmentierungsl\"ange und Typ der
%% Regelinduktion -- gest\"utzt wird.

%% Im zweiten Teil des Berichts wird eine quantitative und qualitative
%% Analyse von W\"ortern durchgef\"uhrt, die aus Sicht von zwei weit
%% verbreiteten, frei verf\"ugbaren Textverarbeitungsprogrammen
%% \texttt{TreeTagger} (Schmid, \cite{schmid}) und \texttt{GNU Hunspell}
%% als unbekannt klassifiziert waren. Das Ziel dieser Analyse ist
%% aufzuzeigen, welche sprachlichen Prozesse oder Erscheinungen zur
%% Abwesenheit des jeweiligen Wortes im maschinenlesbaren Lexikon
%% gef\"uhrt haben und wie die prozentuelle Verteilung dieser
%% Erscheinungen aussieht, d.h. welche Ph\"anomene am meisten unbekannte
%% Vokabeln produziert haben.

%% Im abschlie\ss{}enden Teil stellen wir eine Reihe von automatischen
%% Verfahren vor, mit deren Hilfe die Prozentrate von unbekannten
%% W\"ortern in Tweets um bis zu 9~\% gesenkt werden kann, indem vor
%% allem Twitter-spezifische Ph\"anomene wie Benutzernamen, Hyperlinks,
%% Hashtags, Prolongationen von Buchstaben usw. behandelt werden.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{}
%% \bibitem[2012]{terdiman} Terdiman, D.: %
%%   Report: Twitter hits half a billion tweets a day. %
%%   Unter \url{http://timmurphy.org/2009/07/22/line-spacing-in-latex-documents/},
%%   [abgerufen am: 26.02.2013].

\bibitem[2006]{aw} Aw, A., Zhang, M., Xiao ,J., Su, J.:
  Lexical Normalization of Short Text Messages: Makn Sens a
  \#{}twitter.
  A Phrase-based Statistical Model for {SMS} Text Normalization.
  In COLING/ACL Main Conference Poster Sessions,
  Seiten 33--40.
  (2011)

\bibitem[2011]{han} Han, B., Baldwin T.:
  Lexical Normalization of Short Text Messages: Makn Sens a
  \#{}twitter.
  In Proceedings of the 49th Annual Meeting of the Association
  for Computational Linguistics: Human Language Technologies (ACL
  HLT). Seiten 368--378.
  (2011)

\bibitem[2011]{clark} Clark E., Araki, K.:
  Text Normalization in Social Media: Progress, Problems
  and Applications for a Pre-processing System of Casual
  English.
  In Pacific Association for Computational Linguistics
  (PACLING)
  (2011)

\bibitem[2010]{kaufman} Kaufman M.:
  Syntactic normalization of twitter messages.
  International Conference on Natural Language Processing
  (2010)

\bibitem[1994]{schmid} Schmid, H.:
  Probabilistic Part-of-Speech Tagging Using Decision Trees.
  International Conference on New Methods in Language Processing.
  (1994)
\end{thebibliography}
\end{document}

### 2013-07-25 darmstadt_gscl_2013/article_twitter_normalization.tex
material and paper draft for darmstadt workshop added

\documentclass[citeauthoryear]{llncs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{paralist} % for inparaenum
\usepackage{multirow} % for multirow
\usepackage{tabularx} % for centering in table
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\totaloov}{\% of total OOVs}
\newcommand{\uniqoov}{\% of unique OOVs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{headings}  % switches on printing of running heads
\title{MT @HanBaldwin: Fightin OOVs in German \#twitter}
\titlerunning{Makn Sens a Germa \#twitter}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Max Mustermann \and Otto Normalverbraucher \and John Doe}
%
\authorrunning{xxx et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Max Mustermann, Otto Normalverbraucher, John Doe}
%
\institute{University of Universe, Milky Way City,\\
  \email{max@example.com, %
    otto@example.com, %
    john@example.com},\\
  WWW home page: \texttt{http://www.example.com}}

\maketitle              % typeset the title of the contribution

\begin{abstract}
  %% Since its launch in March 2006 and until today Twitter constantly
  %% gained more and more popularity as a communication means among the
  %% Internet users. As of the end of 2012, approximately half a billion
  %% messages were published every day by using its services (Terdiman,
  %% \cite{terdiman}).  But, unfortunately, this abundant resource of
  %% textual information can not be exploited to the full extent by
  %% solely relying on standard NLP frameworks, because misspellings,
  %% active usage of slang, and various other aspects of texting language
  %% significantly decrease the chances of successful automatic analysis
  %% of this kind of data.

  This article gives an overview of existing approaches to the
  problems of out-of-vocabulary tokens and noisiness effects in
  natural language texts. Additionally, quantitative and qualitative
  analyses of unknown words in German tweets are conducted in order to
  assess how widely this textual genre differs from standard language
  texts with regard to noisiness phenomena. Subsequently, we present a
  set of ad-hoc techniques which are supposed to tackle some of the
  most prominent disturbing effects and show how this set of
  techniques allows us to lower the average rate of out-of-vocabulary
  tokens in Twitter messages.

  \keywords{twitter, social media, text normalization, spelling
    correction}
\end{abstract}
%
\section{Introduction}
When Jack Dorsey, the present CEO of Twitter Inc., was sending the
very first tweet on March 21, 2006 (Dorsey, \cite{dorsey}), he
probably could not imagine that a few years later presidents and
government officials would use this service to communicate with their
voters and the Pope would be posting short messages holding an iPad in
his hand (Pianigiani, \cite{nyt:pope}). Yet another thing that Jack
Dorsey was apparently not aware of at that moment, was the fact that
his message -- ``just setting up my twttr'' -- already contained a
word which was unknown to the majority of NLP applications existing at
that time, and that there would be many of such words in future
causing a lot of headache to natural language specialists.

Though the problem of out-of-vocabulary (OOV) words and its related
task of text normalization have been extensively studied in
computational linguistics since as early as the late 1950s
(cf. Petersen, \cite{petersen}) and were certainly anything but new at
the time when mobile communication emerged, it were small messages
that revived interest in this area in the past two decades.

%% One of the first scientific milestones which marked the renaissance of
%% OOV studies in CL was a comprehensive article by Karen Kukich
%% published in the renowned ACM journal on December 4-th 1992
%% \cite{kukich}. By an interesting coincidence, just exactly one day
%% before that, a British engineer called Neil Papworth had sent the
%% world's first ever SMS-message \cite{guardian:sms}. But in contrast to
%% Papworth's SMS which only said ``Merry Christmas'' to one of his
%% friends, Kukich's work comprised more than 60 pages and provided a
%% fully-fledged review of the state of the art techniques for dealing
%% with unknown words within the scope of spelling correction programs.

In the next Section we will give a short overview of recent scientific
approaches to the problem of tackling out-of-vocabulary words in
non-standard texts. After that, in Section \ref{error:analysis} we
will analyze which types of text noisiness phenomena are especially
characteristic for German Twitter. Section \ref{normalization} will
subsequently describe an automatic procedure for mitigating some of
the most obvious of those effects. In a concluding step, we will
perform an evaluation of the results of this procedure and give
further suggestions for future research.

\section{Related Work}

Before proceeding with the description of existing methods for noisy
text normalization (NTN) task, we first would like to define the
criteria by which these methods could be classified. It should be
noted that there already exist several classifications of NTN methods
including, for example, Kukich (\cite{kukich}), Kobus et
al. (\cite{kobus}), and Sproat et al. (\cite{sproat}). But all of
these classification attempts seem to have one significant
shortcoming, namely they try to involve several independent criteria
within one classification scheme.

Kukich (\cite{kukich}), for example, divided NTN techniques into six
classes:
\begin{enumerate}
\item minimum edit distance techniques;
\item similarity key techniques;
\item rule-based techniques;
\item \textit{n}-gram based techniques;
\item probabilistic techniques;
\item neural nets.
\end{enumerate}

Kobus (\cite{kobus}), on the contrary, referred to existing NTN
methods as \textit{metaphors} and split them into the following
three groups:
\begin{enumerate}
\item ``spell checking'' metaphor;
\item ``translation'' metaphor;
\item ``speech recognition'' metaphor.
\end{enumerate}

Though both divisions seem to be justified to some extent, it is
difficult to determine using them whether an NTN approach that detects
and restores incorrectly spelled words on the basis of phonetical
\textit{n}-gram statistics should fall into \textit{n}-gram based,
probabilistic, spell checking or speech recognition class.

We instead suggest using two separate types of criteria which are
unrelated to each other and characterize NTN approaches from different
points of view.

The first criterion is \emph{segmentation level}. It depends primarily
on the maximal length of syntagmatic segments which are used
\begin{inparaenum}[\itshape a\upshape)]
\item to infer in-vocabulary (IV) equivalents for OOV
  tokens\label{candidate:inferring} and
\item to choose the most probable variant\label{candidate:selection}
  among multiple possible suggestions\footnote{For the cases, when
    segments of different lengths are used for tasks
    \ref{candidate:inferring} and \ref{candidate:selection}, we note
    it explicitly in our classification on which segmentation length
    each subtask relies.}.
\end{inparaenum} For this criterion we propose division into following
classes:
\begin{enumerate}
  \item graphematic\footnote{Depending on whether phonetical
    information is involved or not at this level, this class could be
    further divided into a phonographematic and purely graphematic
    subclasses.};
  \item lexical;
  \item phrasal.
\end{enumerate}
Each broader level of this hierarchy is also supposed to either
incorporate or ignore information provided by its narrower
subsegments. In this way, we only need to mention one (the broadest)
hierarchical class for the cases when multiple segmentation levels are
involved by some techniques.

The second classification criterion regards the \emph{type of
  information induction} that was used to devise the correction
directives. This leads us to the usual NLP-taxonomy which divides all
approaches into:
\begin{enumerate}
  \item rule-based;
  \item statistical\footnote{Depending on the type of training data
    required, this class is usually divided into unsupervised,
    semi-supervised, and supervised groups.};
  \item and hybrid ones.
\end{enumerate}

Equipped with these two criteria, we could now proceed to the
description of main scientific works on NTN task which were done in
recent years.

It is worthwile noting that many approached to NTN, especially the
earlier ones, were heavily influenced by the idea of noisy channel
model. The underlying notion of this model was that observed sentences
had to be considered as corrupted versions of some original language
signals. In order to restore the undistorted signal, one had to come
up with two probabilistic submodels: the error model (one which caused
the corruption) and the language model (one which reflected the nature
of initial signal source). To these works belong Brill and Moore
(\cite{brill}), Sproat et al. (\cite{sproat}), Toutanova and Moore
(\cite{toutanova}), Clark (\cite{alexander-clark}), Choudhury et
al. (\cite{choudhury}), Cook and Stevenson (\cite{cook}), Beaufort et
al. (\cite{beaufort}) etc. The majority of these methods used either
purely graphematic (Brill and Moore, \cite{brill}; Sproat et al.,
\cite{sproat}; Clark, \cite{alexander-clark}) or phonographematic
segmentation (Toutanova and Moore \cite{toutanova}; Choudhury et al.,
\cite{choudhury}; Cook and Stevenson, \cite{cook}) for error
models. For language model, normally phrasal segments (word
\textit{n}-grams) were used. From the point of view of information
induction almost all of these techniques could be characterized as
supervised statistical, with the exception of Cook and Stevenson
(\cite{cook}) who claimed to use an unsupervised technique.

The raising influence and improved quality of machine translation
tools and applications in the 2000s lead to the development of NTN
technologies which used broader levels of segmentation. In \cite{aw},
Aw et al. suggested a supervised statistical system for normalization
of SMS-messages. Their system operated exclusively on phrasal level. A
few years later, Clark and Araki (\cite{clark-araki}) described a
purely rule-based phrasal technique.

As stated by Kobus et al. (\cite{kobus}), NTN methods relying on
either graphematic or phrasal segments usually revealed complementary
strengths and weaknesses. This notion led NLP scientists to the idea
that incorporating multiple levels of language in one NTN system could
improve the total quality of the system as a whole since different
levels would benefit from each other. As a consequence of this notion,
a wealth of combined techniques emerged in the past few years. Among
these we should especially mention Kobus et al. (\cite{kobus}),
Kaufmann (\cite{kaufmann}), Han and Baldwin (\cite{han}), and Oliva et
al. (\cite{oliva}). The system suggested by Kobus et
al. (\cite{kobus}), for example, used a hybrid phrasal approach in a
pre-processing step and subsequently fed the output of this
pre-processing into a finite state transducer (FST). The FST performed
a phonographematic segmentation of data and derived normalization
equivalents on the basis of statistical inference. Another approach
proposed by Kaufmann (\cite{kaufmann}) first used unambigous lexical
mappings and straightforward graphematic correction rules to reduce
the noisiness effects and then redirected pre-normalized input to a
statistical phrasal MT system.

Eventually, in \cite{han}, an article called ``Lexical Normalization
of Short Text Messages: Makn Sens a \#{}twitter'' was published by Han
and Baldwin. In this article the authors separated the tasks of
identification of ill-formed words and finding appropriate correction
for them. For the former problem, they first generated a confusion set
(CS) for each word unknown to \texttt{GNU aspell}. Based on this set,
the decision was made whether a particular word had to be corrected or
regarded as vlid. Subsequently, for words identified as ill-formed the
most probable restoration candidate was chosen from CS by combining
features resulting from dictionary lookup, analysis of surrounding
context, and estimating word similarity to each proposed correction
variant. According to authors' estimations, this combination allowed
them to outperform most of the NTN methods existing at that time.

In our next section will also perform quantitive and qualitative
analyses of unknown words in German Twitter texts in order to assess
whether and to what extent the problem of ill-formed words is relevant
for them. Relying on these analyses we then will suggest a set of
ad-hoc techniques which could help one lower the average rate of
incorrectly spelled words in this kind of text.

\section{Analysis of Unknown Tokens}\label{error:analysis}

In order to estimate the percentage of unknown words in Twitter
messages, we randomly selected 10,000 tweets from a previously
collected corpus, split them into sentences and tokenized using social
media aware tokenizer by Christopher Potts
\footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}.
After skipping all words which did not contain any alphabetic
character or consisted only of a single letter, we
obtained a list of 129,146 tokens. As reference systems for dictionary
lookup we used open source spell checking program
\texttt{hunspell}\footnote{Ispell Version 3.2.06 (Hunspell Version
  1.3.2); dictionary de\_DE.} and publicly available part-of-speech
tagger \texttt{TreeTagger}\footnote{Version 3.2 with German parameter
  file UTF-8.} (Schmid, \cite{schmid}).

Out of this token list, 26,018 tokens (20.15~\%) were regarded as
unknown by \texttt{hunspell} and 28,389 tokens (21.98~\%) were
considered as OOV by \texttt{TreeTagger}. We also performed similar
estimations after leaving only unique words without taking into
account their frequencies. This allowed us to shrink our initial token
list by four times to 32,538 unique tokens. The relative rate of
unknown words raised as expected and run up to 46.96~\% for
\texttt{hunspell} and 58.24~\% for \texttt{TreeTagger}.

Here once again the question of classification arose but this time
with regard to the reasons, why different tokens could have been
omitted from corresponding applications' dictionaries. In this
respect, division into following groups seemed to be appropriate for
us:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionary
    (MRD)}. To this group we counted words of basic vocabulary which
    did not get into applications' MRD either because they supposedly
    were rare or because they did not exist at the time when
    dictionaries were created. Another reason for inclusion in this
    type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are usually deliberately not included in MRDs
    due to impossibility to cover these classes fully;\label{dict}
  \item \textbf{Unintended sloppiness of user's input}. In the scope
    of this group we considered unintended typos including unexpected
    truncation of words at the end of Twitter messages\footnote{As is
      generally known, Twitter imposes a strong restriction on the
      length of posted messages which can be no longer than 140
      characters. Upon exceeding this length, tweets get automatically
      truncated.};\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language texts but were perfectly valid
    terms in the domain of web discourse and Twitter
    communication.\label{style}
\end{enumerate}

In order to see how out-of-vocabulary words were distributed among and
within these 3 major groups, we manually analyzed all OOV tokens which
appeared in text more than once and also looked at 1,000 randomly
selected hapax legomena. The results of these estimations are shown
and explained below.

We subdivided group \ref{dict} into the following subgroups:
\begin{enumerate}
\item regular German words, e.g. \textit{aufm}, \textit{losziehen};\label{regular}
\item compounds, e.g.  \textit{Altwein}, \textit{Amtsapothekerin};\label{compound}
\item abbreviations, e.g. \textit{NBG}, \textit{OL};\label{abbr}
\item interjections, e.g.  \textit{aja}, \textit{haha};\label{inj}
\item named entities, with subclasses:\label{ne}
  \begin{enumerate}
  \item persons, e.g.  \textit{Ahmadinedschad}, \textit{Schweiger};
  \item geographic locations, e.g.  \textit{Biel}, \textit{Limmat};
  \item companies, e.g. \textit{Apple}, \textit{Facebook};
  \item product names, e.g. \textit{iPhone}, \textit{MacBook};
  \end{enumerate}
\item neologisms, with subclasses:\label{neolog}
  \begin{enumerate}
    \item newly coined German terms, e.g. \textit{entfolgen},
      \textit{geskypt};\label{new}
    \item loanwords, e.g. \textit{Community},
      \textit{Stream};\label{loan}
  \end{enumerate}
\item and, finally, foreign words like \textit{is} or \textit{now}
  which in contrast to \ref{loan} were not mentioned in any existing
  German lexicons nor they complied with inflectional rules of German
  grammar.\label{fw}
\end{enumerate}
Though this division is admittedly arbitrarily to a certain degree and
involves different linguistic criteria simultaneously, the underlying
notion for it was simple. Valid words could have been omitted from an
MRD either due to the limitation of developers' capacities (group
\ref{regular}), active word formation or lexical productivity of the
language (groups \ref{compound} through \ref{new}) or also due to
language's openness to foreign language systems (groups \ref{loan} and
\ref{fw}).

In Table \ref{table:mrd} percentage figures for each of the above
subgroups are shown. We have considered OOV-distribution for both
\texttt{hunspell} and \texttt{TreeTagger}. For both of them we
estimated the percentage of particular subclass with regard to the
total number of occurrences of OOV-tokens (column ``\totaloov{}'') as
well as with regard to their percentage in the list of unique OOVs
(column ``\uniqoov{}'') without taking into account their frequencies.

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``objective limitedness of MRD''\label{table:mrd}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    regular German words & 7.88 & 8.85 &  & \\
    compounds & 1.22 & 2.42 &  & \\
    abbreviations & 4.12 & 4.91 &  & \\
    interjections & 5.93 & 4.47 &  & \\
    person names & 4.79 & 6.45 &  & \\
    geographic locations & 1.51 & 2.53 &  & \\
    company names & 2.26 & 2.8 &  & \\
    product names & 2.08 & 2.49 &  & \\
    newly coined terms & 1.22 & 1.24 &  & \\
    loanwords & 3.72 & 4.05 &  & \\
    foreign words & 11.68 & 14 &  & \\\hline
    {\bfseries total} & 46.41 & 54.21 &  & \\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Similarly to class \ref{dict} we subdivided the group of misspellings
into the following subgroups:
\begin{enumerate}
  \item insertion;
  \item deletion;
  \item substitution;
\end{enumerate}
according to the kind of operation which led to a particular spelling
mistake. The statistics on distribution of these subgroups is shown in
Table \ref{table:spell}.
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``unintended sloppiness of user's input''\label{table:spell}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    insertion &  &  &  & \\
    deletion &  &  &  & \\
    substitution &  &  &  & \\\hline
    {\bfseries total} &  &  &  & \\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``stylistic specifics of text genre''}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}} & %
    \multicolumn{2}{c}{\texttt{hunspell}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    hashtags &  &  &  & \\
    @-tokens &  &  &  & \\
    links &  &  &  & \\
    smileys &  &  &  & \\
    slang &  &  &  & \\\hline
    {\bfseries total} &  &  &  & \\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

\section{Text Normalization Procedure}\label{normalization}
\subsection{Replacement of Twitter-Specific Phenomena}
%
\subsection{Restoration of Umlauts}
%
\subsection{Squeezing of Elongated Words}
%
\subsection{Translation of Slang Idioms}
%
\section{Evaluation}\label{evaluation}

\section{Conclusion}\label{concl}

This article provided an overview of exisiting approaches to noisy
text normalization task. Additionally, all mentioned methods were
classified on the basis of two independent criteria. In section
\ref{error:analysis}, we performed qulitative and quantitive analyses
of out-of-vocabulary words in German tweets and suggested a set of
ad-hoc techniques for mitigating their potential negative influence on
natural language processing. This procedure allowed us to reduce the
total OOV rate by ... \% for \texttt{hunspell} and by ... \% for
\texttt{TreeTagger}.

Nevertheless, we should honestly admit that our system still has
potential for development and research, since it mainly addresses only
one of three main groups of OOV tokens. Future directions should
certainly include a more thorough tackling of unintentional spelling
mistakes and especially their most prominent types -- deletions and
substitutions.

Furthemore, a better evalution technique as well as comparison with
other systems are needed for our normalization procedure. On the one
hand, an \textit{extrinsic} evaluation should be performed (cf. Sparck
Jones and Galliers, \cite{sparck}) which means that we not only have
to show how the rate of OOV words goes down but much more how this
lower OOV rate affects the work of the whole NLP system. On the other
hand, we need to assess the quality of our procedure's work on the
basis of metrics used by other researchers.

One possible estimation criterion which was used by Aw et
al. (\cite{aw}), Kaufmann (\cite{kaufmann}), Beaufort et
al. (\cite{beaufort}), and Oliva et al. (\cite{oliva}) is the BLEU
score (Papineni et al., \cite{papineni}). Another possibility would be
to use the Word (WER) and Sentence Error Rates (SER) as suggested by
Kobus et al. (\cite{kobus}). However, an obvious difficulty that we
already encountered here is that both metrics highly rely on a
subjective notion of the look of a ``normalized'' message. While the
BLEU score could be an approriate criterion for normalization of
messages like ``i luv ma mather and wd do evrythin 4 her'' which in
fact looks like as if it were not English. But such highly distorted
tweets are rather atypical for German. In this regard, WER and SER
could be considered as more appropriate measurement criteria. But
these metrics once again are rather dealing with spelling mistakes and
would highly depend on whether one, for example, would consider the
hash sign in a hashtag as an error.

\subsection*{\ackname}

This work was financially supported by ... as part of collaborative
project ``...''. The authors are also thankful to ... for help with
the analysis of data.

%
% ---- Bibliography ----
%
\bibliographystyle{splncs}
\begin{thebibliography}{}
\bibitem[2006]{aw}
  Aw, A., Zhang, M., Xiao, J., Su, J.: %
  A Phrase-based Statistical Model for {SMS} Text Normalization. %
  COLING/ACL (2006) 33--40 %

\bibitem[2002]{bangalore}
  Bangalore, S., Murdock, V., Riccardi, G.: %
  Bootstrapping Bilingual Data using Consensus Translation for a %
  Multilingual Instant Messaging System. %
  COLING (2002) 33--40 %

\bibitem [2010]{beaufort}
  Beaufort, R., Roekhaut, S., Cougnon, L. A.,  Fairon, C.: %
  A Hybrid Rule/Model-Based Finite-State Framework for %
  Normalizing SMS Messages. %
  ACL (2010) 770--779 %

\bibitem[2000]{brill}
  Brill, E., Moore, R. C.: %
  An improved model for noisy channel spelling correction. %
  ACL %
  (2000) 286--293 %

\bibitem[2003]{alexander-clark}
  Clark, A.: %
  Pre-processing very noisy text. %
  In Proceedings of Workshop on Shallow Processing of Large Corpora. %
  (2003) 12--22

\bibitem[2007]{choudhury}
  Choudhury, M., Saraf, R., Jain, V., Mukherjee, A., Sarkar, S., Basu %
  A.: %
  Investigation and Modeling of the Structure of Texting Language. %
  International Journal of Document Analysis and Retrieval: Special %
  Issue on Analytics of Noisy Text. {\bfseries 10} %
  (2007) 157--174 %

\bibitem[2011]{clark-araki}
  Clark, E., Araki, K.: %
  Text Normalization in Social Media: Progress, Problems and %
  Applications for a Pre-processing System of Casual English. %
  PACLING. Procedia - Social and Behavioral Sciences {\bfseries 27} %
  (2011) 2--11

\bibitem[2009]{cook}
  Cook, P., Stevenson, S.: %
  An unsupervised model for text message normalization, %
  Proceedings of the Workshop on Computational Approaches %
  to Linguistic Creativity. %
  CALC '09. (2009) 71--78

\bibitem[2006]{dorsey}
  Dorsey, J.: %
  "just setting up my twttr". %
  \url{https://twitter.com/jack/status/20} %
  Accessed February 26, 2013. (2006)

\bibitem[2011]{han}
  Han, B., Baldwin, T.: %
  Lexical Normalization of Short Text Messages: Makn Sens %
  a \#{}twitter. %
  ACL HLT. %
  (2011) 368--378

\bibitem[2008]{jurafsky}
  Jurafsky, D., Martin, J. H.: %
  Speech and Language Processing. 2nd Edition. %
  Prentice Hall (2008) 129, 323

\bibitem [2010]{kaufmann}
  Kaufmann, M.: %
  Syntactic normalization of twitter messages. %
  The 8-th International Conference on Natural Language Processing. %
  (2010)

\bibitem [2008]{kobus}
  Kobus, C., Yvon, F., Damnati, G.: %
  Normalizing {SMS}: are Two Metaphors Better than One? %
  COLING (2008) 441--448

\bibitem[1992]{kukich}
  Kukich, K.: %
  Techniques for Automatically Correcting Words in Text. %
  ACM Computing Surveys {\bfseries 24/4} (1992) 378--439

\bibitem[2012]{guardian:sms}
  McVeigh, T.: %
  Text messaging turns 20. %
  The Observer (December 1, 2012)

\bibitem [2013]{oliva}
  Oliva, J., Serrano, J. I., and Del Castillo, M. D., %
  and Igesias, Á.: %
  A {SMS} normalization system integrating multiple %
  grammatical resources. %
  Natural Language Engineering. %
  (2013) 121--141 %

\bibitem [2002]{papineni}
  Papineni, K., Roukos, S., Ward, T., Zhu, W.-J.: %
  Bleu: a Method for Automatic Evaluation of Machine Translation. %
  ACL (2002) 311--318

\bibitem [1980]{petersen}
  Petersen, L. J.: %
  Computer Programs for Detecting and Correcting Spelling Errors. %
  Communications of the ACM {\bfseries 23/ 12} (1980) 676--687

\bibitem[2012]{nyt:pope}
  Pianigiani, G., Donadio, R.: %
  Twitter Has A New User: The Pope. %
  The New York Times. Page A6. (December 4, 2012)

\bibitem[2001]{sproat}
  Sproat, R., Black, A. W., Chen, S. F., Kumar, S., %
  Ostendorf, M., Richards, Ch.: %
  Normalization of non-standard words. %
  Computer Speech \& Language, {\bfseries 15/3} (2001) 287--333

\bibitem[1994]{schmid}
  Schmid, H.: %
  Probabilistic Part-of-Speech Tagging Using Decision Trees. %
  In Proceedings of International Conference on New Methods in %
  Language Processing. (1994)

\bibitem[1996]{sparck}
  Sparck Jones, K., Galliers, J. R.: %
  Evaluating Natural Language Processing Systems. %
  An Analysis and Review. Lecture Notes in Computer %
  Science 1083, Springer. (1996)

\bibitem[2012]{terdiman}
  Terdiman, D.: %
  Report: Twitter hits half a billion tweets a day. %
  \url{http://timmurphy.org/2009/07/22/line-spacing-in-latex-documents/},%
  Accessed February 26, 2013. (2012)

\bibitem[2002]{toutanova}
  Toutanova, K., Moore, R. C.: %
  Pronunciation Modeling for Improved Spelling Correction. %
  ACL (2002) 144--151

\end{thebibliography}
%
% ---- End of Bibliography ----
%
\end{document}

### 2013-07-26 darmstadt_gscl_2013/article_twitter_normalization.tex
bibliography dir added, a few lines updated

@@
 %
-\author{Max Mustermann \and Otto Normalverbraucher \and John Doe}
+\author{Uladzimir Sidarenka \and Tatjana Schef\/f\/ler \and Manfred Stede}
 %
-\authorrunning{xxx et al.} % abbreviated author list (for running head)
+\authorrunning{Sidarenka et al.} % abbreviated author list (for running head)
 %
 %%%% list of authors for the TOC (use if author list has to be modified)
-\tocauthor{Max Mustermann, Otto Normalverbraucher, John Doe}
+\tocauthor{Uladzimir Sidarenka, Tatjana Schef\/f\/ler, Manfred Stede}
 %
-\institute{University of Universe, Milky Way City,\\
-  \email{max@example.com, %
-    otto@example.com, %
-    john@example.com},\\
-  WWW home page: \texttt{http://www.example.com}}
+\institute{University of Potsdam,\\
+  \email{{uladzimir.sidarenka@uni-potsdam.de,
+      tatjana.scheffler@uni-potsdam.de,
+      manfred.stede@uni-potsdam.de},\\ WWW home page:
+    \texttt{http://www.ling.uni-potsdam.de/acl-lab/SocMedia/main.htm}}}
 
@@
 
-  This article gives an overview of existing approaches to the
-  problems of out-of-vocabulary tokens and noisiness effects in
-  natural language texts. Additionally, quantitative and qualitative
-  analyses of unknown words in German tweets are conducted in order to
-  assess how widely this textual genre differs from standard language
-  texts with regard to noisiness phenomena. Subsequently, we present a
-  set of ad-hoc techniques which are supposed to tackle some of the
-  most prominent disturbing effects and show how this set of
-  techniques allows us to lower the average rate of out-of-vocabulary
-  tokens in Twitter messages.
+  This article gives an overview of existing approaches to the problem
+  of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
+  language texts. These approaches are classified with regard to the
+  size of text spans and knowledge inference mechanisms which they use
+  in their work. Subsequently, quantitative and qualitative analyses
+  of unknown words are conducted on German Twitter messages, in order
+  to see how relevant the OOV issue is for this particular kind of
+  micro-texts and to determine which peculiarities are especially
+  characteristic for them. In a concluding step, we present a set of
+  ad-hoc techniques which are supposed to tackle some of the most
+  prominent disturbing effects found during the analyses and show how
+  this set of techniques helps us to lower the average rate of
+  out-of-vocabulary tokens in Twitter messages thereby improving their
+  automatic Part-of-speech tagging quality.
 
@@
 
-Though the problem of out-of-vocabulary (OOV) words and its related
-task of text normalization have been extensively studied in
+Though the problem of out-of-vocabulary (OOV) words and its closely
+related task of textual normalization have been extensively studied in
 computational linguistics since as early as the late 1950s
@@
 the time when mobile communication emerged, it were small messages
-that revived interest in this area in the past two decades.
+that revived interest in this research area in the past two
+decades.
+
+Starting from the second half of 1990-ies, the rise of SMS messages,
+growing popularity of online chats and launch of social networks lead
+to a significant boost in the number of publications on preprocessing
+casually typed texts. But despite this increased number of researches,
+the main focus of the majority of these works was on English data with
+a few exceptions of works on Spanish (Oliva et al., \cite{oliva}) and
+French (Beaufort et al., \cite{beaufort}).
 
@@
 In the next Section we will give a short overview of recent scientific
-approaches to the problem of tackling out-of-vocabulary words in
-non-standard texts. After that, in Section \ref{error:analysis} we
-will analyze which types of text noisiness phenomena are especially
-characteristic for German Twitter. Section \ref{normalization} will
-subsequently describe an automatic procedure for mitigating some of
-the most obvious of those effects. In a concluding step, we will
-perform an evaluation of the results of this procedure and give
-further suggestions for future research.
+approaches to the problem of out-of-vocabulary words in non-standard
+texts. After that, in Section \ref{error:analysis} we will analyze
+which types of noisiness phenomena are especially characteristic for
+German Twitter. Section \ref{normalization} will subsequently describe
+an automatic procedure for mitigating some of the most obvious of
+those effects. In a concluding step, we will perform an evaluation of
+the results of this procedure and give further suggestions for future
+research.
 
@@
 Before proceeding with the description of existing methods for noisy
-text normalization (NTN) task, we first would like to define the
-criteria by which these methods could be classified. It should be
-noted that there already exist several classifications of NTN methods
-including, for example, Kukich (\cite{kukich}), Kobus et
-al. (\cite{kobus}), and Sproat et al. (\cite{sproat}). But all of
-these classification attempts seem to have one significant
-shortcoming, namely they try to involve several independent criteria
-within one classification scheme.
+text normalization (NTN), we first would like to define the criteria
+by which these methods could be classified. It should be noted that
+there already exist several classifications of NTN methods including,
+for example, Kukich (\cite{kukich}), Kobus et al. (\cite{kobus}), and
+Sproat et al. (\cite{sproat}). But all of these classification
+attempts seem to have one common shortcoming, namely they try to
+involve several independent criteria within one classification scheme.
 
@@
 
+\bibitem[2012]{mukherjee}
+  Mukherjee, S., Malu, A., Balamurali, A. R., Bhattacharyya, P.: %
+  TwiSent: A Multistage System for Analyzing Sentiment in Twitter. %
+  In Proceedings of The 21st ACM Conference on Information and %
+  Knowledge Management CIKM 2012, Hawai, (Oct 29 - Nov 2, 2012)
+
+  McVeigh, T.: %
+  Text messaging turns 20. %
+  The Observer (December 1, 2012)
+
 \bibitem [2013]{oliva}

### 2013-07-27 darmstadt_gscl_2013/article_twitter_normalization.tex
slight update of article

@@
   language texts. These approaches are classified with regard to the
-  size of text spans and knowledge inference mechanisms which they use
-  in their work. Subsequently, quantitative and qualitative analyses
-  of unknown words are conducted on German Twitter messages, in order
-  to see how relevant the OOV issue is for this particular kind of
-  micro-texts and to determine which peculiarities are especially
-  characteristic for them. In a concluding step, we present a set of
+  size of text spans and knowledge inference mechanisms which they
+  rely on in their work. Subsequently, quantitative and qualitative
+  analyses of unknown words are conducted on German Twitter messages,
+  in order to show how relevant the OOV and text normalization
+  problems are for this particular kind of micro-texts and what their
+  characteristics are there. In a concluding step, we present a set of
   ad-hoc techniques which are supposed to tackle some of the most
@@
   this set of techniques helps us to lower the average rate of
-  out-of-vocabulary tokens in Twitter messages thereby improving their
-  automatic Part-of-speech tagging quality.
+  out-of-vocabulary tokens in Twitter messages thereby improving the
+  quality of their automatic Part-of-speech tagging.
 
@@
 
-Though the problem of out-of-vocabulary (OOV) words and its closely
-related task of textual normalization have been extensively studied in
+Though the problem of out-of-vocabulary words and its closely related
+task of textual normalization have been extensively studied in
 computational linguistics since as early as the late 1950s
@@
 the time when mobile communication emerged, it were small messages
-that revived interest in this research area in the past two
-decades.
+that revived interest in this research area in the past two decades.
 
-Starting from the second half of 1990-ies, the rise of SMS messages,
-growing popularity of online chats and launch of social networks lead
-to a significant boost in the number of publications on preprocessing
-casually typed texts. But despite this increased number of researches,
-the main focus of the majority of these works was on English data with
-a few exceptions of works on Spanish (Oliva et al., \cite{oliva}) and
-French (Beaufort et al., \cite{beaufort}).
+Starting from the second half of the 1990s, not only the number of
+publications on automatic text correction gradually increased every
+year but also the focus of those researches steadily turned away from
+normalization of manually typed or OCR processed official documents to
+the processing of sloppily created user messages and online chat
+posts. But even despite this increased interest, most of the
+researches still were dealing with only English text data. A few
+exceptions from that are works on French (Beaufort et al.,
+\cite{beaufort}) and Spanish (Oliva et al., \cite{oliva}).
 
-%% One of the first scientific milestones which marked the renaissance of
-%% OOV studies in CL was a comprehensive article by Karen Kukich
+%% One of the first scientific milestones which marked the renaissance
+%% of OOV studies in CL was a comprehensive article by Karen Kukich
 %% published in the renowned ACM journal on December 4-th 1992
@@
 %% before that, a British engineer called Neil Papworth had sent the
-%% world's first ever SMS-message \cite{guardian:sms}. But in contrast to
-%% Papworth's SMS which only said ``Merry Christmas'' to one of his
+%% world's first ever SMS-message \cite{guardian:sms}. But in contrast
+%% to Papworth's SMS which only said ``Merry Christmas'' to one of his
 %% friends, Kukich's work comprised more than 60 pages and provided a
 %% fully-fledged review of the state of the art techniques for dealing
-%% with unknown words within the scope of spelling correction programs.
+%% with unknown words within the scope of spelling correction
+%% programs.
 
-In the next Section we will give a short overview of recent scientific
-approaches to the problem of out-of-vocabulary words in non-standard
-texts. After that, in Section \ref{error:analysis} we will analyze
-which types of noisiness phenomena are especially characteristic for
-German Twitter. Section \ref{normalization} will subsequently describe
-an automatic procedure for mitigating some of the most obvious of
-those effects. In a concluding step, we will perform an evaluation of
-the results of this procedure and give further suggestions for future
-research.
+In this article we are going to provide some more insight about the
+relevance of OOV issues for German language by showing how many
+out-of-vocabulary tokens are found in German online texts on average
+and what kind of linguistic phenomena are main sources of these
+OOVs. The next Section will first give a short overview and provide a
+classification of recent scientific approaches to the problem of
+out-of-vocabulary words in non-standard texts. After that, in Section
+\ref{error:analysis} we will analyze which types of noisiness
+phenomena are especially common in German Twitter. Section
+\ref{normalization} will subsequently describe an automatic procedure
+for mitigating some of the most prominent of those effects. In a
+concluding step, we will perform an evaluation of the results of this
+procedure and give some further suggestions for future research.
 
@@
 by which these methods could be classified. It should be noted that
-there already exist several classifications of NTN methods including,
-for example, Kukich (\cite{kukich}), Kobus et al. (\cite{kobus}), and
-Sproat et al. (\cite{sproat}). But all of these classification
-attempts seem to have one common shortcoming, namely they try to
-involve several independent criteria within one classification scheme.
+there already exist several classifications of NTN approaches
+including, for example, Kukich (\cite{kukich}), Kobus et
+al. (\cite{kobus}), and Sproat et al. (\cite{sproat}). But all of
+these classifications seem to share one significant common
+shortcoming, namely they try to involve several independent criteria
+within one classification scheme.
 
@@
 
-Kobus (\cite{kobus}), on the contrary, referred to existing NTN
-methods as \textit{metaphors} and split them into the following
-three groups:
+Kobus (\cite{kobus}), on the contrary, referred to NTN methods as
+\textit{metaphors} and split them into the following three groups:
 \begin{enumerate}
@@
 and restores incorrectly spelled words on the basis of phonetical
-\textit{n}-gram statistics should fall into \textit{n}-gram based,
+\textit{n}-gram statistics should fall into the \textit{n}-gram based,
 probabilistic, spell checking or speech recognition class.
 
-We instead suggest using two separate types of criteria which are
-unrelated to each other and characterize NTN approaches from different
-points of view.
+Instead of that, we suggest using two separate types of criteria which
+are unrelated to each other and characterize NTN approaches from
+different points of view.
 
-The first criterion is \emph{segmentation level}. It depends primarily
+The first criterion is \emph{segmentation level}. It primarily depends
 on the maximal length of syntagmatic segments which are used
@@
     it explicitly in our classification on which segmentation length
-    each subtask relies.}.
-\end{inparaenum} For this criterion we propose division into following
+    each of these subtasks relies.}.
+\end{inparaenum} For this criterion we propose division into the following
 classes:
@@
 incorporate or ignore information provided by its narrower
-subsegments. In this way, we only need to mention one (the broadest)
-hierarchical class for the cases when multiple segmentation levels are
-involved by some techniques.
+subsegments. In this way, only one (the broadest) hierarchical class
+needs to be mentioned for the cases when multiple segmentation levels
+are involved by some techniques.
 
 The second classification criterion regards the \emph{type of
-  information induction} that was used to devise the correction
+  information induction} that is used to devise the correction
 directives. This leads us to the usual NLP-taxonomy which divides all
@@
   \item statistical\footnote{Depending on the type of training data
-    required, this class is usually divided into unsupervised,
+    required, this class is in turn usually divided into unsupervised,
     semi-supervised, and supervised groups.};
@@
 
-Equipped with these two criteria, we could now proceed to the
-description of main scientific works on NTN task which were done in
-recent years.
+Equipped with these two criteria, it should now be easier to get a
+clear picture of the development and recent tendencies in NTN
+research.
 
-It is worthwile noting that many approached to NTN, especially the
+It is worthwile noting that many approaches to NTN, especially the
 earlier ones, were heavily influenced by the idea of noisy channel
 model. The underlying notion of this model was that observed sentences
-had to be considered as corrupted versions of some original language
-signals. In order to restore the undistorted signal, one had to come
-up with two probabilistic submodels: the error model (one which caused
-the corruption) and the language model (one which reflected the nature
-of initial signal source). To these works belong Brill and Moore
-(\cite{brill}), Sproat et al. (\cite{sproat}), Toutanova and Moore
-(\cite{toutanova}), Clark (\cite{alexander-clark}), Choudhury et
-al. (\cite{choudhury}), Cook and Stevenson (\cite{cook}), Beaufort et
-al. (\cite{beaufort}) etc. The majority of these methods used either
-purely graphematic (Brill and Moore, \cite{brill}; Sproat et al.,
-\cite{sproat}; Clark, \cite{alexander-clark}) or phonographematic
-segmentation (Toutanova and Moore \cite{toutanova}; Choudhury et al.,
-\cite{choudhury}; Cook and Stevenson, \cite{cook}) for error
-models. For language model, normally phrasal segments (word
-\textit{n}-grams) were used. From the point of view of information
-induction almost all of these techniques could be characterized as
-supervised statistical, with the exception of Cook and Stevenson
-(\cite{cook}) who claimed to use an unsupervised technique.
+had to be considered as corrupted versions of their respective
+original language signals. In order to restore the undistorted signal,
+one had to come up with two probabilistic submodels: the error model
+(one which caused the corruption) and the language model (one which
+reflected the nature of initial signal source). To these works belong
+Brill and Moore (\cite{brill}), Sproat et al. (\cite{sproat}),
+Toutanova and Moore (\cite{toutanova}), Clark
+(\cite{alexander-clark}), Choudhury et al. (\cite{choudhury}), Cook
+and Stevenson (\cite{cook}), Beaufort et al. (\cite{beaufort})
+etc. The majority of these methods used either purely graphematic
+(Brill and Moore, \cite{brill}; Sproat et al., \cite{sproat}; Clark,
+\cite{alexander-clark}) or phonographematic segmentation (Toutanova
+and Moore \cite{toutanova}; Choudhury et al., \cite{choudhury}; Cook
+and Stevenson, \cite{cook}) for error models. For language model,
+normally phrasal segments (word \textit{n}-grams) were used. From the
+point of view of information induction almost all of these techniques
+could be characterized as supervised statistical, with the exception
+of Cook and Stevenson (\cite{cook}) who claimed to use an unsupervised
+technique.
 
@@
 
-In our next section will also perform quantitive and qualitative
+In the next Section will also perform quantitive and qualitative
 analyses of unknown words in German Twitter texts in order to assess
@@
     interjections) which are usually deliberately not included in MRDs
-    due to impossibility to cover these classes fully;\label{dict}
-  \item \textbf{Unintended sloppiness of user's input}. In the scope
+    due to impossibility to fully cover these classes;\label{dict}
+  \item \textbf{Unintended sloppiness of users' input}. In the scope
     of this group we considered unintended typos including unexpected
@@
       characters. Upon exceeding this length, tweets get automatically
-      truncated.};\label{spell}
+      truncated to maximal allowed length.};\label{spell}
   \item \textbf{Stylistic specifics of text genre}. This group
@@
   which in contrast to \ref{loan} were not mentioned in any existing
-  German lexicons nor they complied with inflectional rules of German
+  German lexicons and did not comply with inflectional rules of German
   grammar.\label{fw}
@@
   \caption{Distribution of OOV words belonging to the class
-    ``unintended sloppiness of user's input''\label{table:spell}}
+    ``unintended sloppiness of users' input''\label{table:spell}}
   \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}

### 2013-07-27 darmstadt_gscl_2013/article_twitter_normalization.tex
minor update

@@
     comprised words which could be considered as illegal from the
-    point of view of standard language texts but were perfectly valid
-    terms in the domain of web discourse and Twitter
+    point of view of standard language but were perfectly valid terms
+    in the domain of web discourse and particularly Twitter
     communication.\label{style}
@@
 \begin{enumerate}
-\item regular German words, e.g. \textit{aufm}, \textit{losziehen};\label{regular}
-\item compounds, e.g.  \textit{Altwein}, \textit{Amtsapothekerin};\label{compound}
+\item regular German words, e.g. \textit{aufm},
+  \textit{losziehen};\label{regular}
+\item compounds, e.g.  \textit{Altwein},
+  \textit{Amtsapothekerin};\label{compound}
 \item abbreviations, e.g. \textit{NBG}, \textit{OL};\label{abbr}

### 2013-07-30 darmstadt_gscl_2013/article_twitter_normalization.tex
small update of related work

@@
 %
-\author{Uladzimir Sidarenka \and Tatjana Schef\/f\/ler \and Manfred Stede}
+\author{Uladzimir Sidarenka \and Tatjana Scheffler \and Manfred Stede}
 %
@@
 %%%% list of authors for the TOC (use if author list has to be modified)
-\tocauthor{Uladzimir Sidarenka, Tatjana Schef\/f\/ler, Manfred Stede}
+\tocauthor{Uladzimir Sidarenka, Tatjana Scheffler, Manfred Stede}
 %
@@
   size of text spans and knowledge inference mechanisms which they
-  rely on in their work. Subsequently, quantitative and qualitative
-  analyses of unknown words are conducted on German Twitter messages,
-  in order to show how relevant the OOV and text normalization
-  problems are for this particular kind of micro-texts and what their
-  characteristics are there. In a concluding step, we present a set of
-  ad-hoc techniques which are supposed to tackle some of the most
-  prominent disturbing effects found during the analyses and show how
-  this set of techniques helps us to lower the average rate of
-  out-of-vocabulary tokens in Twitter messages thereby improving the
-  quality of their automatic Part-of-speech tagging.
+  rely on in their work. Additionally to that, we conduct quantitative
+  and qualitative analyses of unknown words in German Twitter
+  messages, in order to see how relevant the OOV and text
+  normalization problems are for this particular kind of micro-texts
+  and what the characteristics of these OOVs are. In a concluding
+  step, we present a set of ad-hoc techniques which are supposed to
+  tackle some of the most prominent disturbing effects found during
+  these analyses and show how this set of techniques helps us lower
+  the average rate of out-of-vocabulary tokens in Twitter messages and
+  how this lower OOV-rate helps improve the quality of automatic
+  Part-of-speech tagging.
 
@@
 
-Starting from the second half of the 1990s, not only the number of
-publications on automatic text correction gradually increased every
-year but also the focus of those researches steadily turned away from
-normalization of manually typed or OCR processed official documents to
-the processing of sloppily created user messages and online chat
-posts. But even despite this increased interest, most of the
-researches still were dealing with only English text data. A few
-exceptions from that are works on French (Beaufort et al.,
-\cite{beaufort}) and Spanish (Oliva et al., \cite{oliva}).
+%% Starting from the second half of the 1990s, not only the number of
+%% publications on automatic text correction gradually increased every
+%% year but also the focus of those researches steadily turned away from
+%% normalization of manually typed or OCR processed official documents to
+%% the processing of sloppily created user messages and online chat
+%% posts. But even despite this increased interest, most of the
+%% researches still were dealing with only English text data. A few
+%% exceptions from that are works on French (Beaufort et al.,
+%% \cite{beaufort}) and Spanish (Oliva et al., \cite{oliva}).
 
@@
 
-In this article we are going to provide some more insight about the
-relevance of OOV issues for German language by showing how many
-out-of-vocabulary tokens are found in German online texts on average
-and what kind of linguistic phenomena are main sources of these
-OOVs. The next Section will first give a short overview and provide a
-classification of recent scientific approaches to the problem of
-out-of-vocabulary words in non-standard texts. After that, in Section
-\ref{error:analysis} we will analyze which types of noisiness
-phenomena are especially common in German Twitter. Section
-\ref{normalization} will subsequently describe an automatic procedure
-for mitigating some of the most prominent of those effects. In a
-concluding step, we will perform an evaluation of the results of this
-procedure and give some further suggestions for future research.
+%% In this article we are going to provide some more insight about the
+%% relevance of OOV issues for German language by showing how many
+%% out-of-vocabulary tokens are found in German online texts on average
+%% and what kind of linguistic phenomena are main sources of these
+%% OOVs. The next Section will first give a short overview and provide a
+%% classification of recent scientific approaches to the problem of
+%% out-of-vocabulary words in non-standard texts. After that, in Section
+%% \ref{error:analysis} we will analyze which types of noisiness
+%% phenomena are especially common in German Twitter. Section
+%% \ref{normalization} will subsequently describe an automatic procedure
+%% for mitigating some of the most prominent of those effects. In a
+%% concluding step, we will perform an evaluation of the results of this
+%% procedure and give some further suggestions for future research.
+
+In the next Section we will give a short overview of recent scientific
+approaches to the problem of tackling out-of-vocabulary words in
+non-standard texts. After that, in Section \ref{error:analysis} we
+will analyze which types of noisiness phenomena are especially
+characteristic for German Twitter. Section \ref{normalization} will
+subsequently describe an automatic procedure for mitigating some of
+the most prominent of those effects. In a concluding step, we will
+perform an evaluation of the results of this procedure and give
+further suggestions for future research.
 
@@
 there already exist several classifications of NTN approaches
-including, for example, Kukich (\cite{kukich}), Kobus et
-al. (\cite{kobus}), and Sproat et al. (\cite{sproat}). But all of
-these classifications seem to share one significant common
-shortcoming, namely they try to involve several independent criteria
-within one classification scheme.
+including Kukich (\cite{kukich}), Kobus et al. (\cite{kobus}), and
+Sproat et al. (\cite{sproat}).
+%% But all of these classifications seem to share one significant common
+%% shortcoming, namely they try to involve several independent criteria
+%% within one classification scheme.
 
-Kukich (\cite{kukich}), for example, divided NTN techniques into six
-classes:
+So, Kukich (\cite{kukich}), for example, divided NTN techniques into
+six classes:
 \begin{enumerate}
@@
 \end{enumerate}
-
 Kobus (\cite{kobus}), on the contrary, referred to NTN methods as
@@
 and restores incorrectly spelled words on the basis of phonetical
-\textit{n}-gram statistics should fall into the \textit{n}-gram based,
+\textit{n}-gram statistics should fall into \textit{n}-gram based,
 probabilistic, spell checking or speech recognition class.
 
-Instead of that, we suggest using two separate types of criteria which
-are unrelated to each other and characterize NTN approaches from
-different points of view.
+The reason for this confusion is the fact that the above
+classifications both rely on several independent criteria at the same
+time though each of these criteria characterizes an NTN system from a
+different point of view. As a consequence, unambiguous assignment of
+an NTN approach to one particular class often becomes impossible. In
+order to avoid this, we instead suggest using separate classifications
+for each criterion without mixing them.
 
-The first criterion is \emph{segmentation level}. It primarily depends
-on the maximal length of syntagmatic segments which are used
+One of such criteria which in our opinion would be worth a separate
+classification is \emph{segmentation level} which is used
 \begin{inparaenum}[\itshape a\upshape)]
@@
 \item to choose the most probable variant\label{candidate:selection}
-  among multiple possible suggestions\footnote{For the cases, when
-    segments of different lengths are used for tasks
-    \ref{candidate:inferring} and \ref{candidate:selection}, we note
-    it explicitly in our classification on which segmentation length
-    each of these subtasks relies.}.
-\end{inparaenum} For this criterion we propose division into the following
+  among multiple possible ones\footnote{For the cases, when segments
+    of different lengths are used for tasks \ref{candidate:inferring}
+    and \ref{candidate:selection}, we note it explicitly in our
+    classification on which segmentation length each of these subtasks
+    relies.}.
+\end{inparaenum} For this criterion, we propose division into the following
 classes:
@@
 incorporate or ignore information provided by its narrower
-subsegments. In this way, only one (the broadest) hierarchical class
-needs to be mentioned for the cases when multiple segmentation levels
-are involved by some techniques.
+subsegments. In this way, we only need to mention one (the broadest)
+hierarchical class for the cases when multiple segmentation levels are
+involved by some techniques.
 
-The second classification criterion regards the \emph{type of
-  information induction} that is used to devise the correction
-directives. This leads us to the usual NLP-taxonomy which divides all
-approaches into:
+The second criterion regards the \emph{type of information induction}
+that is used to devise the correction rules. This leads us to the
+usual NLP-taxonomy which divides all approaches into:
 \begin{enumerate}
@@
 
-Equipped with these two criteria, it should now be easier to get a
-clear picture of the development and recent tendencies in NTN
-research.
+With these two classifications, we will now try to present and group
+together approaches to the NTN task which appeared in the literature
+in recent years.
 
-It is worthwile noting that many approaches to NTN, especially the
-earlier ones, were heavily influenced by the idea of noisy channel
-model. The underlying notion of this model was that observed sentences
-had to be considered as corrupted versions of their respective
-original language signals. In order to restore the undistorted signal,
-one had to come up with two probabilistic submodels: the error model
-(one which caused the corruption) and the language model (one which
-reflected the nature of initial signal source). To these works belong
-Brill and Moore (\cite{brill}), Sproat et al. (\cite{sproat}),
-Toutanova and Moore (\cite{toutanova}), Clark
-(\cite{alexander-clark}), Choudhury et al. (\cite{choudhury}), Cook
-and Stevenson (\cite{cook}), Beaufort et al. (\cite{beaufort})
-etc. The majority of these methods used either purely graphematic
-(Brill and Moore, \cite{brill}; Sproat et al., \cite{sproat}; Clark,
-\cite{alexander-clark}) or phonographematic segmentation (Toutanova
-and Moore \cite{toutanova}; Choudhury et al., \cite{choudhury}; Cook
-and Stevenson, \cite{cook}) for error models. For language model,
-normally phrasal segments (word \textit{n}-grams) were used. From the
-point of view of information induction almost all of these techniques
-could be characterized as supervised statistical, with the exception
-of Cook and Stevenson (\cite{cook}) who claimed to use an unsupervised
-technique.
+The earlier works on NTN commonly used either purely graphematic or
+phonographematic levels of segmentation for deriving normalization
+variants of incorrectly spelled words. To purely graphematic systems
+belong methods suggested Brill and Moore (\cite{brill}), Sproat et
+al. (\cite{sproat}), and Clark (\cite{alexander-clark}). As
+phonographematic approaches one could regard works done by Toutanova
+and Moore (\cite{toutanova}), Choudhury et al. (\cite{choudhury}),
+Cook and Stevenson (\cite{cook}) etc. With regard to the type of
+information inference, practically all of these methods were
+supervised with the exception of Cook and Stevenson (\cite{cook}) who
+claimed to uns an unsupervised technique.
 
-The raising influence and improved quality of machine translation
-tools and applications in the 2000s lead to the development of NTN
-technologies which used broader levels of segmentation. In \cite{aw},
-Aw et al. suggested a supervised statistical system for normalization
-of SMS-messages. Their system operated exclusively on phrasal level. A
-few years later, Clark and Araki (\cite{clark-araki}) described a
-purely rule-based phrasal technique.
+Starting from the second half of the 2000s, the raising influence and
+improved quality of machine translation tools lead to the development
+of NTN technologies which used broader levels of segmentation. In
+\cite{aw}, Aw et al. suggested a supervised statistical system for
+normalization of SMS-messages which operated on automatically aligned
+phrases. A few years later, Clark and Araki (\cite{clark-araki})
+described a purely rule-based method which used mappings of
+non-standard words and phrases to their corresponding standard
+language forms.
 
-As stated by Kobus et al. (\cite{kobus}), NTN methods relying on
-either graphematic or phrasal segments usually revealed complementary
+As noted by Kobus et al. (\cite{kobus}), NTN methods relying on either
+graphematic or phrasal segments usually revealed complementary
 strengths and weaknesses. This notion led NLP scientists to the idea
-that incorporating multiple levels of language in one NTN system could
-improve the total quality of the system as a whole since different
-levels would benefit from each other. As a consequence of this notion,
-a wealth of combined techniques emerged in the past few years. Among
-these we should especially mention Kobus et al. (\cite{kobus}),
-Kaufmann (\cite{kaufmann}), Han and Baldwin (\cite{han}), and Oliva et
-al. (\cite{oliva}). The system suggested by Kobus et
-al. (\cite{kobus}), for example, used a hybrid phrasal approach in a
-pre-processing step and subsequently fed the output of this
-pre-processing into a finite state transducer (FST). The FST performed
-a phonographematic segmentation of data and derived normalization
-equivalents on the basis of statistical inference. Another approach
-proposed by Kaufmann (\cite{kaufmann}) first used unambigous lexical
-mappings and straightforward graphematic correction rules to reduce
-the noisiness effects and then redirected pre-normalized input to a
-statistical phrasal MT system.
+that by incorporating multiple levels of the language into one NTN
+system the total performace of the system would improve as different
+sources of information would benefit from each other. As a consequence
+of this, a wealth of combined techniques emerged in the past few
+years. Among these we should especially mention the works by Kobus et
+al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), Han and Baldwin
+(\cite{han}), and Oliva et al. (\cite{oliva}). These systems used the
+whole range of segmentation levels from phonographematatic to the
+phrasal one, and also different knowledge inference techniques were
+applied for different levels.
 
-Eventually, in \cite{han}, an article called ``Lexical Normalization
-of Short Text Messages: Makn Sens a \#{}twitter'' was published by Han
-and Baldwin. In this article the authors separated the tasks of
-identification of ill-formed words and finding appropriate correction
-for them. For the former problem, they first generated a confusion set
-(CS) for each word unknown to \texttt{GNU aspell}. Based on this set,
-the decision was made whether a particular word had to be corrected or
-regarded as vlid. Subsequently, for words identified as ill-formed the
-most probable restoration candidate was chosen from CS by combining
-features resulting from dictionary lookup, analysis of surrounding
-context, and estimating word similarity to each proposed correction
-variant. According to authors' estimations, this combination allowed
-them to outperform most of the NTN methods existing at that time.
+%% Eventually, in \cite{han}, an article called ``Lexical Normalization
+%% of Short Text Messages: Makn Sens a \#{}twitter'' was published by Han
+%% and Baldwin. In this article the authors separated the tasks of
+%% identification of ill-formed words and finding appropriate correction
+%% for them. For the former problem, they first generated a confusion set
+%% (CS) for each word unknown to \texttt{GNU aspell}. Based on this set,
+%% the decision was made whether a particular word had to be corrected or
+%% regarded as vlid. Subsequently, for words identified as ill-formed the
+%% most probable restoration candidate was chosen from CS by combining
+%% features resulting from dictionary lookup, analysis of surrounding
+%% context, and estimating word similarity to each proposed correction
+%% variant. According to authors' estimations, this combination allowed
+%% them to outperform most of the NTN methods existing at that time.
 
-In the next Section will also perform quantitive and qualitative
-analyses of unknown words in German Twitter texts in order to assess
-whether and to what extent the problem of ill-formed words is relevant
-for them. Relying on these analyses we then will suggest a set of
-ad-hoc techniques which could help one lower the average rate of
-incorrectly spelled words in this kind of text.
+It should however be noted that almost all of the above methods mainly
+concentrated on only English text data. A few exceptions from that are
+works done by Beaufort et al. (\cite{beaufort}) for French and Oliva
+et al. (\cite{oliva}) for Spanish. To find out which peculiarities of
+ill-formed words are characteristic for German, we will perform a
+quantitive and qualitative analysis of unknown words in German Twitter
+in the next Section to see what kind of NTN techniques would be more
+suitable for handling ill-formed words there.
 

### 2013-07-31 darmstadt_gscl_2013/article_twitter_normalization.tex
statistics updated

@@
   how this lower OOV-rate helps improve the quality of automatic
-  Part-of-speech tagging.
+  part-of-speech tagging.
 
@@
 
-So, Kukich (\cite{kukich}), for example, divided NTN techniques into
-six classes:
+Kukich (\cite{kukich}), for example, divided NTN techniques into six
+classes:
 \begin{enumerate}
@@
 order to avoid this, we instead suggest using separate classifications
-for each criterion without mixing them.
+for each criterion which might characterize an NTN technique.
 
@@
 \item to choose the most probable variant\label{candidate:selection}
-  among multiple possible ones\footnote{For the cases, when segments
-    of different lengths are used for tasks \ref{candidate:inferring}
-    and \ref{candidate:selection}, we note it explicitly in our
-    classification on which segmentation length each of these subtasks
-    relies.}.
+  among multiple possible suggestions\footnote{For the cases, when
+    segments of different lengths are used for tasks
+    \ref{candidate:inferring} and \ref{candidate:selection}, we note
+    it explicitly in our classification on which segmentation length
+    each of these subtasks relies.}.
 \end{inparaenum} For this criterion, we propose division into the following
@@
 \end{enumerate}
-Each broader level of this hierarchy is also supposed to either
-incorporate or ignore information provided by its narrower
-subsegments. In this way, we only need to mention one (the broadest)
-hierarchical class for the cases when multiple segmentation levels are
-involved by some techniques.
+Each broader level of this hierarchy is supposed to either incorporate
+or ignore information provided by its narrower subsegments. In this
+way, we only need to mention one (the broadest) hierarchical class for
+the cases when multiple segmentation levels are involved by some
+techniques.
 
@@
 
-The earlier works on NTN commonly used either purely graphematic or
-phonographematic levels of segmentation for deriving normalization
+The earlier works on NTN commonly relied on either purely graphematic
+or phonographematic levels of segmentation for deriving normalization
 variants of incorrectly spelled words. To purely graphematic systems
@@
 normalization of SMS-messages which operated on automatically aligned
-phrases. A few years later, Clark and Araki (\cite{clark-araki})
+phrases A few years later, Clark and Araki (\cite{clark-araki})
 described a purely rule-based method which used mappings of
@@
 that by incorporating multiple levels of the language into one NTN
-system the total performace of the system would improve as different
-sources of information would benefit from each other. As a consequence
-of this, a wealth of combined techniques emerged in the past few
-years. Among these we should especially mention the works by Kobus et
-al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), Han and Baldwin
-(\cite{han}), and Oliva et al. (\cite{oliva}). These systems used the
-whole range of segmentation levels from phonographematatic to the
-phrasal one, and also different knowledge inference techniques were
-applied for different levels.
+system the total performace of the whole system would improve as
+different sources of information would benefit from each other. As a
+consequence of this, a wealth of combined techniques emerged in the
+past few years. Among these we should especially mention works by
+Kobus et al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), Han and
+Baldwin (\cite{han}), and Oliva et al. (\cite{oliva}). The majority of
+these systems used the whole range of segmentation levels from
+phonographematatic to phrasal one, and in many cases they also applied
+different knowledge inference mechanisms to different levels of the
+language.
 
@@
 It should however be noted that almost all of the above methods mainly
-concentrated on only English text data. A few exceptions from that are
-works done by Beaufort et al. (\cite{beaufort}) for French and Oliva
-et al. (\cite{oliva}) for Spanish. To find out which peculiarities of
-ill-formed words are characteristic for German, we will perform a
-quantitive and qualitative analysis of unknown words in German Twitter
-in the next Section to see what kind of NTN techniques would be more
-suitable for handling ill-formed words there.
+concentrated on only English data. A few exceptions from that are
+approaches suggested by Beaufort et al. (\cite{beaufort}) for French
+and Oliva et al. (\cite{oliva}) for Spanish. To find out which
+peculiarities of ill-formed words are characteristic for German, we
+will perform a quantitive and qualitative analysis of unknown words in
+German Twitter in the next Section in order to see what kind of NTN
+techniques would be more suitable for handling ill-formed words there.
 
@@
 collected corpus, split them into sentences and tokenized using social
-media aware tokenizer by Christopher Potts
+media-aware tokenizer by Christopher Potts
 \footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}.
 After skipping all words which did not contain any alphabetic
-character or consisted only of a single letter, we
-obtained a list of 129,146 tokens. As reference systems for dictionary
-lookup we used open source spell checking program
+character in them or consisted only of a single letter, we obtained a
+list of 129,146 tokens. As reference systems for dictionary lookup we
+used open source spell checking program
 \texttt{hunspell}\footnote{Ispell Version 3.2.06 (Hunspell Version
@@
 
-Here once again the question of classification arose but this time
-with regard to the reasons, why different tokens could have been
-omitted from corresponding applications' dictionaries. In this
-respect, division into following groups seemed to be appropriate for
-us:
+Here once again the question of classification arose. This time with
+regard to the reasons, why different tokens could have been omitted
+from corresponding applications' dictionaries. In this respect,
+division into following groups seemed to be appropriate for us:
 \begin{enumerate}
@@
     were rare or because they did not exist at the time when
-    dictionaries were created. Another reason for inclusion in this
-    type was the belonging of a word to an open lexical or
+    dictionaries were created. Another reason for the inclusion in
+    this type was the belonging of a word to an open lexical or
     part-of-speech class (like, for example, named entities or
-    interjections) which are usually deliberately not included in MRDs
-    due to impossibility to fully cover these classes;\label{dict}
+    interjections) which are often omitted from MRDs due to
+    impossibility to fully cover these classes;\label{dict}
   \item \textbf{Unintended sloppiness of users' input}. In the scope
-    of this group we considered unintended typos including unexpected
-    truncation of words at the end of Twitter messages\footnote{As is
-      generally known, Twitter imposes a strong restriction on the
-      length of posted messages which can be no longer than 140
-      characters. Upon exceeding this length, tweets get automatically
-      truncated to maximal allowed length.};\label{spell}
+    of this second group, we considered unintended typos including
+    unexpected truncation of words at the end of Twitter
+    messages\footnote{As is generally known, Twitter imposes a strong
+      restriction on the length of posted messages which can be no
+      longer than 140 characters. Upon exceeding this length, tweets
+      get automatically truncated to maximal allowed
+      length.};\label{spell}
   \item \textbf{Stylistic specifics of text genre}. This group
     comprised words which could be considered as illegal from the
-    point of view of standard language but were perfectly valid terms
-    in the domain of web discourse and particularly Twitter
-    communication.\label{style}
+    point of view of standard language texts but were perfectly valid
+    terms in the domain of web discourse and Twitter communication in
+    particular.\label{style}
 \end{enumerate}
 
-In order to see how out-of-vocabulary words were distributed among and
-within these 3 major groups, we manually analyzed all OOV tokens which
-appeared in text more than once and also looked at 1,000 randomly
-selected hapax legomena. The results of these estimations are shown
-and explained below.
+In order to see how detected out-of-vocabulary words were distributed
+among and within these 3 major groups, we manually analyzed all OOV
+tokens which appeared in text more than once and also looked at 1,000
+randomly selected hapax legomena. The results of these estimations are
+shown and explained below.
 
@@
     \item newly coined German terms, e.g. \textit{entfolgen},
-      \textit{geskypt};\label{new}
+      \textit{gegoogelt};\label{new}
     \item loanwords, e.g. \textit{Community},
@@
 involves different linguistic criteria simultaneously, the underlying
-notion for it was simple. Valid words could have been omitted from an
+notion for it is simple. Valid words could have been omitted from an
 MRD either due to the limitation of developers' capacities (group
@@
 
-In Table \ref{table:mrd} percentage figures for each of the above
+In Table \ref{table:mrd}, percentage figures for each of the above
 subgroups are shown. We have considered OOV-distribution for both
-\texttt{hunspell} and \texttt{TreeTagger}. For both of them we
-estimated the percentage of particular subclass with regard to the
+\texttt{hunspell} and \texttt{TreeTagger}. For each of them, we
+estimated the percentage of a particular subclass with regard to the
 total number of occurrences of OOV-tokens (column ``\totaloov{}'') as
-well as with regard to their percentage in the list of unique OOVs
-(column ``\uniqoov{}'') without taking into account their frequencies.
+well as with regard to their percentage rate in the list of only
+unique OOVs (column ``\uniqoov{}''), i.e. disregarding their
+frequencies.
 
@@
 
-Similarly to class \ref{dict} we subdivided the group of misspellings
+Similarly to class \ref{dict}, we subdivided the group of misspellings
 into the following subgroups:

### 2013-08-01 darmstadt_gscl_2013/article_twitter_normalization.tex
statistics updated

@@
 
+dict           3.49
+compound       4.55
+abbr           3.44
+inj            4.29
+ne:person      3.47
+ne:geo         1.88
+ne:company     3.01
+ne:product     3.23
+neologism      2.38
+loan           2.87
+fw             10.91
+
 \begin{table}
@@
     \noalign{\smallskip} \hline
-    regular German words & 7.88 & 8.85 &  & \\
-    compounds & 1.22 & 2.42 &  & \\
-    abbreviations & 4.12 & 4.91 &  & \\
-    interjections & 5.93 & 4.47 &  & \\
-    person names & 4.79 & 6.45 &  & \\
-    geographic locations & 1.51 & 2.53 &  & \\
-    company names & 2.26 & 2.8 &  & \\
-    product names & 2.08 & 2.49 &  & \\
-    newly coined terms & 1.22 & 1.24 &  & \\
-    loanwords & 3.72 & 4.05 &  & \\
-    foreign words & 11.68 & 14 &  & \\\hline
-    {\bfseries total} & 46.41 & 54.21 &  & \\
+    regular German words & 7.82 & 8.78 & 2.8 & 3.49\\
+    compounds & 1.21 & 2.42 & 2.51 & 4.55\\
+    abbreviations & 3.98 & 4.77 & 3.27 & 3.44\\
+    interjections & 5.95 & 4.54 & 5.58 & 4.29\\
+    person names & 4.73 & 6.41 & 2.32 & 3.47\\
+    geographic locations & 1.5 & 2.53 & 1.16 & 1.88\\
+    company names & 2.27 & 2.84 & 4.35 & 3.01\\
+    product names & 2.13 & 2.57 & 2.45 & 3.23\\
+    newly coined terms & 1.35 & 1.31 & 3.33 & 2.38\\
+    loanwords & 3.68 & 4.03 & 3.29 & 2.87\\
+    foreign words & 11.5 & 13.76 &  9.57 & 10.91\\\hline
+    {\bfseries total} & 46.12 & 53.96 & 40.63 & 43.52\\
     \noalign{\smallskip} \hline
@@
 
-Similarly to class \ref{dict}, we subdivided the group of misspellings
-into the following subgroups:
+Similarly to class \ref{dict}, we subdivided the class ``Unintended
+sloppiness of users' input'' into the following subgroups:
 \begin{enumerate}
@@
 according to the kind of operation which led to a particular spelling
-mistake. The statistics on distribution of these subgroups is shown in
+mistake. In cases when multiple different operations were involved
+simultaneously, we explicitly marked each of these operations in our
+data. You can see the statistics on distribution of these subgroups in
 Table \ref{table:spell}.
+
 \begin{table}
@@
     \noalign{\smallskip} \hline
-    insertion &  &  &  & \\
-    deletion &  &  &  & \\
-    substitution &  &  &  & \\\hline
-    {\bfseries total} &  &  &  & \\
+    insertion & 0.49 & 1 & 0.18 & 0.34 \\
+    deletion & 8.44 & 6.38 & 6.52 & 5.27 \\
+    substitution & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
+    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
     \noalign{\smallskip} \hline
@@
 
+As it is clear from the table, deletions are by far the most common
+type of spelling mistakes. This results on the one hand from
+deliberate or unintended omissions of characters made by users but an
+even more common source of these ill-formed words is automatic
+truncation of messages made by Twitter.
+
 \begin{table}
   \caption{Distribution of OOV words belonging to the class
-    ``stylistic specifics of text genre''}
+    ``Stylistic specifics of text genre''}
   \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
@@
     \multirow{2}{*}{OOV subclass} & %
-    \multicolumn{2}{c}{\texttt{TreeTagger}} & %
-    \multicolumn{2}{c}{\texttt{hunspell}}\\
+    \multicolumn{2}{c}{\texttt{hunspell}} & %
+    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
     & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
     \noalign{\smallskip} \hline
-    hashtags &  &  &  & \\
-    @-tokens &  &  &  & \\
-    links &  &  &  & \\
-    smileys &  &  &  & \\
-    slang &  &  &  & \\\hline
-    {\bfseries total} &  &  &  & \\
+    hashtags & 7.35 & 6.18 & 13.06 & 10.59\\
+    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
+    links & 2.43 & 0.4 & 4.89 & 6.07\\
+    smileys & 2 & 0.73 & 6.88 & 1.2\\
+    slang & 16.22 & 5.27 & 6.94 & 4.77\\\hline
+    {\bfseries total} & 41.02 & 32.81 & 47.96 & 44.54\\
     \noalign{\smallskip} \hline

### 2013-08-01 darmstadt_gscl_2013/article_twitter_normalization.tex
small update

@@
   \item \textbf{Unintended sloppiness of users' input}. In the scope
-    of this second group, we considered unintended typos including
-    unexpected truncation of words at the end of Twitter
-    messages\footnote{As is generally known, Twitter imposes a strong
-      restriction on the length of posted messages which can be no
-      longer than 140 characters. Upon exceeding this length, tweets
-      get automatically truncated to maximal allowed
-      length.};\label{spell}
+    of this second group, we considered unintended typos;\label{spell}
   \item \textbf{Stylistic specifics of text genre}. This group
@@
 deliberate or unintended omissions of characters made by users but an
-even more common source of these ill-formed words is automatic
-truncation of messages made by Twitter.
+even more common source of these ill-formed words was automatic
+truncation of words at the end of tweets made by Twitter service
+itself. \footnote{As is generally known, Twitter imposes a strong
+  restriction on the length of posted messages which can be no longer
+  than 140 characters. Upon exceeding this length, tweets get
+  automatically truncated to maximal allowed length.}
 

### 2013-08-02 darmstadt_gscl_2013/article_twitter_normalization.tex
section "Analysis of unknwon words" completed (init version)

@@
   the average rate of out-of-vocabulary tokens in Twitter messages and
-  how this lower OOV-rate helps improve the quality of automatic
-  part-of-speech tagging.
+  how this lower OOV-rate in turn helps improve the quality of
+  automatic part-of-speech tagging.
 
@@
 and restores incorrectly spelled words on the basis of phonetical
-\textit{n}-gram statistics should fall into \textit{n}-gram based,
+\textit{n}-gram statistics should fall into the \textit{n}-gram based,
 probabilistic, spell checking or speech recognition class.
@@
 classifications both rely on several independent criteria at the same
-time though each of these criteria characterizes an NTN system from a
+time, though each of these criteria characterizes an NTN system from a
 different point of view. As a consequence, unambiguous assignment of
@@
 order to avoid this, we instead suggest using separate classifications
-for each criterion which might characterize an NTN technique.
+for each type of involved criteria which might characterize an NTN
+technique.
 
 One of such criteria which in our opinion would be worth a separate
-classification is \emph{segmentation level} which is used
+classification is \emph{segmentation level} that is used
 \begin{inparaenum}[\itshape a\upshape)]
@@
 variants of incorrectly spelled words. To purely graphematic systems
-belong methods suggested Brill and Moore (\cite{brill}), Sproat et
+belong methods suggested by Brill and Moore (\cite{brill}), Sproat et
 al. (\cite{sproat}), and Clark (\cite{alexander-clark}). As
@@
 supervised with the exception of Cook and Stevenson (\cite{cook}) who
-claimed to uns an unsupervised technique.
+claimed to use an unsupervised technique.
 
@@
 After skipping all words which did not contain any alphabetic
-character in them or consisted only of a single letter, we obtained a
-list of 129,146 tokens. As reference systems for dictionary lookup we
-used open source spell checking program
-\texttt{hunspell}\footnote{Ispell Version 3.2.06 (Hunspell Version
-  1.3.2); dictionary de\_DE.} and publicly available part-of-speech
-tagger \texttt{TreeTagger}\footnote{Version 3.2 with German parameter
-  file UTF-8.} (Schmid, \cite{schmid}).
+characters or consisted only of a single letter, we obtained a list of
+129,146 tokens. As reference systems for dictionary lookup we used
+open source spell checking program \texttt{hunspell}\footnote{Ispell
+  Version 3.2.06 (Hunspell Version 1.3.2); dictionary de\_DE.} and
+publicly available part-of-speech tagger
+\texttt{TreeTagger}\footnote{Version 3.2 with German parameter file
+  UTF-8.} (Schmid, \cite{schmid}).
 
@@
 from corresponding applications' dictionaries. In this respect,
-division into following groups seemed to be appropriate for us:
+division into following groups seemed to us to be appropriate:
 \begin{enumerate}
   \item \textbf{Objective limitedness of machine-readable dictionary
-    (MRD)}. To this group we counted words of basic vocabulary which
-    did not get into applications' MRD either because they supposedly
-    were rare or because they did not exist at the time when
-    dictionaries were created. Another reason for the inclusion in
-    this type was the belonging of a word to an open lexical or
+    (MRD)}. Among this group, we counted words of basic vocabulary
+    which did not get into applications' MRD either because they
+    supposedly were rare or because they did not exist at the time
+    when dictionaries were created. Another reason for the inclusion
+    in this type was the belonging of a word to an open lexical or
     part-of-speech class (like, for example, named entities or
     interjections) which are often omitted from MRDs due to
-    impossibility to fully cover these classes;\label{dict}
-  \item \textbf{Unintended sloppiness of users' input}. In the scope
-    of this second group, we considered unintended typos;\label{spell}
+    the impossibility to fully cover these classes;\label{dict}
+  \item \textbf{Sloppiness of users' input}. In the scope of this
+    second group, we considered incorrect spellings of words
+    encountered in text;\label{spell}
   \item \textbf{Stylistic specifics of text genre}. This group
     comprised words which could be considered as illegal from the
-    point of view of standard language texts but were perfectly valid
-    terms in the domain of web discourse and Twitter communication in
-    particular.\label{style}
+    point of view of standard language but were perfectly valid terms
+    in the domain of web discourse or more specifically in Twitter
+    communication.\label{style}
 \end{enumerate}
@@
 
-We subdivided group \ref{dict} into the following subgroups:
+We subdivided the class \ref{dict} into the following subclasses:
 \begin{enumerate}
@@
   which in contrast to \ref{loan} were not mentioned in any existing
-  German lexicons and did not comply with inflectional rules of German
+  German lexica and did not comply with inflectional rules of German
   grammar.\label{fw}
@@
 Though this division is admittedly arbitrarily to a certain degree and
-involves different linguistic criteria simultaneously, the underlying
-notion for it is simple. Valid words could have been omitted from an
-MRD either due to the limitation of developers' capacities (group
-\ref{regular}), active word formation or lexical productivity of the
-language (groups \ref{compound} through \ref{new}) or also due to
+also has the disadvantage of simultaneously involving different
+linguistic criteria, the underlying notion here was simple -- valid
+words could have been omitted from an MRD either due to the
+limitations of developers' capacities (group \ref{regular}), active
+word formation processes or lexical productivity of the language
+itself (groups \ref{compound} through \ref{new}) or also due to
 language's openness to foreign language systems (groups \ref{loan} and
@@
 In Table \ref{table:mrd}, percentage figures for each of the above
-subgroups are shown. We have considered OOV-distribution for both
+subgroups are shown. We have considered OOV-distributions for both
 \texttt{hunspell} and \texttt{TreeTagger}. For each of them, we
@@
 well as with regard to their percentage rate in the list of only
-unique OOVs (column ``\uniqoov{}''), i.e. disregarding their
-frequencies.
-
-dict           3.49
-compound       4.55
-abbr           3.44
-inj            4.29
-ne:person      3.47
-ne:geo         1.88
-ne:company     3.01
-ne:product     3.23
-neologism      2.38
-loan           2.87
-fw             10.91
-
+unique OOVs disregarding their frequencies (column ``\uniqoov{}'').
 \begin{table}
   \caption{Distribution of OOV words belonging to the class
-    ``objective limitedness of MRD''\label{table:mrd}}
+    ``Objective limitedness of MRD''\label{table:mrd}}
   \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
@@
 
-Similarly to class \ref{dict}, we subdivided the class ``Unintended
-sloppiness of users' input'' into the following subgroups:
+Similarly to the class \ref{dict}, we subdivided the group
+``Sloppiness of users' input'' into the following subgroups:
 \begin{enumerate}
-  \item insertion;
-  \item deletion;
-  \item substitution;
+  \item insertions, e.g. \textit{dennen} instead of \textit{denen};
+  \item deletions, e.g. \textit{scho} instead of \textit{schon};
+  \item substitutions, e.g. \textit{fur} instead of \textit{f\"ur};
 \end{enumerate}
-according to the kind of operation which led to a particular spelling
+according to the type of operation which led to a particular spelling
 mistake. In cases when multiple different operations were involved
 simultaneously, we explicitly marked each of these operations in our
-data. You can see the statistics on distribution of these subgroups in
-Table \ref{table:spell}.
-
+data. Statistical distribution of these subclasses is shown in Table
+\ref{table:spell}.
 \begin{table}
   \caption{Distribution of OOV words belonging to the class
-    ``unintended sloppiness of users' input''\label{table:spell}}
+    ``Sloppiness of users' input''\label{table:spell}}
   \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
@@
     \noalign{\smallskip} \hline
-    insertion & 0.49 & 1 & 0.18 & 0.34 \\
-    deletion & 8.44 & 6.38 & 6.52 & 5.27 \\
-    substitution & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
+    insertions & 0.49 & 1 & 0.18 & 0.34 \\
+    deletions & 8.44 & 6.38 & 6.52 & 5.27 \\
+    substitutions & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
     {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
@@
 
-As it is clear from the table, deletions are by far the most common
-type of spelling mistakes. This results on the one hand from
-deliberate or unintended omissions of characters made by users but an
-even more common source of these ill-formed words was automatic
-truncation of words at the end of tweets made by Twitter service
-itself. \footnote{As is generally known, Twitter imposes a strong
-  restriction on the length of posted messages which can be no longer
-  than 140 characters. Upon exceeding this length, tweets get
-  automatically truncated to maximal allowed length.}
+As is clear from the table, deletions are by far the most common type
+of misspellings. The reasons for that are on the one hand either
+relatively frequent omissions of characters made by user or even more
+often automatic truncations of too long messages which were performed
+by Twitter service itself.\footnote{As is generally known, Twitter
+  imposes a strong restriction on the length of posted messages which
+  can be no longer than 140 characters. Upon exceeding this length,
+  tweets get automatically truncated to the maximal allowed length.}
 
+Finally, the third group -- ``Stylistic specifics of text genre'' --
+was subdivided into the subgroups:
+\begin{enumerate}
+  \item hashtags, e.g. \textit{\#Kleinanzeigen};
+  \item @-tokens, e.g. \textit{@ZDFonline};
+  \item links, e.g. \textit{http://t.co};
+  \item smileys, e.g. \textit{:-P};
+  \item slang, e.g. \textit{OMG}.
+\end{enumerate}
+according to the lexical or syntactic class which these tokens
+belonged to. Apart from lexical expressions pertaining to the genre of
+Internet-based communication, we also marked as \textit{slang}
+spelling variants of standard language words which could be regarded
+as their corresponding colloquial equivalents. As such equivalents, we
+considred spellings like \textit{ned} instead of \textit{nicht} or
+\textit{grad} instead of \textit{gerade}. These cases were marked by
+us both as misspellings and as slang. A detailed statistics on the
+above subgroups of class 3 is shown in Table \ref{table:style}:
 \begin{table}
   \caption{Distribution of OOV words belonging to the class
-    ``Stylistic specifics of text genre''}
+    ``Stylistic specifics of text genre''\label{table:style}}
   \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
@@
 
+A striking outlier of 16.22~\% for slang in column 1 of the table is
+due to the fact that the word ``RT'' which occurred 1,235 and was by
+far the most frequent OOV in our data was recognized as
+out-of-vocabulary by \texttt{hunspell} but not recognized as such by
+\texttt{TreeTagger}.
+
+This knowledge about composition of unknown and ill-formed words
+should now help us select or devise techniques for recognizing and
+correcting such tokens in cases where it is needed. These procedures
+are described in the next Section of the article.
+
 \section{Text Normalization Procedure}\label{normalization}
@@
 
-This article provided an overview of exisiting approaches to noisy
-text normalization task. Additionally, all mentioned methods were
-classified on the basis of two independent criteria. In section
-\ref{error:analysis}, we performed qulitative and quantitive analyses
-of out-of-vocabulary words in German tweets and suggested a set of
-ad-hoc techniques for mitigating their potential negative influence on
-natural language processing. This procedure allowed us to reduce the
-total OOV rate by ... \% for \texttt{hunspell} and by ... \% for
-\texttt{TreeTagger}.
+%% This article provided an overview of exisiting approaches to noisy
+%% text normalization task. Additionally, all mentioned methods were
+%% classified on the basis of two independent criteria. In section
+%% \ref{error:analysis}, we performed qulitative and quantitive analyses
+%% of out-of-vocabulary words in German tweets and suggested a set of
+%% ad-hoc techniques for mitigating their potential negative influence on
+%% natural language processing. This procedure allowed us to reduce the
+%% total OOV rate by ... \% for \texttt{hunspell} and by ... \% for
+%% \texttt{TreeTagger}.
 
-Nevertheless, we should honestly admit that our system still has
-potential for development and research, since it mainly addresses only
-one of three main groups of OOV tokens. Future directions should
-certainly include a more thorough tackling of unintentional spelling
-mistakes and especially their most prominent types -- deletions and
-substitutions.
+%% Nevertheless, we should honestly admit that our system still has
+%% potential for development and research, since it mainly addresses only
+%% one of three main groups of OOV tokens. Future directions should
+%% certainly include a more thorough tackling of unintentional spelling
+%% mistakes and especially their most prominent types -- deletions and
+%% substitutions.
 
-Furthemore, a better evalution technique as well as comparison with
-other systems are needed for our normalization procedure. On the one
-hand, an \textit{extrinsic} evaluation should be performed (cf. Sparck
-Jones and Galliers, \cite{sparck}) which means that we not only have
-to show how the rate of OOV words goes down but much more how this
-lower OOV rate affects the work of the whole NLP system. On the other
-hand, we need to assess the quality of our procedure's work on the
-basis of metrics used by other researchers.
+%% Furthemore, a better evalution technique as well as comparison with
+%% other systems are needed for our normalization procedure. On the one
+%% hand, an \textit{extrinsic} evaluation should be performed (cf. Sparck
+%% Jones and Galliers, \cite{sparck}) which means that we not only have
+%% to show how the rate of OOV words goes down but much more how this
+%% lower OOV rate affects the work of the whole NLP system. On the other
+%% hand, we need to assess the quality of our procedure's work on the
+%% basis of metrics used by other researchers.
 
-One possible estimation criterion which was used by Aw et
-al. (\cite{aw}), Kaufmann (\cite{kaufmann}), Beaufort et
-al. (\cite{beaufort}), and Oliva et al. (\cite{oliva}) is the BLEU
-score (Papineni et al., \cite{papineni}). Another possibility would be
-to use the Word (WER) and Sentence Error Rates (SER) as suggested by
-Kobus et al. (\cite{kobus}). However, an obvious difficulty that we
-already encountered here is that both metrics highly rely on a
-subjective notion of the look of a ``normalized'' message. While the
-BLEU score could be an approriate criterion for normalization of
-messages like ``i luv ma mather and wd do evrythin 4 her'' which in
-fact looks like as if it were not English. But such highly distorted
-tweets are rather atypical for German. In this regard, WER and SER
-could be considered as more appropriate measurement criteria. But
-these metrics once again are rather dealing with spelling mistakes and
-would highly depend on whether one, for example, would consider the
-hash sign in a hashtag as an error.
+%% One possible estimation criterion which was used by Aw et
+%% al. (\cite{aw}), Kaufmann (\cite{kaufmann}), Beaufort et
+%% al. (\cite{beaufort}), and Oliva et al. (\cite{oliva}) is the BLEU
+%% score (Papineni et al., \cite{papineni}). Another possibility would be
+%% to use the Word (WER) and Sentence Error Rates (SER) as suggested by
+%% Kobus et al. (\cite{kobus}). However, an obvious difficulty that we
+%% already encountered here is that both metrics highly rely on a
+%% subjective notion of the look of a ``normalized'' message. While the
+%% BLEU score could be an approriate criterion for normalization of
+%% messages like ``i luv ma mather and wd do evrythin 4 her'' which in
+%% fact looks like as if it were not English. But such highly distorted
+%% tweets are rather atypical for German. In this regard, WER and SER
+%% could be considered as more appropriate measurement criteria. But
+%% these metrics once again are rather dealing with spelling mistakes and
+%% would highly depend on whether one, for example, would consider the
+%% hash sign in a hashtag as an error.
 

### 2013-08-05 darmstadt_gscl_2013/article_twitter_normalization.tex
small updates in article

@@
   tackle some of the most prominent disturbing effects found during
-  these analyses and show how this set of techniques helps us lower
-  the average rate of out-of-vocabulary tokens in Twitter messages and
-  how this lower OOV-rate in turn helps improve the quality of
-  automatic part-of-speech tagging.
+  the analyses and show how this set of techniques helps us lower the
+  average rate of out-of-vocabulary tokens in Twitter messages and how
+  this lower OOV-rate in turn helps improve the quality of automatic
+  part-of-speech tagging.
 
@@
 
-In the next Section we will give a short overview of recent scientific
-approaches to the problem of tackling out-of-vocabulary words in
-non-standard texts. After that, in Section \ref{error:analysis} we
-will analyze which types of noisiness phenomena are especially
-characteristic for German Twitter. Section \ref{normalization} will
-subsequently describe an automatic procedure for mitigating some of
-the most prominent of those effects. In a concluding step, we will
-perform an evaluation of the results of this procedure and give
-further suggestions for future research.
+In the next Section we will give a short overview of existing
+scientific approaches to the problem of tackling out-of-vocabulary
+words in non-standard texts. After that, in Section
+\ref{error:analysis} we will analyze which types of noisiness
+phenomena are especially characteristic for German Twitter. Section
+\ref{normalization} will subsequently describe an automatic procedure
+for mitigating some of the most prominent of those effects. In a
+concluding step, we will perform an evaluation of the results of this
+procedure and give further suggestions for future research.
 
@@
 
-Before proceeding with the description of existing methods for noisy
+Before proceeding with the description of recent methods for noisy
 text normalization (NTN), we first would like to define the criteria
@@
 there already exist several classifications of NTN approaches
-including Kukich (\cite{kukich}), Kobus et al. (\cite{kobus}), and
-Sproat et al. (\cite{sproat}).
-%% But all of these classifications seem to share one significant common
-%% shortcoming, namely they try to involve several independent criteria
-%% within one classification scheme.
+including, for example, Kukich (\cite{kukich}) and Kobus et
+al. (\cite{kobus}).
 
-Kukich (\cite{kukich}), for example, divided NTN techniques into six
-classes:
+So, Kukich (\cite{kukich}), for instance, divided all NTN techniques
+into six classes:
 \begin{enumerate}
@@
 
-With these two classifications, we will now try to present and group
-together approaches to the NTN task which appeared in the literature
-in recent years.
+Based on these two classifications, recently proposed approaches to
+the NTN task could be grouped together as follows.
 
@@
 information inference, practically all of these methods were
-supervised with the exception of Cook and Stevenson (\cite{cook}) who
-claimed to use an unsupervised technique.
+supervised with the exceptions of Cook and Stevenson (\cite{cook}) who
+claimed to use an unsupervised technique, and Sproat et
+al. (\cite{sproat}) who described both a supervised and an
+unsupervised technique.
 
@@
     supposedly were rare or because they did not exist at the time
-    when dictionaries were created. Another reason for the inclusion
-    in this type was the belonging of a word to an open lexical or
+    when dictionaries were created. Another reason for inclusion in
+    this type was the belonging of a word to an open lexical or
     part-of-speech class (like, for example, named entities or
-    interjections) which are often omitted from MRDs due to
-    the impossibility to fully cover these classes;\label{dict}
+    interjections) which are often omitted from MRDs due to the
+    impossibility to fully cover them;\label{dict}
   \item \textbf{Sloppiness of users' input}. In the scope of this
@@
 
-We subdivided the class \ref{dict} into the following subclasses:
+We subdivided class \ref{dict} into the following subclasses:
 \begin{enumerate}
@@
 estimated the percentage of a particular subclass with regard to the
-total number of occurrences of OOV-tokens (column ``\totaloov{}'') as
-well as with regard to their percentage rate in the list of only
-unique OOVs disregarding their frequencies (column ``\uniqoov{}'').
+total number of occurrences of all OOV-tokens (column ``\totaloov{}'')
+as well as with regard to their percentage rate in the list of only
+unique OOVs disregarding the frequencies (column ``\uniqoov{}'').
 \begin{table}
@@
 
-Similarly to the class \ref{dict}, we subdivided the group
-``Sloppiness of users' input'' into the following subgroups:
+Similarly to class \ref{dict}, we subdivided the group ``Sloppiness of
+users' input'' into the following subgroups:
 \begin{enumerate}
@@
 of misspellings. The reasons for that are on the one hand either
-relatively frequent omissions of characters made by user or even more
-often automatic truncations of too long messages which were performed
-by Twitter service itself.\footnote{As is generally known, Twitter
+relatively frequent omissions of characters made by users or even more
+often automatic truncation of too long messages which is performed by
+Twitter service itself.\footnote{As is generally known, Twitter
   imposes a strong restriction on the length of posted messages which
@@
 \end{enumerate}
-according to the lexical or syntactic class which these tokens
-belonged to. Apart from lexical expressions pertaining to the genre of
-Internet-based communication, we also marked as \textit{slang}
-spelling variants of standard language words which could be regarded
-as their corresponding colloquial equivalents. As such equivalents, we
-considred spellings like \textit{ned} instead of \textit{nicht} or
-\textit{grad} instead of \textit{gerade}. These cases were marked by
+according to the formal or lexical class which these tokens belonged
+to. Additionally, we also considered as \textit{slang} spelling
+variants of standard language words which could be regarded as their
+corresponding colloquial equivalents like, for example, \textit{ned}
+instead of \textit{nicht} or \textit{grad} instead of \textit{gerade}.
+
+These cases were marked by
 us both as misspellings and as slang. A detailed statistics on the

### 2013-08-06 darmstadt_gscl_2013/article_twitter_normalization.tex
small updates in article

@@
 
-Based on these two classifications, recently proposed approaches to
+According to these two classification criteria, recent approaches to
 the NTN task could be grouped together as follows.
@@
 and Moore (\cite{toutanova}), Choudhury et al. (\cite{choudhury}),
-Cook and Stevenson (\cite{cook}) etc. With regard to the type of
-information inference, practically all of these methods were
-supervised with the exceptions of Cook and Stevenson (\cite{cook}) who
-claimed to use an unsupervised technique, and Sproat et
-al. (\cite{sproat}) who described both a supervised and an
-unsupervised technique.
+Cook and Stevenson (\cite{cook}), Han and Baldwin (\cite{han})
+etc. With regard to the type of information inference, practically all
+of these methods were supervised with the exceptions of Cook and
+Stevenson (\cite{cook}) who claimed to use an unsupervised technique,
+and Sproat et al. (\cite{sproat}) who described both a supervised and
+an unsupervised method.
 
 Starting from the second half of the 2000s, the raising influence and
-improved quality of machine translation tools lead to the development
+improved quality of machine translation tools led to the development
 of NTN technologies which used broader levels of segmentation. In
@@
 past few years. Among these we should especially mention works by
-Kobus et al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), Han and
-Baldwin (\cite{han}), and Oliva et al. (\cite{oliva}). The majority of
-these systems used the whole range of segmentation levels from
-phonographematatic to phrasal one, and in many cases they also applied
-different knowledge inference mechanisms to different levels of the
-language.
+Kobus et al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), and Oliva et
+al. (\cite{oliva}). The majority of these systems used the whole range
+of segmentation levels from phonographematatic to phrasal one, and in
+many cases they also applied different knowledge inference mechanisms
+to different levels of the language.
 
@@
 as well as with regard to their percentage rate in the list of only
-unique OOVs disregarding the frequencies (column ``\uniqoov{}'').
+unique OOVs disregarding frequencies (column ``\uniqoov{}'').
 \begin{table}
@@
 As is clear from the table, deletions are by far the most common type
-of misspellings. The reasons for that are on the one hand either
-relatively frequent omissions of characters made by users or even more
-often automatic truncation of too long messages which is performed by
-Twitter service itself.\footnote{As is generally known, Twitter
-  imposes a strong restriction on the length of posted messages which
-  can be no longer than 140 characters. Upon exceeding this length,
-  tweets get automatically truncated to the maximal allowed length.}
+of misspellings. The reasons for that are either relatively frequent
+omissions of characters made by users or, even more often, automatic
+truncations of too long messages which are performed by Twitter
+service itself.\footnote{As is generally known, Twitter imposes a
+  strong restriction on the length of posted messages which can be no
+  longer than 140 characters. Upon exceeding this length, tweets get
+  automatically truncated to the maximal allowed length.}
 
@@
 \begin{enumerate}
+  \item @-tokens, e.g. \textit{@ZDFonline};
   \item hashtags, e.g. \textit{\#Kleinanzeigen};
-  \item @-tokens, e.g. \textit{@ZDFonline};
   \item links, e.g. \textit{http://t.co};
@@
 \end{enumerate}
-according to the formal or lexical class which these tokens belonged
+according to the formal or lexical class which the tokens belonged
 to. Additionally, we also considered as \textit{slang} spelling
 variants of standard language words which could be regarded as their
-corresponding colloquial equivalents like, for example, \textit{ned}
-instead of \textit{nicht} or \textit{grad} instead of \textit{gerade}.
-
-These cases were marked by
-us both as misspellings and as slang. A detailed statistics on the
-above subgroups of class 3 is shown in Table \ref{table:style}:
+colloquial equivalents. Such words included cases like, for example,
+\textit{ned} instead of \textit{nicht} or \textit{grad} instead of
+\textit{gerade} and were marked both as \textit{misspelling}s and
+\textit{slang} in our classification. A detailed statistics on the
+subgroups of class 3 is shown in Table \ref{table:style}:
 \begin{table}
@@
     \noalign{\smallskip} \hline
+    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
     hashtags & 7.35 & 6.18 & 13.06 & 10.59\\
-    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
     links & 2.43 & 0.4 & 4.89 & 6.07\\
@@
 
-A striking outlier of 16.22~\% for slang in column 1 of the table is
-due to the fact that the word ``RT'' which occurred 1,235 and was by
-far the most frequent OOV in our data was recognized as
-out-of-vocabulary by \texttt{hunspell} but not recognized as such by
-\texttt{TreeTagger}.
+A striking outlier of 16.22~\% for slang tokens in column 1 is
+explained by the fact that the word ``RT'' which occurred 1,235 times
+in our data and was by far the most frequent OOV in analyzed texts,
+was recognized as out-of-vocabulary by \texttt{hunspell} but was not
+deemed as such by \texttt{TreeTagger}. Luckily, such singleton cases
+were rather rare exceptions during the analyses and did not affect
+much the remaining classes of OOVs, so that distributions of unknown
+tokens for both tools were more or less similar or at least comparable
+to a certain extent.
 
-This knowledge about composition of unknown and ill-formed words
-should now help us select or devise techniques for recognizing and
-correcting such tokens in cases where it is needed. These procedures
-are described in the next Section of the article.
+But an even more important conclusion which can be drawn from the
+analyzed data is the fact that for both \texttt{TreeTagger} and
+\texttt{hunspell}, Twitter-specific phenomena like special tokens,
+colloquial expressions or sloppily typed words accounted for more than
+a half of all unknown words found in data. Since different classes of
+these Twitter phenomena were formed by different processes and also
+have different degrees of ambiguity, we will suggest different
+normalization procedures for each of them in the next Section.
 
 \section{Text Normalization Procedure}\label{normalization}
+
 \subsection{Replacement of Twitter-Specific Phenomena}
+Though hashtags are almost ubiquitous in today's tweets and one would
+probably think that they are as old as Twitter itself, an admirable
+truth would be that hashtags actually existed long before
+Twitter-service was introduced. It were Internet Relay Chats (IRC) --
+the forebears of all modern social networks -- which used the hash
+sign to mark channel names. And it was Chris Messina, a renowned
+advocate of open-source community, who borrowed this idea and brought
+it to Twitter. The ``hash godfather'', as Chris Messina describes
+himself, sent out a Twitter message suggesting that the pound sign
+coul be used for organizing groups on Twitter in August 2007. But a
+noticeable dissemination of this ``novelty'' among the Twitter
+community only happened a few years later, in 2010. ``I would say 2010
+was really the year of the hashtag.'' claims Ginger Wilcox, a founder
+of the Social Media Marketing Institute (cf. Parker, \cite{parker}).
+
+Luckily for us, both hashtags and @-names which are another
+omnipresent phenomenon in Twitter have very clear formal criteria by
+which these tokens could be identified and captured. The existence of
+such formal cues suggests that these phenomena could best be handled
+by means of rule-based methods. A most appropriate of such methods
+seemed to be an analog of finite-state transducers (FST).
+
 %
@@
 
+\bibitem [2011]{parker}
+  Parker, A.: %
+  Twitter's Secret Handshake. %
+  The New York Times, Page ST1, (June 10, 2011)
+
 \bibitem [1980]{petersen}

### 2013-08-07 darmstadt_gscl_2013/article_twitter_normalization.tex
rule-based section for Twitter-specific phenomena added

@@
 
-So, Kukich (\cite{kukich}), for instance, divided all NTN techniques
-into six classes:
+Kukich (\cite{kukich}), for instance, divided all NTN techniques into
+six classes:
 \begin{enumerate}
@@
 
-Though both divisions seem to be justified to some extent, it is
-difficult to determine using them whether an NTN approach that detects
-and restores incorrectly spelled words on the basis of phonetical
-\textit{n}-gram statistics should fall into the \textit{n}-gram based,
-probabilistic, spell checking or speech recognition class.
+Though both of these divisions seem to be justified to some extent, it
+is difficult to determine using them whether an NTN approach that
+detects and restores incorrectly spelled words on the basis of
+phonetical \textit{n}-gram statistics should fall into the
+\textit{n}-gram based, probabilistic, spell checking or speech
+recognition class.
 
@@
 Cook and Stevenson (\cite{cook}), Han and Baldwin (\cite{han})
-etc. With regard to the type of information inference, practically all
-of these methods were supervised with the exceptions of Cook and
-Stevenson (\cite{cook}) who claimed to use an unsupervised technique,
-and Sproat et al. (\cite{sproat}) who described both a supervised and
-an unsupervised method.
+etc. With regard to the type of information inference, most of these
+methods were supervised with the exceptions of Cook and Stevenson
+(\cite{cook}) and Han and Baldwin (\cite{han}) who claimed to use an
+unsupervised technique. Sproat et al. (\cite{sproat}) described in
+their article both a supervised and unsupervised approach.
 
@@
 concentrated on only English data. A few exceptions from that are
-approaches suggested by Beaufort et al. (\cite{beaufort}) for French
+approaches suggested by Beaufort et al. (\cite{beaufort}) for French,
 and Oliva et al. (\cite{oliva}) for Spanish. To find out which
@@
 German Twitter in the next Section in order to see what kind of NTN
-techniques would be more suitable for handling ill-formed words there.
+techniques would be most suitable for handling such words there.
 
@@
 129,146 tokens. As reference systems for dictionary lookup we used
-open source spell checking program \texttt{hunspell}\footnote{Ispell
+open-source spell checking program \texttt{hunspell}\footnote{Ispell
   Version 3.2.06 (Hunspell Version 1.3.2); dictionary de\_DE.} and
@@
 Here once again the question of classification arose. This time with
-regard to the reasons, why different tokens could have been omitted
+regard to the reasons why different tokens could have been omitted
 from corresponding applications' dictionaries. In this respect,
-division into following groups seemed to us to be appropriate:
+division into following groups seemed to us to be appropriate to us:
 \begin{enumerate}
@@
 \end{enumerate}
-Though this division is admittedly arbitrarily to a certain degree and
+Though this division is admittedly arbitrary to a certain degree and
 also has the disadvantage of simultaneously involving different
@@
 of misspellings. The reasons for that are either relatively frequent
-omissions of characters made by users or, even more often, automatic
+omissions of characters made by users or even more often automatic
 truncations of too long messages which are performed by Twitter
@@
 
-A striking outlier of 16.22~\% for slang tokens in column 1 is
-explained by the fact that the word ``RT'' which occurred 1,235 times
-in our data and was by far the most frequent OOV in analyzed texts,
-was recognized as out-of-vocabulary by \texttt{hunspell} but was not
-deemed as such by \texttt{TreeTagger}. Luckily, such singleton cases
-were rather rare exceptions during the analyses and did not affect
-much the remaining classes of OOVs, so that distributions of unknown
-tokens for both tools were more or less similar or at least comparable
-to a certain extent.
+A striking outlier of 16.22~\% for slang tokens in column 1 of the
+Table is explained by the fact that the word ``RT'' which occurred
+1,235 times in our texts and was by far the most frequent OOV in
+analyzed data, was recognized as out-of-vocabulary by
+\texttt{hunspell} but was not deemed as such by
+\texttt{TreeTagger}. Luckily, such singleton cases were rather rare
+exceptions during the analyses and did not affect much the remaining
+classes of OOVs, so that distributions of unknown tokens for both
+tools were more or less similar or at least comparable to a certain
+extent.
 
@@
 colloquial expressions or sloppily typed words accounted for more than
-a half of all unknown words found in data. Since different classes of
-these Twitter phenomena were formed by different processes and also
-have different degrees of ambiguity, we will suggest different
-normalization procedures for each of them in the next Section.
+a half of all unknown words found during the analysis. Since different
+classes of these Twitter phenomena were formed by different processes
+and also have different degrees of ambiguity, we will suggest
+different normalization procedures for each of them in the next
+Section.
 
@@
 \subsection{Replacement of Twitter-Specific Phenomena}
-Though hashtags are almost ubiquitous in today's tweets and one would
-probably think that they are as old as Twitter itself, an admirable
-truth would be that hashtags actually existed long before
-Twitter-service was introduced. It were Internet Relay Chats (IRC) --
-the forebears of all modern social networks -- which used the hash
-sign to mark channel names. And it was Chris Messina, a renowned
-advocate of open-source community, who borrowed this idea and brought
-it to Twitter. The ``hash godfather'', as Chris Messina describes
-himself, sent out a Twitter message suggesting that the pound sign
-coul be used for organizing groups on Twitter in August 2007. But a
-noticeable dissemination of this ``novelty'' among the Twitter
-community only happened a few years later, in 2010. ``I would say 2010
-was really the year of the hashtag.'' claims Ginger Wilcox, a founder
-of the Social Media Marketing Institute (cf. Parker, \cite{parker}).
+In August 2007, Chris Messina, a renowned advocate of open-source
+community, sent out a Twitter message suggesting that the pound sign
+could be used for organizing groups on Twitter (cf. Parker,
+\cite{parker}). The ``hash godfather'', as Chris Messina described
+himself, allegedly borrowed this idea from Internet Relay Chats (IRC)
+-- the forebears of modern social networks -- which have been using
+the ``\#{}''-sign to mark channel names since the early 1990s.
 
-Luckily for us, both hashtags and @-names which are another
-omnipresent phenomenon in Twitter have very clear formal criteria by
-which these tokens could be identified and captured. The existence of
-such formal cues suggests that these phenomena could best be handled
-by means of rule-based methods. A most appropriate of such methods
-seemed to be an analog of finite-state transducers (FST).
+Luckily for us, this ``novelty'' by Messina as well as @-tokens which
+are in Twitter to mark names of user account both have strict formal
+features by which these tokens could be identified. Other types of
+words which are usually considered as OOVs and have unambiguous formal
+traits are hyperlinks, e-mail addresses, and smileys. The presence of
+such formal criteria suggests that these classes could best be handled
+by rule-methods and namely finite-state techniques like finite-state
+transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
+pp.57-60).
+
+For our purposes, we developed a prototypic Python system analogous to
+FSTs in which a set of regular expressions was associated with
+corresponding actions performed on matched subgroups. In this system,
+absolutely unambiguous tokens like web links and e-mail addresses were
+replaced with special words ``\%Mail'' and ``\%Link''
+correspondingly. Emoticons were replaced with tokens ``\%PosSmiley'',
+``\%NegSmiley'', depending on the type of emotion presumably conveyed
+by these expressions. In cases when an emoticon was ambiguous with
+regard to its polarity, it was replaced with the artificial word
+``\%Smiley''.
+
+Additionally to that, problematic UTF-8 characters like special quotes
+and ellipsis which caused incorrect work of tokenizer were converted
+to their corresponding ISO-8859-1 equivalents.
+
+For hashtags, we simply stripped off the pound character from the
+beginning of such words thus leaving only the alphabetic part of
+tokens. A more complicated case turned out to be the @-tokens. For
+them, we had to decide depending on the context whether these tokens
+played an important syntactic role in sentence or not. In cases they
+did, we additionally looked whether the alphabetic part following the
+``@'' character was present in dictionary. If it was, we only stripped
+the ``at'' character off, otherwise whole word was replaced with token
+``\%UserName''. In cases when @-tokens served as addresses or retweet
+marks, we deleted them from message since they were of little interest
+and importance for further syntactic and semantic analysis and could
+hardly be assigned a proper part-of-speech tag or syntactic role.
+
+All the artificially introduced words were added to custom user
+dictionaries of \texttt{TreeTagger} and \texttt{hunspell}. For
+tagging, we assigned NE tags to all artificial words except for smiley
+replacements which got the tag INJ. Additionally, positions and
+lengths of all replacements we remembered along with original words
+which were replaced and a restoration step to original forms was
+performed for certain classes of tokens after tagging.
 

### 2013-08-08 darmstadt_gscl_2013/article_twitter_normalization.tex
test data for noise cleaner added

@@
 Luckily for us, this ``novelty'' by Messina as well as @-tokens which
-are in Twitter to mark names of user account both have strict formal
-features by which these tokens could be identified. Other types of
-words which are usually considered as OOVs and have unambiguous formal
-traits are hyperlinks, e-mail addresses, and smileys. The presence of
-such formal criteria suggests that these classes could best be handled
-by rule-methods and namely finite-state techniques like finite-state
-transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
-pp.57-60).
+are used in Twitter to mark names of user account, both have strict
+formal features by which these tokens could be identified. Other types
+of words which are usually considered as OOVs and also have
+unambiguous formal traits are hyperlinks, e-mail addresses, and
+smileys. The presence of such formal criteria suggests that these
+classes could best be handled by rule-methods and namely finite-state
+techniques like finite-state transducers (FST) (cf. Jurafsky and
+Martin, \cite{jurafsky}, pp.57-60).
 
@@
 ``\%UserName''. In cases when @-tokens served as addresses or retweet
-marks, we deleted them from message since they were of little interest
-and importance for further syntactic and semantic analysis and could
-hardly be assigned a proper part-of-speech tag or syntactic role.
+marks, we deleted them from message completely since they were of
+little interest and importance for further syntactic and semantic
+analysis and could hardly be assigned a proper part-of-speech tag or
+syntactic role.
 
@@
 dictionaries of \texttt{TreeTagger} and \texttt{hunspell}. For
-tagging, we assigned NE tags to all artificial words except for smiley
-replacements which got the tag INJ. Additionally, positions and
-lengths of all replacements we remembered along with original words
-which were replaced and a restoration step to original forms was
+tagging, we assigned NE tags to all artificial words except for
+emoticon replacements which got the tag INJ. Additionally, positions
+and lengths of all replacements we remembered along with original
+words which were replaced and a restoration step to original forms was
 performed for certain classes of tokens after tagging.
 
+Precision, recall and F1 score for replacement of Twitter-specific
+phenomena is shown in Table \ref{table:tw-phenomen-metrics}.
+
+\begin{table}
+  \caption{Precision, recall and F1 score for replacement of
+    Twitter-specific phenomena\label{table:tw-phenomen-metrics}}
+  \begin{tabular}{*{4}{>{\centering\arraybackslash}p{0.25\textwidth}}}
+    \hline\noalign{\smallskip}
+    OOV subclass & Precision & Recall & F1 score\\\hline
+    @-tokens & 0 & 0 & 0\\
+    hashtags & 0 & 0 & 0\\
+    links & 0 & 0 & 0\\
+    e-mail addresses & 0 & 0 & 0\\
+    smileys & 0 & 0 & 0\\
+    \noalign{\smallskip} \hline
+  \end{tabular}
+\end{table}
+
 %
-\subsection{Restoration of Umlauts}
+\subsection{Restoration of misspellings}
 %
-\subsection{Squeezing of Elongated Words}
+\subsubsection{Restoration of Umlauts}
 %
-\subsection{Translation of Slang Idioms}
+\subsubsection{Squeezing of Elongated Words}
+%
+\subsubsection{Translation of Slang Misspellings}
 %

### 2013-08-12 darmstadt_gscl_2013/article_twitter_normalization.tex
f-score added for twitter specific stuff

@@
     OOV subclass & Precision & Recall & F1 score\\\hline
-    @-tokens & 0 & 0 & 0\\
-    hashtags & 0 & 0 & 0\\
-    links & 0 & 0 & 0\\
-    e-mail addresses & 0 & 0 & 0\\
-    smileys & 0 & 0 & 0\\
+    attoken & 98.87 & 98.87 & 98.87\\
+    link & 99.44 & 100.00 & 99.72\\
+    smiley & 93.79 & 76.26 & 84.12\\
     \noalign{\smallskip} \hline

### 2013-08-12 darmstadt_gscl_2013/article_twitter_normalization.tex
statistics for spell class in hunspell updated

@@
 
-In the next Section we will give a short overview of existing
+In the next Section, we will give a short overview of existing
 scientific approaches to the problem of tackling out-of-vocabulary
@@
 
-The reason for this confusion is the fact that the above
-classifications both rely on several independent criteria at the same
-time, though each of these criteria characterizes an NTN system from a
-different point of view. As a consequence, unambiguous assignment of
-an NTN approach to one particular class often becomes impossible. In
+This confusion is explained by the fact that the above classifications
+both rely on several independent criteria at the same time, however
+each of these criteria characterizes an NTN system from a different
+point of view. As a consequence of this, unambiguous assignment of an
+NTN approach to one particular class often becomes impossible. In
 order to avoid this, we instead suggest using separate classifications
-for each type of involved criteria which might characterize an NTN
-technique.
+for each type of involved characterizing criterion.
 
@@
 
-Here once again the question of classification arose. This time with
-regard to the reasons why different tokens could have been omitted
-from corresponding applications' dictionaries. In this respect,
-division into following groups seemed to us to be appropriate to us:
+We classified found OOV tokens into the following three groups
+according to the reasons why these tokens could have been omitted from
+corresponding applications' dictionaries:
 \begin{enumerate}
-  \item \textbf{Objective limitedness of machine-readable dictionary
+  \item \textbf{Objective limitedness of machine-readable dictionaries
     (MRD)}. Among this group, we counted words of basic vocabulary
     which did not get into applications' MRD either because they
-    supposedly were rare or because they did not exist at the time
-    when dictionaries were created. Another reason for inclusion in
-    this type was the belonging of a word to an open lexical or
+    supposedly were rare or did not exist at the time when
+    dictionaries were created. Another reason for inclusion in this
+    type was the belonging of a word to an open lexical or
     part-of-speech class (like, for example, named entities or
@@
 \begin{enumerate}
-\item regular German words, e.g. \textit{aufm},
+\item regular German words, e.g. \textit{meins},
   \textit{losziehen};\label{regular}
@@
 
-As is clear from the table, deletions are by far the most common type
-of misspellings. The reasons for that are either relatively frequent
-omissions of characters made by users or even more often automatic
-truncations of too long messages which are performed by Twitter
-service itself.\footnote{As is generally known, Twitter imposes a
-  strong restriction on the length of posted messages which can be no
-  longer than 140 characters. Upon exceeding this length, tweets get
-  automatically truncated to the maximal allowed length.}
+%% As is clear from the table, deletions are by far the most common type
+%% of misspellings. The reasons for that are either relatively frequent
+%% omissions of characters made by users or even more often automatic
+%% truncations of too long messages which are performed by Twitter
+%% service itself.\footnote{As is generally known, Twitter imposes a
+%%   strong restriction on the length of posted messages which can be no
+%%   longer than 140 characters. Upon exceeding this length, tweets get
+%%   automatically truncated to the maximal allowed length.}
 
@@
 \begin{enumerate}
-  \item @-tokens, e.g. \textit{@ZDFonline};
-  \item hashtags, e.g. \textit{\#Kleinanzeigen};
-  \item links, e.g. \textit{http://t.co};
-  \item smileys, e.g. \textit{:-P};
-  \item slang, e.g. \textit{OMG}.
+  \item @-tokens, e.g. \textit{@ZDFonline}, \textit{@sechsdreinuller};
+  \item hashtags, e.g. \textit{\#Kleinanzeigen}, \textit{\#wetter};
+  \item links, e.g. \textit{http://t.co}, \textit{sueddeutsche.de};
+  \item smileys, e.g. \textit{:-P}, \textit{xD};
+  \item slang, e.g. \textit{OMG}, \textit{WTF} etc.
 \end{enumerate}
@@
 \textit{ned} instead of \textit{nicht} or \textit{grad} instead of
-\textit{gerade} and were marked both as \textit{misspelling}s and
+\textit{gerade}, and were marked both as \textit{misspelling}s and
 \textit{slang} in our classification. A detailed statistics on the
@@
 1,235 times in our texts and was by far the most frequent OOV in
-analyzed data, was recognized as out-of-vocabulary by
+analyzed data set, was recognized as out-of-vocabulary by
 \texttt{hunspell} but was not deemed as such by
@@
 
-But an even more important conclusion which can be drawn from the
+However, an even more important conclusion which can be drawn from the
 analyzed data is the fact that for both \texttt{TreeTagger} and
@@
 \subsection{Replacement of Twitter-Specific Phenomena}
-In August 2007, Chris Messina, a renowned advocate of open-source
-community, sent out a Twitter message suggesting that the pound sign
-could be used for organizing groups on Twitter (cf. Parker,
-\cite{parker}). The ``hash godfather'', as Chris Messina described
-himself, allegedly borrowed this idea from Internet Relay Chats (IRC)
--- the forebears of modern social networks -- which have been using
-the ``\#{}''-sign to mark channel names since the early 1990s.
+According to Parker (\cite{parker}), hasthags were supposedly
+introduced by Chris Messina, a renowned advocate of open-source
+community, in August 2007. The ``hash godfather'', as Messina
+describes himself, presumably borrowed the idea of marking relevant
+topics with the ``\#''- sign from Internet Relay Chats (IRC) -- the
+forebears of modern social networks -- which have been using the pound
+character for marking their channel names since the early 1990s.
 
-Luckily for us, this ``novelty'' by Messina as well as @-tokens which
-are used in Twitter to mark names of user account, both have strict
-formal features by which these tokens could be identified. Other types
-of words which are usually considered as OOVs and also have
-unambiguous formal traits are hyperlinks, e-mail addresses, and
-smileys. The presence of such formal criteria suggests that these
-classes could best be handled by rule-methods and namely finite-state
-techniques like finite-state transducers (FST) (cf. Jurafsky and
-Martin, \cite{jurafsky}, pp.57-60).
+Luckily for us, this ``novelty'' by Messina brought along a strict
+formal feature by which future hashtags could be identified. Other
+types of words which are usually considered as OOVs in Twitter but
+also have some unambiguous formal traits include at-tokens,
+hyperlinks, e-mail addresses, and smileys. The presence of such formal
+criteria suggests that these classes could best be handled by
+rule-based methods and namely finite-state techniques like
+finite-state transducers (FST) (cf. Jurafsky and Martin,
+\cite{jurafsky}, pp.57-60).
 
 For our purposes, we developed a prototypic Python system analogous to
-FSTs in which a set of regular expressions was associated with
-corresponding actions performed on matched subgroups. In this system,
-absolutely unambiguous tokens like web links and e-mail addresses were
-replaced with special words ``\%Mail'' and ``\%Link''
-correspondingly. Emoticons were replaced with tokens ``\%PosSmiley'',
-``\%NegSmiley'', depending on the type of emotion presumably conveyed
-by these expressions. In cases when an emoticon was ambiguous with
-regard to its polarity, it was replaced with the artificial word
-``\%Smiley''.
+an FST in which a set of regular expressions was associated with
+corresponding actions performed on matched subgroups in cases when
+these subgroups did not overlap. If some rules clashed together on
+certain contexts, a set of special criteria was used to determine
+which rule the preference should be given.
 
-Additionally to that, problematic UTF-8 characters like special quotes
-and ellipsis which caused incorrect work of tokenizer were converted
-to their corresponding ISO-8859-1 equivalents.
+In this system, unambiguous tokens like web links and e-mail addresses
+were replaced with an artificial word ``\%Mail''. Emoticons were
+substituted by tokens ``\%PosSmiley'' or ``\%NegSmiley'', depending on
+the type of emotion presumably conveyed by these expressions. In cases
+when an emoticon was ambiguous with regard to its polarity, it was
+replaced with the special word ``\%Smiley''. Furthermore, leading
+``\#{}'' characters were stripped off from the beginning of hashtags
+thus leaving only the alphabetic part of these tokens.
 
-For hashtags, we simply stripped off the pound character from the
-beginning of such words thus leaving only the alphabetic part of
-tokens. A more complicated case turned out to be the @-tokens. For
-them, we had to decide depending on the context whether these tokens
-played an important syntactic role in sentence or not. In cases they
-did, we additionally looked whether the alphabetic part following the
-``@'' character was present in dictionary. If it was, we only stripped
-the ``at'' character off, otherwise whole word was replaced with token
-``\%UserName''. In cases when @-tokens served as addresses or retweet
-marks, we deleted them from message completely since they were of
-little interest and importance for further syntactic and semantic
-analysis and could hardly be assigned a proper part-of-speech tag or
-syntactic role.
-
-All the artificially introduced words were added to custom user
-dictionaries of \texttt{TreeTagger} and \texttt{hunspell}. For
-tagging, we assigned NE tags to all artificial words except for
-emoticon replacements which got the tag INJ. Additionally, positions
-and lengths of all replacements we remembered along with original
-words which were replaced and a restoration step to original forms was
-performed for certain classes of tokens after tagging.
+A more complicated case turned out to be the at-tokens and
+hyperlinks. For them, we had to disambiguate whether these words
+played a certain syntactic role in a sentence or could be easily
+omitted without breaking the syntactic structure. In the former case,
+these words were replaced with artificial counterparts. In the latter
+case, such words were deleted from sentence in order not to confuse
+further intended parsing processing.
 
@@
 
+All the artificial words were added to custom user dictionaries of
+\texttt{TreeTagger} and \texttt{hunspell}. For tagging, we assigned NE
+tags to all artificial tokens with the only exception of emoticon
+replacements which got the tag INJ. Furthermore, positions and lengths
+of all replacements we remembered along with original words which were
+replaced and a restoration step to original forms was performed for
+certain classes of tokens after tagging.
+
 %
 \subsection{Restoration of misspellings}
-%
-\subsubsection{Restoration of Umlauts}
-%
-\subsubsection{Squeezing of Elongated Words}
-%
-\subsubsection{Translation of Slang Misspellings}
+
 %

### 2013-08-13 darmstadt_gscl_2013/article_twitter_normalization.tex
misspelling section expanded

@@
 \usepackage{url}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\uniqoov}{\% of unique OOVs}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \pagestyle{headings}  % switches on printing of running heads
-\title{MT @HanBaldwin: Fightin OOVs in German \#twitter}
-\titlerunning{Makn Sens a Germa \#twitter}  % abbreviated title (for running head)
+\title{Rule-Based Normalization of German Twitter Messages}
+\titlerunning{Rule-Based Normalization of German Twets}  % abbreviated title (for running head)
 %                                     also used for the TOC unless
@@
 \begin{enumerate}
-\item regular German words, e.g. \textit{meins},
+\item regular German words, e.g. \textit{Piraterie},
   \textit{losziehen};\label{regular}
@@
 
-Luckily for us, this ``novelty'' by Messina brought along a strict
+Luckily for us, this Messina's ``novelty'' brought along a strict
 formal feature by which future hashtags could be identified. Other
-types of words which are usually considered as OOVs in Twitter but
-also have some unambiguous formal traits include at-tokens,
-hyperlinks, e-mail addresses, and smileys. The presence of such formal
-criteria suggests that these classes could best be handled by
-rule-based methods and namely finite-state techniques like
-finite-state transducers (FST) (cf. Jurafsky and Martin,
-\cite{jurafsky}, pp.57-60).
+types of words which also are usually considered as OOVs in Twitter
+but have unambiguous formal traits are at-tokens, hyperlinks, e-mail
+addresses, and smileys. The presence of such formal criteria suggests
+that these classes could best be handled by rule-based methods and
+namely finite-state techniques like finite-state transducers (FST)
+(cf. Jurafsky and Martin, \cite{jurafsky}, pp.57-60).
 
@@
 an FST in which a set of regular expressions was associated with
-corresponding actions performed on matched subgroups in cases when
-these subgroups did not overlap. If some rules clashed together on
-certain contexts, a set of special criteria was used to determine
-which rule the preference should be given.
+corresponding actions performed on matched subgroups. If some rules'
+subgroups clashed together on certain contexts, a set of special
+criteria was used to determine which rule had to be preferred. These
+criteria involved length of text spans matched by subgroups, length of
+left and right context mathced by corresponding regular expressions,
+and, finally, the order in which these expressions appeared in rule
+file.
 
-In this system, unambiguous tokens like web links and e-mail addresses
+In our system, unambiguous tokens like, for example, e-mail addresses
 were replaced with an artificial word ``\%Mail''. Emoticons were
@@
 hyperlinks. For them, we had to disambiguate whether these words
-played a certain syntactic role in a sentence or could be easily
-omitted without breaking the syntactic structure. In the former case,
-these words were replaced with artificial counterparts. In the latter
-case, such words were deleted from sentence in order not to confuse
-further intended parsing processing.
+played an important syntactic role in sentence or not. In the former
+case, these words were replaced with artificial counterparts. In the
+latter case, such words were deleted from sentence in order not to
+confuse further intended parsing processing.
 
-Precision, recall and F1 score for replacement of Twitter-specific
-phenomena is shown in Table \ref{table:tw-phenomen-metrics}.
+Precision, recall and F1 metrics for replacement of Twitter-specific
+phenomena are shown in Table \ref{table:tw-phenomen-metrics}.
 
@@
 replacements which got the tag INJ. Furthermore, positions and lengths
-of all replacements we remembered along with original words which were
-replaced and a restoration step to original forms was performed for
-certain classes of tokens after tagging.
+of all replacements we remembered along with the original words which
+were replaced, and a restoration step to original forms was performed
+for user names after tagging.
 
@@
 
+A closer look at unknown words which were classified as misspellings
+revealed that a prevailing majority of them was considered as
+colloquial spelling variants. Such spellings accounted for 70.5~\% of
+detected spelling mistakes in \texttt{hunspell} data and 66.17~\% of
+misspellings recognized by \texttt{TreeTagger}. Frequency distribution
+of colloquial and non-colloquial misspellings for data analyzed with
+either tools is shown in Figures \ref{fig:misspl-hunspell} and
+\ref{fig:misspl-ttagger}.
+...
+%% \begin{minipage}[t]{0.45\textwidth}
+%%   \begin{figure}[!ht]\label{fig:misspl-hunspell}
+%%   \end{figure}
+%% \end{minipage}
+
+%% \begin{minipage}[t]{0.45\textwidth}
+%%   \begin{figure}[!ht]\label{fig:misspl-ttagger}
+%%   \end{figure}
+%% \end{minipage}
+
+As can be seen from the Figures, both kinds of spelling variations
+have nearly Zipfian distribution. However colloquial spelling
+variants, if used, tend to be used frequently whereas non-colloquial
+misspellings are rather represented by sporadic singleton cases. This
+could be explained by fact that colloquial spellings are usually
+formed by systematic rewriting processes. These processes are supposed
+to make written form of words more similar to their casual soundings
+in everyday speech. According to our data, the most productive of such
+processes were:
+\begin{itemize}
+  \item Omissions of `e' in unstressed (``schwa'') positions,
+    e.g. \textit{w\"urd}, \textit{zuguckn} etc. In cases when `e' was
+    part of the impersonal pronoun ``es'' and followed a verb,
+    remaining `s' was usually appended to the preceding verb form;
+
+  \item Complete omissions or replacement of final consonants with
+    their voiceless equivalents, e.g. \textit{nich} instead of
+    \textit{nicht} or \textit{Tach} instead of \textit{Tag};
+
+  \item Omissions of `ei' from indefinite articles, e.g. \textit{ne}
+    instead of \textit{eine} or \textit{nem} in lieu of
+    \textit{einem};
+
+  \item Multiple repetions of characters as a means of expressing
+    elongation of sounds, e.g. \textit{Hilfeeee},
+    \textit{s\"u\"u\"u\ss};
+\end{itemize}
+
 %
 \section{Evaluation}\label{evaluation}
+To evaluate our system, we used metrics
 
-\section{Conclusion}\label{concl}
+\section{Conclusion}\label{conclusion}
 

### 2013-08-14 darmstadt_gscl_2013/article_twitter_normalization.tex
final sections updated with stubs

@@
 \usepackage{tabularx} % for centering in table
+\usepackage{graphicx} % for \includegraphics
 \usepackage{url}
@@
 \subsection{Replacement of Twitter-Specific Phenomena}
-According to Parker (\cite{parker}), hasthags were supposedly
-introduced by Chris Messina, a renowned advocate of open-source
-community, in August 2007. The ``hash godfather'', as Messina
-describes himself, presumably borrowed the idea of marking relevant
-topics with the ``\#''- sign from Internet Relay Chats (IRC) -- the
-forebears of modern social networks -- which have been using the pound
-character for marking their channel names since the early 1990s.
+According to Parker (\cite{parker}), hasthags were presumably introduced by
+Chris Messina, a renowned advocate of open-source community, in August
+2007. The ``hash godfather'', as Messina describes himself, allegedly borrowed
+the idea of marking relevant topics with the ``\#''- sign from Internet Relay
+Chats (IRC) -- the forebears of modern social networks -- which have been
+using the pound character for marking their channel names since the early
+1990s.
 
-Luckily for us, this Messina's ``novelty'' brought along a strict
-formal feature by which future hashtags could be identified. Other
-types of words which also are usually considered as OOVs in Twitter
-but have unambiguous formal traits are at-tokens, hyperlinks, e-mail
-addresses, and smileys. The presence of such formal criteria suggests
-that these classes could best be handled by rule-based methods and
-namely finite-state techniques like finite-state transducers (FST)
-(cf. Jurafsky and Martin, \cite{jurafsky}, pp.57-60).
+Luckily for us, this Messina's ``novelty'' brought along a strict formal
+feature by which future hashtags could be identified. Other types of words
+which also are usually considered as OOVs in Twitter but have unambiguous
+formal traits are at-tokens, hyperlinks, e-mail addresses, and smileys. The
+presence of such formal criteria suggests that these classes could best be
+handled by rule-based methods and namely finite-state techniques like
+finite-state transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
+pp.57-60).
 
@@
 
-In our system, unambiguous tokens like, for example, e-mail addresses
-were replaced with an artificial word ``\%Mail''. Emoticons were
-substituted by tokens ``\%PosSmiley'' or ``\%NegSmiley'', depending on
-the type of emotion presumably conveyed by these expressions. In cases
-when an emoticon was ambiguous with regard to its polarity, it was
-replaced with the special word ``\%Smiley''. Furthermore, leading
-``\#{}'' characters were stripped off from the beginning of hashtags
-thus leaving only the alphabetic part of these tokens.
+In our system, unambiguous tokens like, for example, e-mail addresses were
+replaced with an artificial word ``\%Mail''. Emoticons were substituted by
+tokens ``\%PosSmiley'' or ``\%NegSmiley'' depending on the type of emotion
+presumably conveyed by these expressions. In cases when an emoticon was
+ambiguous with regard to its polarity, it was replaced with the special word
+``\%Smiley''. Furthermore, leading ``\#{}'' characters were stripped off from
+the beginning of hashtags thus leaving only the alphabetic part of these
+tokens.
 
-A more complicated case turned out to be the at-tokens and
-hyperlinks. For them, we had to disambiguate whether these words
-played an important syntactic role in sentence or not. In the former
-case, these words were replaced with artificial counterparts. In the
-latter case, such words were deleted from sentence in order not to
-confuse further intended parsing processing.
+A more complicated case turned out to be the at-tokens and hyperlinks. For
+them, we had to disambiguate whether these words played an important syntactic
+role in sentence or not. In the former case, these words were replaced with
+artificial counterparts. In the latter case, such words were deleted from
+sentence in order not to confuse further intended parsing processing.
 
-Precision, recall and F1 metrics for replacement of Twitter-specific
-phenomena are shown in Table \ref{table:tw-phenomen-metrics}.
+Precision, recall and F1 metrics for replacement of Twitter-specific phenomena
+are shown in Table \ref{table:tw-phenomen-metrics}.
 
@@
 All the artificial words were added to custom user dictionaries of
-\texttt{TreeTagger} and \texttt{hunspell}. For tagging, we assigned NE
-tags to all artificial tokens with the only exception of emoticon
-replacements which got the tag INJ. Furthermore, positions and lengths
-of all replacements we remembered along with the original words which
-were replaced, and a restoration step to original forms was performed
-for user names after tagging.
+\texttt{TreeTagger} and \texttt{hunspell}. For tagging, we assigned NE tags to
+all artificial tokens with the only exception of emoticon replacements which
+got the tag INJ. Furthermore, positions and lengths of all replacements we
+remembered along with the original words which were replaced, and a
+restoration step to original forms was performed for user names after tagging.
 
@@
 
-A closer look at unknown words which were classified as misspellings
-revealed that a prevailing majority of them was considered as
-colloquial spelling variants. Such spellings accounted for 70.5~\% of
-detected spelling mistakes in \texttt{hunspell} data and 66.17~\% of
-misspellings recognized by \texttt{TreeTagger}. Frequency distribution
-of colloquial and non-colloquial misspellings for data analyzed with
-either tools is shown in Figures \ref{fig:misspl-hunspell} and
-\ref{fig:misspl-ttagger}.
-...
-%% \begin{minipage}[t]{0.45\textwidth}
-%%   \begin{figure}[!ht]\label{fig:misspl-hunspell}
-%%   \end{figure}
-%% \end{minipage}
+A closer look at unknown words which were classified as misspellings revealed
+that a prevailing majority of them was considered as colloquial spelling
+variants. Such variants accounted for 70.5~\% of detected spelling mistakes in
+\texttt{hunspell} data and for 66.17~\% of misspellings recognized by
+\texttt{TreeTagger}. Frequency distributions of colloquial and non-colloquial
+misspellings in data analyzed with either tools are shown in Figures
+\ref{fig:misspl-hunspell} and \ref{fig:misspl-ttagger}.
+\begin{figure}[ht]
+  \centering
+  \begin{minipage}[b]{0.45\linewidth}
+    \caption{Frequency distributions of non-standard spellings in data
+      analyzed with \texttt{hunspell}}
+    \includegraphics[width=\textwidth]{data/img/hunspell_spell.png}
+    \label{fig:misspl-hunspell}
+  \end{minipage}
+  \hspace{0.5cm}
+  \begin{minipage}[b]{0.45\linewidth}
+    \caption{Frequency distributions of non-standard spellings in data
+      analyzed with \texttt{TreeTagger}}
+    \includegraphics[width=\textwidth]{data/img/treetagger_spell.png}
+    \label{fig:misspl-ttagger}
+  \end{minipage}
+\end{figure}
 
-%% \begin{minipage}[t]{0.45\textwidth}
-%%   \begin{figure}[!ht]\label{fig:misspl-ttagger}
-%%   \end{figure}
-%% \end{minipage}
-
-As can be seen from the Figures, both kinds of spelling variations
-have nearly Zipfian distribution. However colloquial spelling
-variants, if used, tend to be used frequently whereas non-colloquial
-misspellings are rather represented by sporadic singleton cases. This
-could be explained by fact that colloquial spellings are usually
-formed by systematic rewriting processes. These processes are supposed
-to make written form of words more similar to their casual soundings
-in everyday speech. According to our data, the most productive of such
-processes were:
+As can be seen from the figures, both kinds of spelling variations have nearly
+Zipfian distribution. However colloquial spelling variants, if used, tend to
+be used frequently whereas non-colloquial misspellings are rather represented
+by sporadic singletons. This could be explained by the fact that colloquial
+spellings are usually formed by systematic rewriting processes. These
+processes are supposed to make written form of words more similar to their
+casual soundings in everyday speech. According to our data, the most
+productive of such processes were:
 \begin{itemize}
   \item Omissions of `e' in unstressed (``schwa'') positions,
-    e.g. \textit{w\"urd}, \textit{zuguckn} etc. In cases when `e' was
-    part of the impersonal pronoun ``es'' and followed a verb,
-    remaining `s' was usually appended to the preceding verb form;
+    e.g. \textit{w\"urd}, \textit{zuguckn} etc. In cases when `e' was part of
+    the impersonal pronoun ``es'' following a verb, remaining `s' of this
+    pronoun was usually appended to the preceding verb form;
 
-  \item Complete omissions or replacement of final consonants with
-    their voiceless equivalents, e.g. \textit{nich} instead of
-    \textit{nicht} or \textit{Tach} instead of \textit{Tag};
+  \item Complete omissions or replacements of final consonants with their
+    voiceless equivalents, e.g. \textit{nich} instead of \textit{nicht} or
+    \textit{Tach} instead of \textit{Tag};
 
-  \item Omissions of `ei' from indefinite articles, e.g. \textit{ne}
-    instead of \textit{eine} or \textit{nem} in lieu of
-    \textit{einem};
+  \item Omissions of `ei' from indefinite articles, e.g. \textit{ne} instead
+    of \textit{eine} or \textit{nem} in lieu of \textit{einem};
 
-  \item Multiple repetions of characters as a means of expressing
-    elongation of sounds, e.g. \textit{Hilfeeee},
-    \textit{s\"u\"u\"u\ss};
+  \item Multiple repetions of characters as a means of expressing elongation
+    of sounds, e.g. \textit{Hilfeeee}, \textit{s\"u\"u\"u\ss};
 \end{itemize}
+
+Since all of the above processes followed some specific formation patterns. We
+developed a set of reverese transformation rules which first captured tokens
+with suspicious character sequences, checked them in the dictionary, and if
+these words were not found there, a transformation associated with each
+matched incorrect character sequence was applied.
+
+TODO: more detailed and coherent description of rule module
+
+Unfortunately, spelling variants which were classified as true misspellings
+did not show any regularities except for cases of incorrect spelling of sharp
+``s'' and umlauts. While writting of ``ss'' instead of sharp ``s'' could also
+be considered as correct variant with regard to the Swiss norm. For umlauts, a
+straightforward replacement of character sequences like ``ae'', ``oe'' or
+``ue'' because these character sequences also appeared in regular German words
+like ``israelisch'' or ``quer''. Therefore a set of exceptional cases had to
+be found before applying substitutions. As a possible source of such
+exceptions we considered words classified by us as in-vocabulary or valid
+out-of-vocabulary terms. Another source of possible exceptions was a corpus of
+newspaper texts which by definition were supposed to contain only proof-read
+content. To derive exceptional character sequences, we subsequently expanded
+the substrings to the left and to the right or simultaneously to both
+directions until these subsequence only captured words present in our
+``normal'' data without capturing any misspeling from the list. After having
+collected exceptions, we only applied replacement operation to text spans
+lying in between exceptional substrings. On another test set of 500 cases,
+this method turned out to have made only one mistake. It replaced the word
+``zuende'' with ``z\"unde'' in the sentence ``RT @Netznarr: Als Amtstr\"ager
+wei\ss man, dass es zuende geht, wenn man in Umfragen unbeliebter als
+Westerwelle ist. \#Wulff''
+
+TODO: should be described as algorithm, should the same approach be tried for
+other misspelling char sequences?
 
@@
 \section{Evaluation}\label{evaluation}
-To evaluate our system, we used metrics
+To evaluate our system, we first performed an intrinsic evaluation by
+measuring the rate by which the amount of unknown tokens was reduced for
+\texttt{TreeTagger} and \texttt{hunspell}.
+
+TODO: figures for OOV rates after normalization.
+
+To comply with metrics commonly used for evaluating text normalization
+procedures for other languages, we also measured word error rate (WER) and
+sentence error rate (SER) for restoration of non-standard and incorrect
+spellings.
+
+TODO: WER and SER figures after normalization.
+
+Finally, as a first step towards an extrinsic evaluation, we measured
+\texttt{TreeTagger}
+
+TODO: Figures for tagging quality before and after normalization.
 
@@
 
-%% This article provided an overview of exisiting approaches to noisy
-%% text normalization task. Additionally, all mentioned methods were
-%% classified on the basis of two independent criteria. In section
-%% \ref{error:analysis}, we performed qulitative and quantitive analyses
-%% of out-of-vocabulary words in German tweets and suggested a set of
-%% ad-hoc techniques for mitigating their potential negative influence on
-%% natural language processing. This procedure allowed us to reduce the
-%% total OOV rate by ... \% for \texttt{hunspell} and by ... \% for
-%% \texttt{TreeTagger}.
+With this article, we hope to have provided a better insight into the nature
+and composition of ill-formed words in German Twitter messages. As was shown
+in Section \ref{error:analysis}, special markup elements and casual sppellings
+account for more than a half unknown words discovered in Tweets. Furthermore,
+almost three quarters of non-standard spellings could be regarded as
+colloquial spelling variants rather than occasional slip of the finger. Such
+colloquial spellings also showed the tendency to be formed by well formalized
+processes and to be used over and over again in texts.
 
-%% Nevertheless, we should honestly admit that our system still has
-%% potential for development and research, since it mainly addresses only
-%% one of three main groups of OOV tokens. Future directions should
-%% certainly include a more thorough tackling of unintentional spelling
-%% mistakes and especially their most prominent types -- deletions and
-%% substitutions.
+We also suggested a rule-based text normalization approach which could serve
+as a baseline comparison measure for future normalization methods which may be
+suggested for German tweets. As was shown in previous sections, our approach
+could effectively address some ofthe most frequent phenomena which contribute
+to a higher rate of out-of-vocabulary words in Twitter texts such as
+Twitter-specific elements and non-standard spellings.
 
-%% Furthemore, a better evalution technique as well as comparison with
-%% other systems are needed for our normalization procedure. On the one
-%% hand, an \textit{extrinsic} evaluation should be performed (cf. Sparck
-%% Jones and Galliers, \cite{sparck}) which means that we not only have
-%% to show how the rate of OOV words goes down but much more how this
-%% lower OOV rate affects the work of the whole NLP system. On the other
-%% hand, we need to assess the quality of our procedure's work on the
-%% basis of metrics used by other researchers.
+We are going to make our classification and test data available online at
+\url{http://dasom.ling.uni-potsdam.de/} under the terms consistent with
+Twitter regulations. Our classified data could, in our opinion, significantly
+save tedious manual work for other researchers.
 
-%% One possible estimation criterion which was used by Aw et
-%% al. (\cite{aw}), Kaufmann (\cite{kaufmann}), Beaufort et
-%% al. (\cite{beaufort}), and Oliva et al. (\cite{oliva}) is the BLEU
-%% score (Papineni et al., \cite{papineni}). Another possibility would be
-%% to use the Word (WER) and Sentence Error Rates (SER) as suggested by
-%% Kobus et al. (\cite{kobus}). However, an obvious difficulty that we
-%% already encountered here is that both metrics highly rely on a
-%% subjective notion of the look of a ``normalized'' message. While the
-%% BLEU score could be an approriate criterion for normalization of
-%% messages like ``i luv ma mather and wd do evrythin 4 her'' which in
-%% fact looks like as if it were not English. But such highly distorted
-%% tweets are rather atypical for German. In this regard, WER and SER
-%% could be considered as more appropriate measurement criteria. But
-%% these metrics once again are rather dealing with spelling mistakes and
-%% would highly depend on whether one, for example, would consider the
-%% hash sign in a hashtag as an error.
+Admittedly, our method still could be further refined and improved. As
+possible steps for such refinement, we see a possible addition of a
+machine-learning classifier which could help distinguish spelling mistakes
+from valid unknown words. On the other side, a better disambiguation of
+suggested replacement variants for misspellings could be achieved by letting
+part-of-speech tagger process a word grid with input tokens and their
+suggested replacements. At the end of tagging, not only the most probable tag
+sequence but the most likely word/tag mesh could be chosen in a single run. At
+any rate, these steps are beyond the scope of this work. But we hope to have
+laid the groundwork for them.
 
@@
 
-This work was financially supported by ... as part of collaborative
-project ``...''. The authors are also thankful to ... for help with
-the analysis of data.
+This work was financially supported by ... as part of collaborative project
+``...''. The authors are also thankful to ... for help with the analysis of
+data.
 

### 2013-08-15 darmstadt_gscl_2013/article_twitter_normalization.tex
minor changes

@@
 order to avoid this, we instead suggest using separate classifications
-for each type of involved characterizing criterion.
+for each type of involved criteria.
 
@@
 collected corpus, split them into sentences and tokenized using social
-media-aware tokenizer by Christopher Potts
-\footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}.
+media-aware tokenizer by Christopher Potts.
+\footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}
 After skipping all words which did not contain any alphabetic
@@
     supposedly were rare or did not exist at the time when
-    dictionaries were created. Another reason for inclusion in this
-    type was the belonging of a word to an open lexical or
+    dictionaries were created. Another reason for the inclusion in
+    this type was the belonging of a word to an open lexical or
     part-of-speech class (like, for example, named entities or
@@
     impossibility to fully cover them;\label{dict}
-  \item \textbf{Sloppiness of users' input}. In the scope of this
-    second group, we considered incorrect spellings of words
-    encountered in text;\label{spell}
   \item \textbf{Stylistic specifics of text genre}. This group
@@
     in the domain of web discourse or more specifically in Twitter
-    communication.\label{style}
+    communication;\label{style}
+  \item \textbf{Sloppiness of users' input}. In the scope of this
+    group, we considered incorrect spellings of words encountered in
+    text.\label{spell}
 \end{enumerate}
@@
 
-In Table \ref{table:mrd}, percentage figures for each of the above
-subgroups are shown. We have considered OOV-distributions for both
-\texttt{hunspell} and \texttt{TreeTagger}. For each of them, we
-estimated the percentage of a particular subclass with regard to the
-total number of occurrences of all OOV-tokens (column ``\totaloov{}'')
-as well as with regard to their percentage rate in the list of only
-unique OOVs disregarding frequencies (column ``\uniqoov{}'').
+In Table \ref{table:mrd} on Page \pageref{table:mrd}, percentage
+figures for each of the above subgroups are shown. We have considered
+OOV-distributions for both \texttt{hunspell} and
+\texttt{TreeTagger}. For each of them, we estimated the percentage of
+a particular subclass with regard to the total number of occurrences
+of all OOVs (column ``\totaloov{}'') as well as with regard to their
+percentage rate in the list of only unique unknown tokens disregarding
+their frequencies (column ``\uniqoov{}'').
 \begin{table}
@@
 
-Similarly to class \ref{dict}, we subdivided the group ``Sloppiness of
-users' input'' into the following subgroups:
-\begin{enumerate}
-  \item insertions, e.g. \textit{dennen} instead of \textit{denen};
-  \item deletions, e.g. \textit{scho} instead of \textit{schon};
-  \item substitutions, e.g. \textit{fur} instead of \textit{f\"ur};
-\end{enumerate}
-according to the type of operation which led to a particular spelling
-mistake. In cases when multiple different operations were involved
-simultaneously, we explicitly marked each of these operations in our
-data. Statistical distribution of these subclasses is shown in Table
-\ref{table:spell}.
-\begin{table}
-  \caption{Distribution of OOV words belonging to the class
-    ``Sloppiness of users' input''\label{table:spell}}
-  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
-    \hline\noalign{\smallskip}
-    \multirow{2}{*}{OOV subclass} & %
-    \multicolumn{2}{c}{\texttt{hunspell}} & %
-    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
-    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
-    \noalign{\smallskip} \hline
-    insertions & 0.49 & 1 & 0.18 & 0.34 \\
-    deletions & 8.44 & 6.38 & 6.52 & 5.27 \\
-    substitutions & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
-    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
-    \noalign{\smallskip} \hline
-  \end{tabular}
-\end{table}
-
-%% As is clear from the table, deletions are by far the most common type
-%% of misspellings. The reasons for that are either relatively frequent
-%% omissions of characters made by users or even more often automatic
-%% truncations of too long messages which are performed by Twitter
-%% service itself.\footnote{As is generally known, Twitter imposes a
-%%   strong restriction on the length of posted messages which can be no
-%%   longer than 140 characters. Upon exceeding this length, tweets get
-%%   automatically truncated to the maximal allowed length.}
-
-Finally, the third group -- ``Stylistic specifics of text genre'' --
-was subdivided into the subgroups:
+Similarly to class \ref{dict}, we subdivided the group -- ``Stylistic
+specifics of text genre'' -- into the following subgroups:
 \begin{enumerate}
@@
 \end{enumerate}
-according to the formal or lexical class which the tokens belonged
-to. Additionally, we also considered as \textit{slang} spelling
-variants of standard language words which could be regarded as their
-colloquial equivalents. Such words included cases like, for example,
-\textit{ned} instead of \textit{nicht} or \textit{grad} instead of
-\textit{gerade}, and were marked both as \textit{misspelling}s and
-\textit{slang} in our classification. A detailed statistics on the
-subgroups of class 3 is shown in Table \ref{table:style}:
+according to the formal or lexical class which tokens of this group
+belonged to. Additionally, spelling variants of standard language
+words which could also be regarded as their colloquial equivalents
+like, for example, \textit{ned} instead of \textit{nicht} or
+\textit{grad} instead of \textit{gerade}, were considered by us both
+as \textit{misspelling}s and as \textit{slang} in our
+classification. A detailed statistics on the subgroups of class
+\ref{style} is shown in Table \ref{table:style}:
 \begin{table}
@@
 analyzed data set, was recognized as out-of-vocabulary by
-\texttt{hunspell} but was not deemed as such by
-\texttt{TreeTagger}. Luckily, such singleton cases were rather rare
-exceptions during the analyses and did not affect much the remaining
-classes of OOVs, so that distributions of unknown tokens for both
-tools were more or less similar or at least comparable to a certain
-extent.
+\texttt{hunspell} but was not deemed as such by \texttt{TreeTagger}.
 
-However, an even more important conclusion which can be drawn from the
+Finally, the last group -- ``Sloppiness of users' input'' -- was split
+into the following subclasses:
+\begin{enumerate}
+  \item insertions, e.g. \textit{dennen} instead of \textit{denen};
+  \item deletions, e.g. \textit{scho} instead of \textit{schon};
+  \item substitutions, e.g. \textit{fur} instead of \textit{f\"ur};
+\end{enumerate}
+according to the type of operation which led to a particular spelling
+mistake. In cases when multiple different operations were involved
+simultaneously on one word, we explicitly marked each of these
+operations in our data. Statistical distribution of these subclasses
+is shown in Table \ref{table:spell}.
+\begin{table}
+  \caption{Distribution of OOV words belonging to the class
+    ``Sloppiness of users' input''\label{table:spell}}
+  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
+    \hline\noalign{\smallskip}
+    \multirow{2}{*}{OOV subclass} & %
+    \multicolumn{2}{c}{\texttt{hunspell}} & %
+    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
+    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
+    \noalign{\smallskip} \hline
+    insertions & 0.49 & 1 & 0.18 & 0.34 \\
+    deletions & 8.44 & 6.38 & 6.52 & 5.27 \\
+    substitutions & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
+    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
+    \noalign{\smallskip} \hline
+  \end{tabular}
+\end{table}
+
+As is clear from the Table, deletions are by far the most common type
+of misspellings. The reasons for that are either relatively frequent
+omissions of characters made by users or even more often automatic
+truncations of too long messages which are performed by Twitter
+service itself.\footnote{As is generally known, Twitter imposes a
+  strong restriction on the length of posted messages which can be no
+  longer than 140 characters. Upon exceeding this length, tweets get
+  automatically truncated to the maximal allowed length.}
+
+But an even more important conclusion that can be drawn from the
 analyzed data is the fact that for both \texttt{TreeTagger} and
-\texttt{hunspell}, Twitter-specific phenomena like special tokens,
-colloquial expressions or sloppily typed words accounted for more than
-a half of all unknown words found during the analysis. Since different
-classes of these Twitter phenomena were formed by different processes
-and also have different degrees of ambiguity, we will suggest
-different normalization procedures for each of them in the next
-Section.
+\texttt{hunspell}, Twitter-specific phenomena like specially marked
+tokens, colloquial expressions or sloppily typed words accounted for
+more than a half of all OOVs found during the analysis. And since
+different classes of these Internet-based communication phenomena were
+formed by different processes and also showed different degrees of
+ambiguity, they should most probably be differently normalized
+depending on the characteristics they show.
 
@@
 \subsection{Replacement of Twitter-Specific Phenomena}
-According to Parker (\cite{parker}), hasthags were presumably introduced by
-Chris Messina, a renowned advocate of open-source community, in August
-2007. The ``hash godfather'', as Messina describes himself, allegedly borrowed
-the idea of marking relevant topics with the ``\#''- sign from Internet Relay
-Chats (IRC) -- the forebears of modern social networks -- which have been
-using the pound character for marking their channel names since the early
-1990s.
+According to Parker (\cite{parker}), hasthags were presumably
+introduced by Chris Messina, a renowned advocate of open-source
+community, in August 2007. The ``hash godfather'', as Messina calls
+himself, allegedly borrowed the idea of marking relevant topics in
+messages with the ``\#''- sign from Internet Relay Chats (IRC) -- the
+forebears of modern social networks -- which have been using the pound
+character for marking their channel names since the early 1990s.
 
-Luckily for us, this Messina's ``novelty'' brought along a strict formal
-feature by which future hashtags could be identified. Other types of words
-which also are usually considered as OOVs in Twitter but have unambiguous
-formal traits are at-tokens, hyperlinks, e-mail addresses, and smileys. The
-presence of such formal criteria suggests that these classes could best be
-handled by rule-based methods and namely finite-state techniques like
-finite-state transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
+Luckily for us, this markup ``novelty'' brought along a strict formal
+feature by which future hashtags could be identified. Other types of
+words which are also usually considered as OOVs in Twitter but have
+unambiguous traits in their written form are at-tokens, hyperlinks,
+e-mail addresses, and smileys. The presence of such formal criteria
+suggests that these classes could best be handled by rule-based
+methods and namely finite-state techniques like finite-state
+transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
 pp.57-60).
@@
 an FST in which a set of regular expressions was associated with
-corresponding actions performed on matched subgroups. If some rules'
-subgroups clashed together on certain contexts, a set of special
-criteria was used to determine which rule had to be preferred. These
-criteria involved length of text spans matched by subgroups, length of
-left and right context mathced by corresponding regular expressions,
-and, finally, the order in which these expressions appeared in rule
-file.
+corresponding actions performed on matched subgroups. In this system,
+unambiguous tokens like, for example, e-mail addresses were replaced
+with an artificial word ``\%Mail''. Emoticons were substituted by
+tokens ``\%PosSmiley'' or ``\%NegSmiley'' depending on the type of
+emotion presumably conveyed by these expressions. In cases when an
+emoticon was ambiguous with regard to its polarity, it was replaced
+with the special word ``\%Smiley''. Furthermore, leading ``\#{}''
+characters were stripped off from the beginning of hashtags thus
+leaving only the alphabetic part of these tokens.
 
-In our system, unambiguous tokens like, for example, e-mail addresses were
-replaced with an artificial word ``\%Mail''. Emoticons were substituted by
-tokens ``\%PosSmiley'' or ``\%NegSmiley'' depending on the type of emotion
-presumably conveyed by these expressions. In cases when an emoticon was
-ambiguous with regard to its polarity, it was replaced with the special word
-``\%Smiley''. Furthermore, leading ``\#{}'' characters were stripped off from
-the beginning of hashtags thus leaving only the alphabetic part of these
-tokens.
+A more complicated case turned out to be the at-mentions and
+hyperlinks. For them, we had to disambiguate whether these words
+played an important syntactic role in sentence or could be easily
+omitted without breaking the syntactic structure. In the former case,
+these words were replaced with artificial counterparts. In the latter
+case, such words were deleted from sentence in order not to confuse
+further intended parsing processing.
 
-A more complicated case turned out to be the at-tokens and hyperlinks. For
-them, we had to disambiguate whether these words played an important syntactic
-role in sentence or not. In the former case, these words were replaced with
-artificial counterparts. In the latter case, such words were deleted from
-sentence in order not to confuse further intended parsing processing.
-
-Precision, recall and F1 metrics for replacement of Twitter-specific phenomena
-are shown in Table \ref{table:tw-phenomen-metrics}.
+We measured on 1,000 sentences how well our system could disambiguate
+contexts for the two above-mentioned classes and also how well it
+could recognize emoticons and assign them correct polarity. Our
+estimated precision, recall and F1 metrics are shown in Table
+\ref{table:tw-phenomen-metrics}.
 
@@
     OOV subclass & Precision & Recall & F1 score\\\hline
-    attoken & 98.87 & 98.87 & 98.87\\
-    link & 99.44 & 100.00 & 99.72\\
-    smiley & 93.79 & 76.26 & 84.12\\
+    at-mentions & 98.87 & 98.87 & 98.87\\
+    links & 99.44 & 100.00 & 99.72\\
+    smileys & 93.79 & 76.26 & 84.12\\
     \noalign{\smallskip} \hline
@@
 
-All the artificial words were added to custom user dictionaries of
-\texttt{TreeTagger} and \texttt{hunspell}. For tagging, we assigned NE tags to
-all artificial tokens with the only exception of emoticon replacements which
-got the tag INJ. Furthermore, positions and lengths of all replacements we
-remembered along with the original words which were replaced, and a
-restoration step to original forms was performed for user names after tagging.
+Additionally, all the artificial words were added to custom user
+dictionaries of \texttt{TreeTagger} and \texttt{hunspell}. For
+tagging, we assigned NE tags to all artificial tokens with the only
+exception of emoticon replacements which got the tag INJ. Furthermore,
+positions and lengths of all replacements we remembered along with the
+original words which were replaced, and a restoration step to original
+forms was performed for user names after tagging.
 
@@
 
-A closer look at unknown words which were classified as misspellings revealed
-that a prevailing majority of them was considered as colloquial spelling
-variants. Such variants accounted for 70.5~\% of detected spelling mistakes in
-\texttt{hunspell} data and for 66.17~\% of misspellings recognized by
-\texttt{TreeTagger}. Frequency distributions of colloquial and non-colloquial
-misspellings in data analyzed with either tools are shown in Figures
+A closer look at unknown words which were classified as misspellings
+revealed that a prevailing majority of them was considered as
+colloquial spelling variants. Such variants accounted for 70.5~\% of
+detected spelling mistakes in \texttt{hunspell} data and for 66.17~\%
+of misspellings recognized by \texttt{TreeTagger}. Frequency
+distributions of colloquial and non-colloquial misspellings in data
+analyzed with either tools are shown in Figures
 \ref{fig:misspl-hunspell} and \ref{fig:misspl-ttagger}.
@@
 
-As can be seen from the figures, both kinds of spelling variations have nearly
-Zipfian distribution. However colloquial spelling variants, if used, tend to
-be used frequently whereas non-colloquial misspellings are rather represented
-by sporadic singletons. This could be explained by the fact that colloquial
-spellings are usually formed by systematic rewriting processes. These
-processes are supposed to make written form of words more similar to their
-casual soundings in everyday speech. According to our data, the most
-productive of such processes were:
+As can be seen from the figures, both kinds of spelling variations
+have nearly Zipfian distribution. However colloquial spelling
+variants, if used, tend to be used frequently whereas non-colloquial
+misspellings are rather represented by sporadic singletons. This could
+be explained by the fact that colloquial spellings are usually formed
+by systematic rewriting processes which are also usually applied to
+frequently used words. True misspellings, on the contrary, are rather
+produced by occasional slips of the finger, so they neither have an
+apparent system in them nor they tend to reoccur in text.
+
+In order to investigate which processes were the most common sources
+of colloquial spellings
+
+These processes are supposed to make written form of words more
+similar to their casual soundings in everyday speech.
+
+According to our data, the most productive of such
+processes were:
 \begin{itemize}
@@
 
-Since all of the above processes followed some specific formation patterns. We
-developed a set of reverese transformation rules which first captured tokens
-with suspicious character sequences, checked them in the dictionary, and if
-these words were not found there, a transformation associated with each
-matched incorrect character sequence was applied.
+Since all of the above processes followed some specific formation
+patterns. We developed a set of reverese transformation rules which
+first captured tokens with suspicious character sequences, checked
+them in the dictionary, and if these words were not found there, a
+transformation associated with each matched incorrect character
+sequence was applied.
 
@@
 
-Unfortunately, spelling variants which were classified as true misspellings
-did not show any regularities except for cases of incorrect spelling of sharp
-``s'' and umlauts. While writting of ``ss'' instead of sharp ``s'' could also
-be considered as correct variant with regard to the Swiss norm. For umlauts, a
-straightforward replacement of character sequences like ``ae'', ``oe'' or
-``ue'' because these character sequences also appeared in regular German words
-like ``israelisch'' or ``quer''. Therefore a set of exceptional cases had to
-be found before applying substitutions. As a possible source of such
-exceptions we considered words classified by us as in-vocabulary or valid
-out-of-vocabulary terms. Another source of possible exceptions was a corpus of
-newspaper texts which by definition were supposed to contain only proof-read
-content. To derive exceptional character sequences, we subsequently expanded
-the substrings to the left and to the right or simultaneously to both
+Unfortunately, spelling variants which were classified as true
+misspellings did not show any regularities except for cases of
+incorrect spelling of sharp ``s'' and umlauts. While writting of
+``ss'' instead of sharp ``s'' could also be considered as correct
+variant with regard to the Swiss norm. For umlauts, a straightforward
+replacement of character sequences like ``ae'', ``oe'' or ``ue''
+because these character sequences also appeared in regular German
+words like ``israelisch'' or ``quer''. Therefore a set of exceptional
+cases had to be found before applying substitutions. As a possible
+source of such exceptions we considered words classified by us as
+in-vocabulary or valid out-of-vocabulary terms. Another source of
+possible exceptions was a corpus of newspaper texts which by
+definition were supposed to contain only proof-read content. To derive
+exceptional character sequences, we subsequently expanded the
+substrings to the left and to the right or simultaneously to both
 directions until these subsequence only captured words present in our
-``normal'' data without capturing any misspeling from the list. After having
-collected exceptions, we only applied replacement operation to text spans
-lying in between exceptional substrings. On another test set of 500 cases,
-this method turned out to have made only one mistake. It replaced the word
-``zuende'' with ``z\"unde'' in the sentence ``RT @Netznarr: Als Amtstr\"ager
-wei\ss man, dass es zuende geht, wenn man in Umfragen unbeliebter als
-Westerwelle ist. \#Wulff''
+``normal'' data without capturing any misspeling from the list. After
+having collected exceptions, we only applied replacement operation to
+text spans lying in between exceptional substrings. On another test
+set of 500 cases, this method turned out to have made only one
+mistake. It replaced the word ``zuende'' with ``z\"unde'' in the
+sentence ``RT @Netznarr: Als Amtstr\"ager wei\ss man, dass es zuende
+geht, wenn man in Umfragen unbeliebter als Westerwelle ist. \#Wulff''
 
-TODO: should be described as algorithm, should the same approach be tried for
-other misspelling char sequences?
+TODO: should be described as algorithm, should the same approach be
+tried for other misspelling char sequences?
 
@@
 To evaluate our system, we first performed an intrinsic evaluation by
-measuring the rate by which the amount of unknown tokens was reduced for
-\texttt{TreeTagger} and \texttt{hunspell}.
+measuring the rate by which the amount of unknown tokens was reduced
+for \texttt{TreeTagger} and \texttt{hunspell}.
 
@@
 To comply with metrics commonly used for evaluating text normalization
-procedures for other languages, we also measured word error rate (WER) and
-sentence error rate (SER) for restoration of non-standard and incorrect
-spellings.
+procedures for other languages, we also measured word error rate (WER)
+and sentence error rate (SER) for restoration of non-standard and
+incorrect spellings.
 
@@
 Finally, as a first step towards an extrinsic evaluation, we measured
-\texttt{TreeTagger}
+how \texttt{TreeTagger} performance changed after normalization step
+was applied
 
@@
 
-\section{Conclusion}\label{conclusion}
+\section{Conclusions and Future Work}\label{conclusion}
 
-With this article, we hope to have provided a better insight into the nature
-and composition of ill-formed words in German Twitter messages. As was shown
-in Section \ref{error:analysis}, special markup elements and casual sppellings
-account for more than a half unknown words discovered in Tweets. Furthermore,
-almost three quarters of non-standard spellings could be regarded as
-colloquial spelling variants rather than occasional slip of the finger. Such
-colloquial spellings also showed the tendency to be formed by well formalized
+With this article, we hope to have provided a better insight into the
+nature and composition of ill-formed words in German Twitter
+messages. As was shown in Section \ref{error:analysis}, special markup
+elements and casual sppellings account for more than a half unknown
+words discovered in Tweets. Furthermore, almost three quarters of
+non-standard spellings could be regarded as colloquial spelling
+variants rather than occasional slip of the finger. Such colloquial
+spellings also showed the tendency to be formed by well formalized
 processes and to be used over and over again in texts.
 
-We also suggested a rule-based text normalization approach which could serve
-as a baseline comparison measure for future normalization methods which may be
-suggested for German tweets. As was shown in previous sections, our approach
-could effectively address some ofthe most frequent phenomena which contribute
-to a higher rate of out-of-vocabulary words in Twitter texts such as
-Twitter-specific elements and non-standard spellings.
+We also suggested a rule-based text normalization approach which could
+serve as a baseline comparison measure for future normalization
+methods which may be suggested for German tweets. As was shown in
+previous sections, our approach could effectively address some ofthe
+most frequent phenomena which contribute to a higher rate of
+out-of-vocabulary words in Twitter texts such as Twitter-specific
+elements and non-standard spellings.
 
-We are going to make our classification and test data available online at
-\url{http://dasom.ling.uni-potsdam.de/} under the terms consistent with
-Twitter regulations. Our classified data could, in our opinion, significantly
-save tedious manual work for other researchers.
+We are going to make our classification and test data available online
+at \url{http://dasom.ling.uni-potsdam.de/} under the terms consistent
+with Twitter regulations. Our classified data could, in our opinion,
+significantly save tedious manual work for other researchers.
 
@@
 possible steps for such refinement, we see a possible addition of a
-machine-learning classifier which could help distinguish spelling mistakes
-from valid unknown words. On the other side, a better disambiguation of
-suggested replacement variants for misspellings could be achieved by letting
-part-of-speech tagger process a word grid with input tokens and their
-suggested replacements. At the end of tagging, not only the most probable tag
-sequence but the most likely word/tag mesh could be chosen in a single run. At
-any rate, these steps are beyond the scope of this work. But we hope to have
-laid the groundwork for them.
+machine-learning classifier which could help distinguish spelling
+mistakes from valid unknown words. On the other side, a better
+disambiguation of suggested replacement variants for misspellings
+could be achieved by letting part-of-speech tagger process a word grid
+with input tokens and their suggested replacements. At the end of
+tagging, not only the most probable tag sequence but the most likely
+word/tag mesh could be chosen in a single run. At any rate, these
+steps are beyond the scope of this work. But we hope to have laid the
+groundwork for them.
 
@@
 
-This work was financially supported by ... as part of collaborative project
-``...''. The authors are also thankful to ... for help with the analysis of
-data.
+This work was financially supported by ... as part of collaborative
+project ``...''. The authors are also thankful to ... for help with
+the analysis of data.
 

### 2013-08-16 darmstadt_gscl_2013/data/evaluation/bleu_kit/scripts/bleulib.rb
step towards evaluation

@@ -1,0 +1,248 @@
+module JnMtLib
+	# Create an array count of n.
+	# Each elements are selected randomly from an interval of [0,max].
+	def randext(n,max)
+	  counter = 0
+
+	  ret = []
+
+	  while counter < n
+	    id = rand(max)
+	    ret << id
+	    counter += 1
+	  end
+	  ret
+	end
+
+	def calc_line_ngram_count(words, n)
+    c = words.length-n+1
+    (c < 0)? words.length : c
+	end
+
+	def get_line_ngrams(words, n, ngram_count)
+		ngrams = {}
+		words.each_index{|idx|
+			break if idx == ngram_count
+			subwords = words[idx,n]
+			ngrams[subwords] ||= 0
+			ngrams[subwords] += 1
+		}
+		ngrams
+	end
+
+	#Calculate 'clip count' of each line..
+	def calc_line_clip_count(tngrams, rngramss)
+		clipcount = 0
+		tngrams.each{|tngram, tnc|
+			rnc = 0
+			rngramss.each{|rngrams|
+				next if rngrams[tngram] == nil
+				rnc = rngrams[tngram] if rnc < rngrams[tngram]
+			}
+			clipcount += (rnc > tnc)? tnc : rnc
+		}
+		clipcount
+	end
+
+	def count_multi_ngrams(tws, rwss, n)
+		tcount = 0
+		clipcount = 0
+
+		tws.each_index{|lidx|
+			tline = tws[lidx]
+			tnum= calc_line_ngram_count(tline, n)
+			tcount += tnum
+
+			tngrams = get_line_ngrams(tline, n, tnum)
+
+			rngramss = []
+			rwss.each{|rws|
+				rnum = calc_line_ngram_count(rws[lidx], n)
+				rngrams = get_line_ngrams(rws[lidx], n, rnum)
+
+				rngramss << rngrams
+			}
+
+			clipcount += calc_line_clip_count(tngrams, rngramss)
+		}
+		[clipcount, tcount]
+	end
+
+	#calculate 'best match length'.
+	def get_best_match_length(tlen, references)
+		ret = nil
+		mindist = nil
+		references.map{|ref| ref.length}.each{|num|
+			dist = (tlen-num).abs
+			if mindist == nil or dist < mindist
+				mindist = dist
+				ret = num
+			#elsif dist == mindist and num < ret
+			#	ret = num
+			end
+		}
+		ret
+	end
+
[…]

### 2013-08-16 darmstadt_gscl_2013/article_twitter_normalization.tex
srticle updated

@@
 be explained by the fact that colloquial spellings are usually formed
-by systematic rewriting processes which are also usually applied to
+by systematic rewriting processes which are also normally applied to
 frequently used words. True misspellings, on the contrary, are rather
@@
 
-In order to investigate which processes were the most common sources
-of colloquial spellings
+On closer examination of colloquial spellings, it could be found that
+a large part of them was a result of phonetically motivated
+rewritings.
 
-These processes are supposed to make written form of words more
-similar to their casual soundings in everyday speech.
+According to our data, the most productive of such slang producing
+processes turned out to be:
+\begin{itemize}
+  \item Omission of `e' in unstressed positions, e.g. \textit{w\"urd},
+    \textit{zuguckn} etc. In cases when `e' was part of the impersonal
+    pronoun ``es'' following a verb, the remaining `s' of this pronoun
+    was usually appended to the preceding verb form,
+    e.g. \textit{wirds} instead of \textit{wird es};
 
-According to our data, the most productive of such
-processes were:
-\begin{itemize}
-  \item Omissions of `e' in unstressed (``schwa'') positions,
-    e.g. \textit{w\"urd}, \textit{zuguckn} etc. In cases when `e' was part of
-    the impersonal pronoun ``es'' following a verb, remaining `s' of this
-    pronoun was usually appended to the preceding verb form;
-
-  \item Complete omissions or replacements of final consonants with their
-    voiceless equivalents, e.g. \textit{nich} instead of \textit{nicht} or
-    \textit{Tach} instead of \textit{Tag};
+  \item Complete omission or replacement of final consonants with
+    their voiceless equivalents, e.g. \textit{nich} instead of
+    \textit{nicht} or \textit{Tach} instead of \textit{Tag};
 

### 2013-08-21 darmstadt_gscl_2013/article_twitter_normalization.tex
next to last update before merges from Tatjana

@@
 
-A closer look at unknown words which were classified as misspellings
-revealed that a prevailing majority of them was considered as
-colloquial spelling variants. Such variants accounted for 70.5~\% of
-detected spelling mistakes in \texttt{hunspell} data and for 66.17~\%
-of misspellings recognized by \texttt{TreeTagger}. Frequency
+A closer look at unknown words classified as misspellings revealed
+that a prevailing majority of them was considered as colloquial
+spelling variants. Such variants accounted for 70.5~\% of detected
+spelling mistakes in \texttt{hunspell} data and for 66.17~\% of
+misspellings recognized by \texttt{TreeTagger}. Frequency
 distributions of colloquial and non-colloquial misspellings in data

### 2013-08-25 darmstadt_gscl_2013/data/evaluation/bleu_kit/scripts/doc_bleu.rb
small update of Makefile for test procedure

@@ -1,3 +1,5 @@
+#!/usr/bin/env ruby1.9
+
 require 'optparse'
 require "#{File.dirname(__FILE__)}/bleulib"
 

### 2013-08-26 darmstadt_gscl_2013/data/evaluation/scripts/mteval-v13.pl
procedure for caclualting BLEU scroe updated

@@ -1,0 +1,1163 @@
+#!/usr/bin/env perl
+
+use warnings;
+use strict;
+use utf8;
+use Encode;
+use XML::Twig;
+
+binmode STDOUT, ":utf8";
+binmode STDERR, ":utf8";
+
+
+#################################
+# History:
+#
+# version 13
+#    * Uses a XML parser to read data (only when extension is .xml)
+#    * Smoothing of the segment-level BLEU scores, done by default
+#        * smoothing method similar to that of bleu-1.04.pl (IBM)
+#        * see comments above the 'bleu_score' method for more details on how the smoothing is computed
+#        * added a '--no-smoothing' option to simulate old scripts behavior
+#    * Introduction of the 'brevity-penalty' option, taking one of two values:
+#        * 'closest' (default) : act as IBM BLEU (taking the closest reference translation length)
+#            * in case two reference translations are at the same distance, will take the shortest one
+#            * for more details regarding how the BP is computed, see comments of the 'brevity_penalty_closest' function
+#        * 'shortest' : act as previous versions of the script (taking shortest reference translation length)
+#    * Introduction of the 'international-tokenization' option, boolean, disabled by default
+#        by default (when the option is not provided), uses 11b's tokenization function
+#        when option specified, uses v12's tokenization function
+#    * Introduction of a 'Metrics MATR output' flag (option '--metricsMATR')
+#        when used, creates three files for both BLEU score and NIST score:
+#            * BLEU-seg.scr and NIST-seg.scr: contain segment-level scores
+#            * BLEU-doc.scr and NIST-doc.scr: contain document-level scores
+#            * BLEU-sys.scr and NIST-sys.scr: contain system-level scores
+#    * SGML parsing
+#        * script will halt if source, reference and test files don't share the same setid attribute value (used for metricsMATR output)
+#        * correct segment IDs extracted from the files (was previously using an array, and using the index as a segID for output)
+#    * detailed output flag (-d) can now be used when running both BLEU and NIST
+#
+# version 12
[…]

### 2013-08-27 darmstadt_gscl_2013/article_twitter_normalization.tex
related work partially re-written

@@
 \usepackage{url}
+\usepackage{amsmath}
 
@@
 \newcommand{\uniqoov}{\% of unique OOVs}
+
+\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 
-  This article gives an overview of existing approaches to the problem
-  of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
-  language texts. These approaches are classified with regard to the
-  size of text spans and knowledge inference mechanisms which they
-  rely on in their work. Additionally to that, we conduct quantitative
-  and qualitative analyses of unknown words in German Twitter
-  messages, in order to see how relevant the OOV and text
-  normalization problems are for this particular kind of micro-texts
-  and what the characteristics of these OOVs are. In a concluding
-  step, we present a set of ad-hoc techniques which are supposed to
-  tackle some of the most prominent disturbing effects found during
-  the analyses and show how this set of techniques helps us lower the
-  average rate of out-of-vocabulary tokens in Twitter messages and how
-  this lower OOV-rate in turn helps improve the quality of automatic
-  part-of-speech tagging.
+  %% This article gives an overview of existing approaches to the problem
+  %% of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
+  %% language texts. These approaches are classified with regard to the
+  %% size of text spans and knowledge inference mechanisms which they
+  %% rely on in their work. Additionally to that, we conduct quantitative
+  %% and qualitative analyses of unknown words in German Twitter
+  %% messages, in order to see how relevant the OOV and text
+  %% normalization problems are for this particular kind of micro-texts
+  %% and what the characteristics of these OOVs are. In a concluding
+  %% step, we present a set of ad-hoc techniques which are supposed to
+  %% tackle some of the most prominent disturbing effects found during
+  %% the analyses and show how this set of techniques helps us lower the
+  %% average rate of out-of-vocabulary tokens in Twitter messages and how
+  %% this lower OOV-rate in turn helps improve the quality of automatic
+  %% part-of-speech tagging.
+
+ In this article, we conduct quantitative and qualitative analyses of
+ unknown words in German Twitter messages, and propose a normalization
+ method which prepares German Twitter text for standard text
+ processing tools. In the first part, the prevalence of different
+ types of out-of-vocabulary (OOV) tokens and non-standard language in
+ German Twitter data is determined. In a second step, we present a set
+ of ad-hoc techniques which can tackle some of the most prominent
+ effects found during the analyses. We show how this set of techniques
+ helps us lower the average rate of out-of-vocabulary tokens in
+ Twitter messages and how this lower OOV-rate in turn helps improve
+ the quality of automatic part-of-speech tagging.
 
@@
 
-In the next Section, we will give a short overview of existing
-scientific approaches to the problem of tackling out-of-vocabulary
-words in non-standard texts. After that, in Section
-\ref{error:analysis} we will analyze which types of noisiness
-phenomena are especially characteristic for German Twitter. Section
-\ref{normalization} will subsequently describe an automatic procedure
-for mitigating some of the most prominent of those effects. In a
-concluding step, we will perform an evaluation of the results of this
-procedure and give further suggestions for future research.
+In the next Section, we give a short overview of existing scientific
+approaches to the problem of tackling out-of-vocabulary words in
+non-standard texts. After that, in Section \ref{error:analysis} we
+will analyze which types of noisiness phenomena are especially
+characteristic for German Twitter. Section \ref{normalization} will
+subsequently describe an automatic procedure for mitigating some of
+the most prominent of those effects. In a concluding step, we will
+perform an evaluation of the results of this procedure and give
+further suggestions for future research.
 
@@
 
-Before proceeding with the description of recent methods for noisy
-text normalization (NTN), we first would like to define the criteria
-by which these methods could be classified. It should be noted that
-there already exist several classifications of NTN approaches
-including, for example, Kukich (\cite{kukich}) and Kobus et
-al. (\cite{kobus}).
+%% Before proceeding with the description of recent methods for noisy
+%% text normalization (NTN), we first would like to define the criteria
+%% by which these methods could be classified. It should be noted that
+%% there already exist several classifications of NTN approaches
+%% including, for example, Kukich (\cite{kukich}) and Kobus et
+%% al. (\cite{kobus}).
 
-Kukich (\cite{kukich}), for instance, divided all NTN techniques into
-six classes:
-\begin{enumerate}
-\item minimum edit distance techniques;
-\item similarity key techniques;
-\item rule-based techniques;
-\item \textit{n}-gram based techniques;
-\item probabilistic techniques;
-\item neural nets.
-\end{enumerate}
-Kobus (\cite{kobus}), on the contrary, referred to NTN methods as
-\textit{metaphors} and split them into the following three groups:
-\begin{enumerate}
-\item ``spell checking'' metaphor;
-\item ``translation'' metaphor;
-\item ``speech recognition'' metaphor.
-\end{enumerate}
+%% Kukich (\cite{kukich}), for instance, divided all NTN techniques into
+%% six classes:
+%% \begin{enumerate}
+%% \item minimum edit distance techniques;
+%% \item similarity key techniques;
+%% \item rule-based techniques;
+%% \item \textit{n}-gram based techniques;
+%% \item probabilistic techniques;
+%% \item neural nets.
+%% \end{enumerate}
+%% Kobus (\cite{kobus}), on the contrary, referred to NTN methods as
+%% \textit{metaphors} and split them into the following three groups:
+%% \begin{enumerate}
+%% \item ``spell checking'' metaphor;
+%% \item ``translation'' metaphor;
+%% \item ``speech recognition'' metaphor.
+%% \end{enumerate}
 
-Though both of these divisions seem to be justified to some extent, it
-is difficult to determine using them whether an NTN approach that
-detects and restores incorrectly spelled words on the basis of
-phonetical \textit{n}-gram statistics should fall into the
-\textit{n}-gram based, probabilistic, spell checking or speech
-recognition class.
+%% Though both of these divisions seem to be justified to some extent, it
+%% is difficult to determine using them whether an NTN approach that
+%% detects and restores incorrectly spelled words on the basis of
+%% phonetical \textit{n}-gram statistics should fall into the
+%% \textit{n}-gram based, probabilistic, spell checking or speech
+%% recognition class.
 
-This confusion is explained by the fact that the above classifications
-both rely on several independent criteria at the same time, however
-each of these criteria characterizes an NTN system from a different
-point of view. As a consequence of this, unambiguous assignment of an
-NTN approach to one particular class often becomes impossible. In
-order to avoid this, we instead suggest using separate classifications
-for each type of involved criteria.
+%% This confusion is explained by the fact that the above classifications
+%% both rely on several independent criteria at the same time, however
+%% each of these criteria characterizes an NTN system from a different
+%% point of view. As a consequence of this, unambiguous assignment of an
+%% NTN approach to one particular class often becomes impossible. In
+%% order to avoid this, we instead suggest using separate classifications
+%% for each type of involved criteria.
 
-One of such criteria which in our opinion would be worth a separate
-classification is \emph{segmentation level} that is used
-\begin{inparaenum}[\itshape a\upshape)]
-\item to infer in-vocabulary (IV) equivalents for OOV
-  tokens\label{candidate:inferring} and
-\item to choose the most probable variant\label{candidate:selection}
-  among multiple possible suggestions\footnote{For the cases, when
-    segments of different lengths are used for tasks
-    \ref{candidate:inferring} and \ref{candidate:selection}, we note
-    it explicitly in our classification on which segmentation length
-    each of these subtasks relies.}.
-\end{inparaenum} For this criterion, we propose division into the following
-classes:
-\begin{enumerate}
-  \item graphematic\footnote{Depending on whether phonetical
-    information is involved or not at this level, this class could be
-    further divided into a phonographematic and purely graphematic
-    subclasses.};
-  \item lexical;
-  \item phrasal.
-\end{enumerate}
-Each broader level of this hierarchy is supposed to either incorporate
-or ignore information provided by its narrower subsegments. In this
-way, we only need to mention one (the broadest) hierarchical class for
-the cases when multiple segmentation levels are involved by some
-techniques.
+%% We use two independent criteria to classify normalization methods.
+%% One of such criteria which in our opinion would be worth a separate
+%% classification
+%% is the \emph{segmentation level} that is used
+%% \begin{inparaenum}[\itshape a\upshape)]
+%% \item to infer in-vocabulary (IV) equivalents for OOV
+%%   tokens\label{candidate:inferring} and
+%% \item to choose the most probable variant\label{candidate:selection}
+%%   among multiple possible suggestions\footnote{If
+%%     segments of different lengths are used for tasks
+%%     \ref{candidate:inferring} and \ref{candidate:selection}, this can
+%%     be noted explicitly.}.
+%% \end{inparaenum} For this criterion, we propose division into the following
+%% classes:
+%% \begin{enumerate}
+%%   \item graphematic\footnote{Depending on whether phonetic
+%%     information is involved at this level, this class can be
+%%     further divided into a phonographematic and purely graphematic
+%%     subclasses.};
+%%   \item lexical;
+%%   \item phrasal.
+%% \end{enumerate}
+%% Each broader level of this hierarchy is supposed to either incorporate
+%% or ignore information provided by its narrower subsegments. In this
+%% way, we only need to mention one (the broadest) hierarchical class for
+%% the cases when multiple segmentation levels are involved by some
+%% techniques.
 
-The second criterion regards the \emph{type of information induction}
-that is used to devise the correction rules. This leads us to the
-usual NLP-taxonomy which divides all approaches into:
-\begin{enumerate}
-  \item rule-based;
-  \item statistical\footnote{Depending on the type of training data
-    required, this class is in turn usually divided into unsupervised,
-    semi-supervised, and supervised groups.};
-  \item and hybrid ones.
-\end{enumerate}
+%% The second criterion regards the \emph{type of information induction}
+%% that is used to devise the correction rules. This leads us to the
+%% usual NLP-taxonomy which divides all approaches into:
+%% \begin{enumerate}
+%%   \item rule-based;
+%%   \item statistical\footnote{Depending on the type of training data
+%%     required, this class is in turn usually divided into unsupervised,
+%%     semi-supervised, and supervised groups.};
+%%   \item and hybrid ones.
+%% \end{enumerate}
 
-According to these two classification criteria, recent approaches to
-the NTN task could be grouped together as follows.
+%% According to these two classification criteria, recent approaches to
+%% the NTN task could be grouped together as follows.
 
-The earlier works on NTN commonly relied on either purely graphematic
-or phonographematic levels of segmentation for deriving normalization
-variants of incorrectly spelled words. To purely graphematic systems
-belong methods suggested by Brill and Moore (\cite{brill}), Sproat et
-al. (\cite{sproat}), and Clark (\cite{alexander-clark}). As
-phonographematic approaches one could regard works done by Toutanova
-and Moore (\cite{toutanova}), Choudhury et al. (\cite{choudhury}),
-Cook and Stevenson (\cite{cook}), Han and Baldwin (\cite{han})
-etc. With regard to the type of information inference, most of these
-methods were supervised with the exceptions of Cook and Stevenson
-(\cite{cook}) and Han and Baldwin (\cite{han}) who claimed to use an
-unsupervised technique. Sproat et al. (\cite{sproat}) described in
-their article both a supervised and unsupervised approach.
+The earlier works on normalization of noisy messages were greatly
+influenced by text restoration techniques commonly applied in the
+domains of speech and optical character recognition. One of the most
+well-established techniques in those fields at the beginning of the
+1990-s was the method of ``noisy channel model'' (NCM) first
+introduced by Shannon in \cite{shannon}. In this method, an input text
+$T$ was regarded as a distorted version of some initial clean language
+signal $S$. And in order to find the original sequence, one had to
+solve the equation $\mathop{arg\,max} P(S|T)$ by computing an
+equivalent expression $\mathop{arg\,max} P(T|S)P(S)$. In this last
+form, the term -- $P(T|S)$ -- was usually referred to as \textit{error
+  model}, i.e. one which showed how likely it was that the given
+non-standard form $T$ could have resulted from the assumed standard
+counterpart $S$. The latter part of the equation -- $P(S)$ -- was
+called the \textit{language model} and accounted for the probability
+of form $S$ to appear in standard text in general. %% It is however
+%% not specified by NCM, what should regarded as language model, what
+%% has to be considered as an error model and eventually how a set of
+%% standard language equivalents $S$ should be derived for given
+%% non-standard form $T$.
 
-Starting from the second half of the 2000s, the raising influence and
-improved quality of machine translation tools led to the development
-of NTN technologies which used broader levels of segmentation. In
-\cite{aw}, Aw et al. suggested a supervised statistical system for
-normalization of SMS-messages which operated on automatically aligned
-phrases A few years later, Clark and Araki (\cite{clark-araki})
-described a purely rule-based method which used mappings of
-non-standard words and phrases to their corresponding standard
-language forms.
+Among works belonging to the NCM framework, we could mention the
+approach suggested by Mayes, Damerau et al. (\cite{mayes}) who used a
+uniform error model and calculated $P(S)$ on the basis of word bigrams
+statistics. As a set $S$ of possible replacement suggestions, the
+authors regarded the original input word $T$ as well as all words in
+dictionary which could be derived from the original word by applying
+at most one edit operation either insertion, or deletion, or
+substituion of a single character. In \cite{church}, Church and Gale
+suggested a more elaborated error model in which every edit operation
+was weihgted according to statistics gathered from a training corpus
+and conditioned on the letter context in which this edit operation
+apeeared. Brill and Moore (\cite{Brill}) further enhanced this model
+by considering edit operations not only on single letters but rather
+on word subsegments of different lengths. Toutanova and Moore
+(\cite{toutanova}) improved the performance of the latter work by
+23~\% by incorporating phonetical information. Eventually, Alexander
+Clark (\cite{clark}) was one among the first who addressed the text
+noisiness problem in the genre of Internet-based communication
+(IBC). In his presented system, multiple indpendent modules were used
+to perform tokenization, normalization and correction of Usenet forum
+posts. The system relied on a 3-gram language model and a trainable
+stateless stochastic transduces as error model, however no particular
+details about its implementation were provided in the article. In
+\cite{choudhury}, Choudhury et al. proposed
+
+Bangalore et al. - MT
+
+suggested an NCM
+approach in which they derived the set $S$ by applying one of the four
+operations: insertion, deletion or substitution of a single character
+or transposition of two adjacent characters to string $T$ and then
+leaving only variants which were present in vocabulary. Original word
+$T$ was also included in the generated set. As language model, the
+authors used word bigrams. As error model, a uniform distribution was
+used which assigned equal probabilities to all generated variants and
+a constant probability $\alpha$ to the original word.
+
+%% According to this, the main task of NCM consisted in finding such $S$
+%% which could maximize the probability of $S$ given $T$. By using the
+%% Bayesian rule of probability, $P(S|T)$ was defined as
+%% $\frac{P(T|S)P(S)}{P(T)}$ and in order to find $arg$ and further as
+%% $P(T|S)P(S)$ since the denominator $P()$
+
+%%  commonly relied on either purely graphematic or phonographematic
+%%  levels of segmentation for deriving normalization variants of
+%%  incorrectly spelled words. Methods suggested by Brill and Moore
+%%  (\cite{brill}), Sproat et al. (\cite{sproat}), and Clark
+%%  (\cite{alexander-clark}) are purely graphematic, whereas works by
+%%  Toutanova and Moore (\cite{toutanova}), Choudhury et
+%%  al. (\cite{choudhury}), Cook and Stevenson (\cite{cook}), Han and
+%%  Baldwin (\cite{han}), etc., can be classified as
+%%  phonographematic. With regard to the type of information inference,
+%%  most of these methods were supervised with the exceptions of Cook and
+%%  Stevenson (\cite{cook}) and Han and Baldwin (\cite{han}) who claim to
+%%  use an unsupervised technique. Sproat et al. (\cite{sproat})
+%%  described in their article both a supervised and an unsupervised
+%%  approach.
+
+%% Starting from the second half of the 2000s, the raising influence and
+%% improved quality of machine translation tools led to the development
+%% of NTN technologies which used broader levels of segmentation. In
+%% \cite{aw}, Aw et al. suggested a supervised statistical system for
+%% normalization of mobile text messages which operates on automatically
+%% aligned phrases. A few years later, Clark and Araki
+%% (\cite{clark-araki}) described a purely rule-based method which uses
+%% mappings of non-standard words and phrases to their corresponding
+%% standard language forms.
 
 As noted by Kobus et al. (\cite{kobus}), NTN methods relying on either
-graphematic or phrasal segments usually revealed complementary
-strengths and weaknesses. This notion led NLP scientists to the idea
-that by incorporating multiple levels of the language into one NTN
-system the total performace of the whole system would improve as
-different sources of information would benefit from each other. As a
-consequence of this, a wealth of combined techniques emerged in the
-past few years. Among these we should especially mention works by
-Kobus et al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), and Oliva et
+graphematic or phrasal segments usually reveal complementary strengths
+and weaknesses. This notion led NLP scientists to the idea that by
+incorporating multiple levels of the language into one NTN system the
+total performace of the whole system would improve as different
+sources of information would benefit from each other. As a consequence
+of this, a wealth of combined techniques emerged in the past few
+years. Among these we should especially mention works by Kobus et
+al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), and Oliva et
 al. (\cite{oliva}). The majority of these systems used the whole range
-of segmentation levels from phonographematatic to phrasal one, and in
-many cases they also applied different knowledge inference mechanisms
-to different levels of the language.
+of segmentation levels from phonographematatic to phrasal, and in many
+cases they also applied different knowledge inference mechanisms to
+different levels of the language.
+% % *TS*
+% It's not quite clear what these approaches actually DO -  for
+% example the combined methods above or some of the early
+% approaches. I liked how "Clark and Araki" was described in half a
+% sentence, maybe add something like that for one or two of the papers
+% in the first paragraph ("earlier works") and also for the last
+% paragraph ("combined methods"). I can shorten the "combined methods"
+% paragraph more if needed.
+%
 
@@
 It should however be noted that almost all of the above methods mainly
-concentrated on only English data. A few exceptions from that are
+concentrated on only English data. A few exceptions are the
 approaches suggested by Beaufort et al. (\cite{beaufort}) for French,
-and Oliva et al. (\cite{oliva}) for Spanish. To find out which
-peculiarities of ill-formed words are characteristic for German, we
-will perform a quantitive and qualitative analysis of unknown words in
+and Oliva et al. (\cite{oliva}) for Spanish. Since the peculiarities
+of short messages are often language-specific, we
+perform a quantitive and qualitative analysis of unknown words in
 German Twitter in the next Section in order to see what kind of NTN
 techniques would be most suitable for handling such words there.
-
 \section{Analysis of Unknown Tokens}\label{error:analysis}
@@
     communication;\label{style}
-  \item \textbf{Sloppiness of users' input}. In the scope of this
-    group, we considered incorrect spellings of words encountered in
+  \item \textbf{Misspellings}. In the scope of this group, we
+    considered incorrect spellings of words encountered in
     text.\label{spell}
@@
 
+\bibitem[1991]{church}
+  Church, K., Gale, W.: %
+  Probability scoring for spelling correction. %
+  Statistics and Computing. {\bfseries 1} %
+  (1991) 93--103 %
+
+\bibitem[2003]{clark}
+  Clark, A.,: %
+  Pre-Processing very noisy text. %
+  In Proceedings of Workshop on Shallow Processing of Large Corpora. %
+  Corpus Linguistics. %
+  Lancaster (2003)
+
 \bibitem[2011]{clark-araki}
@@
 
+\bibitem[1991]{mayes}
+  Mayes, E., F. Damerau, et al.: %
+  Context Based Spelling Correction. %
+  Information Processing and Management. 27(5) %
+  (1991) 517--522
+
 \bibitem[2012]{guardian:sms}
@@
   Knowledge Management CIKM 2012, Hawai, (Oct 29 - Nov 2, 2012)
-
-  McVeigh, T.: %
-  Text messaging turns 20. %
-  The Observer (December 1, 2012)
 
@@
 
+\bibitem[1948]{shannon}
+  Shannon, C. E.: %
+  A mathematical theory of communication. %
+  Bell system techical journal, 27:379--423 %
+  (1948) 623--656
+
 \bibitem[1996]{sparck}

### 2013-08-28 darmstadt_gscl_2013/article_twitter_normalization.tex
related work partially expanded

@@
 
-Among works belonging to the NCM framework, we could mention the
-approach suggested by Mayes, Damerau et al. (\cite{mayes}) who used a
-uniform error model and calculated $P(S)$ on the basis of word bigrams
-statistics. As a set $S$ of possible replacement suggestions, the
-authors regarded the original input word $T$ as well as all words in
-dictionary which could be derived from the original word by applying
-at most one edit operation either insertion, or deletion, or
-substituion of a single character. In \cite{church}, Church and Gale
-suggested a more elaborated error model in which every edit operation
-was weihgted according to statistics gathered from a training corpus
-and conditioned on the letter context in which this edit operation
-apeeared. Brill and Moore (\cite{Brill}) further enhanced this model
-by considering edit operations not only on single letters but rather
-on word subsegments of different lengths. Toutanova and Moore
-(\cite{toutanova}) improved the performance of the latter work by
-23~\% by incorporating phonetical information. Eventually, Alexander
-Clark (\cite{clark}) was one among the first who addressed the text
-noisiness problem in the genre of Internet-based communication
-(IBC). In his presented system, multiple indpendent modules were used
-to perform tokenization, normalization and correction of Usenet forum
-posts. The system relied on a 3-gram language model and a trainable
-stateless stochastic transduces as error model, however no particular
-details about its implementation were provided in the article. In
-\cite{choudhury}, Choudhury et al. proposed
+Among works belonging to the NCM framework, we could mention the approach
+suggested by Mayes, Damerau et al. (\cite{mayes}) who used a uniform error
+model and calculated $P(S)$ on the basis of word bigrams statistics. As a set
+$S$ of possible replacement suggestions, the authors regarded the original
+input word $T$ as well as all words in dictionary which could be derived from
+$T$ by applying at most one edit operation which could be either insertion, or
+deletion, or substituion of a single character or a transposition of two
+adjacent characters. In \cite{church}, Church and Gale suggested a more
+elaborated error model in which they weighted every edit operation according
+to statistics generated from a training corpus and additionally conditioned
+each of these operations on the letter context in which they appeared. Brill
+and Moore (\cite{Brill}) enhanced this model by considering edit operations
+not only for single letters but for whole word subsegments up to a length of 5
+characters. Toutanova and Moore (\cite{toutanova}) improved the performance of
+the latter work by 23~\% by incorporating phonetical information in
+it. Eventually, Alexander Clark (\cite{clark}) was one among the first who
+addressed the text noisiness problem in the genre of Internet-based
+communication (IBC). In his presented system, multiple independent modules
+were used to simultaneously perform tokenization, normalization and correction
+of Usenet forum posts and . This system relied on a 3-gram language model and
+a trainable stateless stochastic transduces as error model, however no
+particular details about its implementation were given in the article. In
+\cite{choudhury}, Choudhury et al. proposed a modified version of NCM approach
+which was specifically targeted at normalization of texting language in
+English SMS messages. This model built on the basis of the work by Toutanova
+and Moore (\cite{toutanova}) and utilized bigram statistics as language model
+for its work. An important change in contrast to the work done by Toutanova
+(\cite{toutanova}), however, consisted in the fact, that Choudhury et
+al. (\cite{choudhury}) used a joint phone-character HMM lattice for computing
+probabilities of restoration suggestions, whereas Toutanova and Moore
+(\cite{toutanova}) separately calculated probabilities for phonemic and
+graphemic derivations, linearly interpolating them at the end.
 
